### 2015-05-15 nlpcc/paper.tex
first commit of nlpcc

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{url}
\usepackage{color}

\urldef{\mailthu}\path|{lijuanzi@}tsinghua.edu.cn|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip\noindent\keywordname\enspace\ignorespaces#1}
\newcommand{\para}[1]{\vspace{0.1cm}\noindent\textbf{#1}}

\begin{document}
\mainmatter

\title{Building Large-Scale Bilingual Knowledge Base from Multi-Encyclopedia}
\titlerunning{Bilingual Knowledge Base}
\author{Mingyang Li$^\dag$ \and Yao Shi$^\dag$ \and Zhigang Wang$^\dag$}
\authorrunning{Mingyang Li et.al}

\institute{$^\dag$Tsinghua National Laboratory for Information Science and Technology,\\
Department of Computer Science and Technology,\\
Tsinghua University, Beijing 100084, China\\
\mailthu\\
}

\maketitle

\begin{abstract}
    Abstract Text

\keywords{Knowledge Base, Semantic Web, Linked Data, Ontology, Cross-lingual}
\end{abstract}

\section{Introduction}

Introduction Text

Current situation of KB
Current situation of cross-lingual KB

Knowledge bases such as DBpedia, YAGO, and BabelNet are mainly built upon the multilingual Wikipedia. ..

Some problems are to be addressed:
\begin{itemize}
  \item The imbalanced size of different Wikipedia languages leads to less data of various languages, which makes it more difficult to build a multi-language knowledge base.
  \item The number of existed cross-lingual links in Wikipedia is so small that affects the quality of a bilingual knowledge base. Especially there is no obvious links in properties.
  \item The large but irrigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example, 
\end{itemize}

Our main contributions include:
\begin{itemize}
  \item We propose a method to build a Chinese-English ontology combining four encyclopedias, which are English Wikipedia, Chinese Wikipedia, Baidu and Hudong. The latter three contain large amount of Chinese knowledge, which helps balance information of two languages and enrich the knowledge base.
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and by analysing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise SubClassOf and InstanceOf relation.
  \item A website is developed based on our ontology and also a SPARQL interface is provided for public query operations in our knowledge base.
\end{itemize}

The rest of the paper is organized as follows. Section \ref{sec:pre} introduces the four encyclopedias which are English Wikipedia, Chinese Wikipedia, Baidu and Hudong. Besides, definitions are proposed in this section. Section \ref{sec:oe} presents the extraction approach in concept, instance and property level. Method of initiating cross-lingual link set will also be mentioned. Section \ref{sec:cle} propose an extension approach for discovering more cross-lingual relations. Section \ref{sec:tp} describes how to prune the taxonomy. Section \ref{sec:result} shows the results of established knowledge base. Section \ref{sec:con} gives the conclusion and future work.

\section{Preliminary}
\label{sec:pre}
In this section, we firstly introduce the four encyclopedias which are used to build and enrich our knowledge base. They are English and Chinese Wikipedia, Baidu and Hudong Encyclopedia. Then we gives some related definitions to formalize our model.

\subsection{Encyclopedias}
\label{sec:encyclopedias}
\subsubsection{Wikipedia}
Nowadays, Wikipedia is the largest store of human knowledge. It was launched in 2001 and has hold over 35 million articles in 288 language by 2015. Among these articles, English articles contribute most. There are \textcolor{red}{4,867,719} articles in English while only \textcolor{red}{over 800,000 articles} in Chinese. It is obvious that the quantity of English articles is far more than Chinese. Such imbalance makes those ontologies based on Wikipedia only behave bad in cross-lingual aspect. For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that helps little when other poeple want to do cross-lingual research depending on DBpedia. To avoid the imbalance problem, two other Chinese encyclopedias are utilized to enrich Chinese source.
Articles in Wikipedia are manually editted by various authors. Wikipedia provides many templates to guide authors composing their context in a regular way. For example, \textcolor{red}{China use template XXX}. Moreover, an infobox in one article also follows an infobox template, which maintains a property set of similar articles and display labels on website page.
\subsubsection{Other Chinese Encyclopedias}
There are several large-scale monolingual Chinese Encyclopedias currently. Among those, Baidu Baike and Hudong are the most well-known. Hudong was founded in 2005 and contains more than 12 millions articles with about 9 millions experts' contribution util 2015, April. At the mean time, Baidu Baike maintains more than 11 millions articles. These two resource are similar in article structure, somethimes even in content. 
\subsubsection{Encyclopedia Page}
All these four encyclopedias have two important elements, articles and category taxonomy. A taxonomy presents the relation between categories. Usually a category has its sub classes and super classes. Besides, an article belongs to one or more categories. Fig. \ref{fig:hudong-taxonomy} An article describes an topic with rich information created and modified by several verified editors. The content and relation of an article provide a lot when building a \textcolor{red}{global?} knowledge base. In general, there are five elements can be exploited:
\begin{figure}
    \centering
    %\subfigure[]{
    \begin{minipage}[t]{0.5\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy}}
        \label{fig:hudong-taxonomy}
        \caption{Taxonomy in Hudong.}
    %}
    \end{minipage}%
    \begin{minipage}[t]{0.5\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/baidu-article}}
        \label{fig:baidu-article}
        \caption{A snap of an article in Baidu Baike}
    \end{minipage}%
\end{figure}
\begin{itemize}
  \item Title: A Title is the label of topic. Every article has a unique title, which can be used to distinguish each topic.
  \item Abstract: An abstract is a brief summarize of the article topic. It's always the first paragraph of an article. Usually it can be taken as an important feature to a topic. 
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are in general subject-attribute-value triples formalized as a table. Information in this table includes important properties of the topic.
  \item Links: Links are entries directing to other articles within the encyclopedia. They lead readers to reference articles. Actually, they represent the relations between the current article and other articles.
  \item Category: The categories that an article belongs to are usually listed below the article page, shown as tags. An article attaches to one or more categories.
\end{itemize}
Fig. \ref{fig:baidu-article} shows a snap of an article in Baidu Baike. The five elements mentioned above are annotated.
\subsection{Cross-lingual Links}
In order to build a bilingual knowledge base, we need the relation between Chinese source and English source, which helps merge different language information into their unique and common topic. In Wikipedia, most articles have language links which guide the reader to the article in specific language under the same topic. Fig. \ref{fig:lang-link} shows an example of language links in Wikipedia. Taking advantage of such existed links in Wikipedia, we can generate an initial bilingual ontology based on Chinese and English Wikipedia. However, the result is just an ontology based on Wikipedia, like DBpedia. To combine Hudong and Baidu Baike ,which are lack of cross-lingual information but more Chinese source, we employ the approach from \cite{} to discover bilingual links between English Wikipedia and Hudong in Section \ref{sec:cld}

\subsection{Definitions}

\section{Extraction}
\label{sec:oe}
In order to build a billinual knowledge base, we first set up an ontology to schema information from the four encyclopedia. The ontology includes concepts, which are extracted from category taxonomy, instances, which are defined according to articles and properties, which are based on infobox and also templates assistant. We will describe our building approach as follow.
\subsection{Concept Extraction}
\label{sec:ce}
A concept in ontology is defined as a type of similar instances. For example, the concept of instance \emph{Tsinghua University} is \emph{University} or \emph{Organization}. In general, a concept has super classes and sub classes, which means it has \emph{subClassOf} relation with other classes. Those concepts comprise a taxonomy which presents a backbone of the ontology.
In an encyclopedia, a category groups several articles and also has super-categories and sub-categories, just like concept doing. Therefore we can extract concepts based on existed category system. 
However, the whole taxonomy can not directly transform from category system because of the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages that are typical of Wikipedia. For example, \textcolor{red}{list of ... or tempalte:infobox}
    \item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-categories of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one or two articles. According to the definition of concept, such categories are less representive to a group of instance, therefore it's unwise to retain it as concept.
\end{itemize}
   To retrieve a cleaner and preciser concept taxonomy, we firstly do some refine works as follow:
\begin{itemize}
    \item Delete specific categories in Wikipedia.
    \item Delete inconsistent sub-categories and keep the super one.
    \item Delete categories that relate to less than two articles.
\end{itemize}
The cleaning works are carried out in all encyclopedias for rule consistency when extracting. The remaining categories comprise an original concept taxonomy. A category and its sub-categories are correlated by the relation \emph{SubClassOf}, and a category and its articles are correlated by the relation \emph{InstanceOf}. However, there are still inaccurate samples in the two relations. For example, \textcolor{red}{example}. We will prune the taxonomy later.

\subsection{Property Extraction}
\label{sec:pe}
A property is defined as an attribute of instance. It represents the relation between two instances or an instance and its value. We divided properties into two types: datatype properties, which \textcolor{red}{...}; object properties, which \textcolor{red}{...}. Considering both content and infobox of an article, we extract two groups of properties, general-properties and Infobox-properties.

\subsubsection{General-properties}
Characteristics of an instance are seen as general-properties, including label, abstract, and url. Those properties describe specific information of an instance. The label property identifies a unique instance, whose value is article title. The abstract property provides a brief description of an instance, whose value is the first paragraph of article. The url property saves the resource of an instance, which is actually a url in Wikipedia or Hudong or Baidu Baike. All of them are datetype properies.
\subsubsection{Infobox-properties}
Attributes acquired from infobox data are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. All attributes are relating with a typical value in the infobox, the value maybe a text or a reference, usually a url links to anothor instance. The type of a property, datatype or object, depends on the value. Ordinarily, a plain text value marks the property as datetype while an instance reference determines the property as object. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.
We occur some chanllenges when extracting properties from infoboxes:
\begin{itemize}
    \item There are some 
    \item 
    \item 
\end{itemize}

\subsection{Instance Extraction}
\label{sec:ie}
In encyclopedia, an article describes an unique entity in the world. Therefore we can extract article content as an instance. But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including Category List pages, Template documentations \textcolor{red}{and...}.
Each instance contains relations with concepts and properties. Take the movie 星际穿越(Interstellar) as an example in Fig.\ref{fig:interstellar}. concepts are assigned according to the category tags below the article page. 美国科幻片(American science fiction films) is a concept to Interstellar. In the meantime, we obtain label property from article title, which is 星际穿越(Interstellar) and abstract property from the first paragraph. Infobox-properties are also acquired via extracting from infobox in the article. Besides, according to links placing in content, we gain the reference between the current instance to others, such as 华纳兄弟(Warner Bros.).
After the preprocessing above, we harvest two types of information. One is the characteristics of instance, including instance-label, instance-abstract. The other is relationships, containing concept-instance, instance-property-value and instance-instance.
\subsection{Cross-lingual Links Extraction}
\label{sec:cld}
Wikipedia has \textcolor{red}{number} cross-lingual links between articles of English and Chinese. By extracting language links from Wikipedia, we can get an initial cross-lingual link set of concepts and instances. 
However, in property aspect, there is no obvious infobox links between English and its mapping Chinese article. According to the edit mechanism of Wikipedia, we use infobox template to get display label and cross-lingual links of an infobox-property. Fig. \ref{fig:template} shows a typical example of infobox template. 
\section{Cross-lingual Links Extension}
\label{sec:cle}
Research of Wang ZhiChun

After the extracting preprocessing, we acquire a series of semi-structured data, including concept information, property pairs, instance information, relations among the three and cross-lingual links. Holding these raw data in hand, we then build an ontology schema for the futher knowledge base.

\section{Cross-lingual Knowledge Base Building}
To construct an cross-lingual ontology schema with existing semi-structured data, firstly we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing. Secondly, we prune the taxonomy which generates from concept relationships to retain a more accurate one. At last, we hung instances and properties on to taxonomy to create a complete knowledge base.

\subsection{Cross-lingual Linking}
\label{sec:cld}
combine four ontology into on

\subsection{Taxonomy Prune}
\label{sec:tp}
Research of Wang Zhigang

\subsection{Taxonomy Prune}

\section{Result}
\label{sec:result}
\subsection{DataSet}
The four encyclopedias and their statistics data
\subsection{Extracted Knowledge Base}
Xlore statistics data.
\subsection{Query Interface}
Xlore query interface

\section{Related Work}
\label{sec:work}

\section{Conclusion and Future Work}
\label{sec:con}

\section*{Acknowledgement}
Thanks anonymous reviewers for their valuable suggestions that help us improve the quality of the paper. Thanks Prof. Chua Tat-Seng from National University of Singapore for discussion. The work is supported by 973 Program (No. 2014CB340504 ), NSFC-ANR (No. 61261130588), Tsinghua University Initiative Scientific Research Program (No. 20131089256) and THU-NUS NExT Co-Lab.

\bibliographystyle{splncs03}
\bibliography{paper}

\end{document}

### 2015-05-18 nlpcc/paper.tex
doc

@@
 \subsection{Definitions}
+Here we list definitions involved in the later sections/
+Definition 1: A Encyclopedia is considered as a collection of articles, category system and links, which can be defined as a 3-tuple:
+\begin{equation}
+W = <A,C,L>
+\end{equation} 
+where A denotes articles, C denotes categories, and L denotes links in W.
+We involve four encyclopedias, which are expressed as Wen, Wzh, Whd and Wbb.
+Definition 2: According to Section \ref {sec:}
 

### 2015-05-20 nlpcc/paper.tex
初初稿

--- 2015-05-15 nlpcc/paper.tex
@@
 \documentclass[runningheads,a4paper]{llncs}
+
+\usepackage[BoldFont,SlantFont,CJKsetspaces,CJKchecksingle]{xeCJK}
+\setCJKmainfont[BoldFont=SimHei]{SimSun}
+\setCJKmonofont{SimSun}% 设置缺省中文字体
 
@@
 \usepackage{color}
+\usepackage{CJKutf8}
 
-\urldef{\mailthu}\path|{lijuanzi@}tsinghua.edu.cn|
+\urldef{\mailthu}\path|{lmy13@}tsinghua.edu.cn|
+\urldef{\mailsy}\path|{fantasysy@}sina.com|
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip\noindent\keywordname\enspace\ignorespaces#1}
@@
 
-\title{Building Large-Scale Bilingual Knowledge Base from Multi-Encyclopedia}
+\title{Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia}
 \titlerunning{Bilingual Knowledge Base}
@@
 \mailthu\\
+\mailsy\\
 }
@@
 \section{Introduction}
+With LOD growing recent years, more and more knowledge bases are generated in different languages and in various domains.
+Several large-scale knowledge bases, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are well-known and often used for information extraction \cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and so on.
+These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.
 
-Introduction Text
+Take DBpedia as an example, it extracts structural information from Wikipedia, the largest knowledge sharing resource in the world and have already contained approximately 38.3 million things.
+Right now DBpedia provides 124 versions of non-English language including German, French and Japanese etc.
+Moreover, there are instances and 11 classes in Chinese.
+Obviously, the quality of Chinese information is not enough for further research or application.
+Neither do the other knowledge bases containing Chinese version.
 
-Current situation of KB
-Current situation of cross-lingual KB
+To build a cross-lingual knowledge base, some problems are to be addressed:(1)The imbalanced size of different Wikipedia languages leads to less data of various languages.
+In Wikipeida, the number of articles in English has reached almost 5 millions, while in Chinese there are only 800 thousand.
+The scarcity of resources makes structuring a large-scale cross-lingual knowledge base within Chinese and English difficult.
+(2)The number of existed cross-lingual links in Wikipedia is so small that affects the quality of a bilingual knowledge base.
+Especially there is no obvious links in properties.Statistically, only about XX thousand cross-lingual links are between English and Chinese articles.(3)The large but irrigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
+For example,\textcolor{red}{example}
 
-Knowledge bases such as DBpedia, YAGO, and BabelNet are mainly built upon the multilingual Wikipedia. ..
+%In Semantic Web, a large-scale multilingual knowledge base can help …
 
-Some problems are to be addressed:
+%Thus it’s significative to build a Chinese-English knowledge base and benefit from it.
+
+Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong and Baidu Baike.
+To solve the unbalance problem, we utilize such seperated resources to enrich our Chinese information.
+In this paper, we propose an approach to combine four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
+To get a more available result, we also make judgement on the relation among concepts and instances.
+At last, a query interface is provided to access the knowledge base.
+Specifically, our work makes the following contributions:
 \begin{itemize}
-  \item The imbalanced size of different Wikipedia languages leads to less data of various languages, which makes it more difficult to build a multi-language knowledge base.
-  \item The number of existed cross-lingual links in Wikipedia is so small that affects the quality of a bilingual knowledge base. Especially there is no obvious links in properties.
-  \item The large but irrigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example, 
-\end{itemize}
-
-Our main contributions include:
-\begin{itemize}
-  \item We propose a method to build a Chinese-English ontology combining four encyclopedias, which are English Wikipedia, Chinese Wikipedia, Baidu and Hudong.
-The latter three contain large amount of Chinese knowledge, which helps balance information of two languages and enrich the knowledge base.
-  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and by analysing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise SubClassOf and InstanceOf relation.
+  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining four encyclopedias, which are English Wikipedia, Chinese Wikipedia, Baidu and Hudong.
+The latter three contain large amount of Chinese knowledge, which helps balance and enrich information of two languages.
+  %\item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and by analysing templates in Wikipedia for property.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relation in ontology.
   \item A website is developed based on our ontology and also a SPARQL interface is provided for public query operations in our knowledge base.
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:pre} introduces the four encyclopedias which are English Wikipedia, Chinese Wikipedia, Baidu and Hudong.
+Section \ref{sec:pre} introduces the four involved encyclopedias.
 Besides, definitions are proposed in this section.
-Section \ref{sec:oe} presents the extraction approach in concept, instance and property level.
+Section \ref{sec:extraction} presents the extraction approach in concept, instance and property level.
 Method of initiating cross-lingual link set will also be mentioned.
-Section \ref{sec:cle} propose an extension approach for discovering more cross-lingual relations.
-Section \ref{sec:tp} describes how to prune the taxonomy.
+\iffalse Section \ref{sec:cle} propose an extension approach for discovering more cross-lingual relations.\fi Section \ref{sec:tp} describes how to prune the taxonomy.
 Section \ref{sec:result} shows the results of established knowledge base.
+Section \ref{sec:work} induces related work about this paper.
 Section \ref{sec:con} gives the conclusion and future work.
@@
 \label{sec:pre}
-In this section, we firstly introduce the four encyclopedias which are used to build and enrich our knowledge base.
-They are English and Chinese Wikipedia, Baidu and Hudong Encyclopedia.
-Then we gives some related definitions to formalize our model.
+In this section, we firstly introduce the four encyclopedias used to build and enrich our knowledge base. Then we give some related definitions to formalize our precedure.
 
@@
 \subsubsection{Wikipedia}
-Nowadays, Wikipedia is the largest store of human knowledge.
+Nowadays, Wikipedia is the largest data store of human knowledge.
 It was launched in 2001 and has hold over 35 million articles in 288 language by 2015.
-Among these articles, English articles contribute most.
-There are \textcolor{red}{4,867,719} articles in English while only \textcolor{red}{over 800,000 articles} in Chinese.
+Out of these, English articles contribute most.
+There are 4.8 million articles in English while only over 800thousand articles in Chinese.
 It is obvious that the quantity of English articles is far more than Chinese.
-Such imbalance makes those ontologies based on Wikipedia only behave bad in cross-lingual aspect.
+Such imbalance makes those ontologies based on Wikipedia-only behave badly in cross-lingual aspect.
 For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that helps little when other poeple want to do cross-lingual research depending on DBpedia.
-To avoid the imbalance problem, two other Chinese encyclopedias are utilized to enrich Chinese source.
+To avoid the imbalance problem, two other Chinese encyclopedias are utilized to extend Chinese source.
+
 Articles in Wikipedia are manually editted by various authors.
-Wikipedia provides many templates to guide authors composing their context in a regular way.
+Wikipedia provides many templates to guide authors composing their context in a standard way.
 For example, \textcolor{red}{China use template XXX}.
 Moreover, an infobox in one article also follows an infobox template, which maintains a property set of similar articles and display labels on website page.
+
 \subsubsection{Other Chinese Encyclopedias}
 There are several large-scale monolingual Chinese Encyclopedias currently.
-Among those, Baidu Baike and Hudong are the most well-known.
-Hudong was founded in 2005 and contains more than 12 millions articles with about 9 millions experts' contribution util 2015, April.
+Among those, Baidu Baike and Hudong Baike are the most well-known.
+Hudong Baike was founded in 2005 and contains more than 12 millions articles with about 9 millions experts' contribution util 2015.
 At the mean time, Baidu Baike maintains more than 11 millions articles.
-These two resource are similar in article structure, somethimes even in content.
+These two resources are similar in article structure, somethimes even in content.
+
 \subsubsection{Encyclopedia Page}
@@
 A taxonomy presents the relation between categories.
-Usually a category has its sub classes and super classes.
+Usually a category has its sub-categories and super-categories.
 Besides, an article belongs to one or more categories.
 Fig.
-\ref{fig:hudong-taxonomy} An article describes an topic with rich information created and modified by several verified editors.
-The content and relation of an article provide a lot when building a \textcolor{red}{global?} knowledge base.
+\ref{fig:hudong-taxonomy} An article describes an entity with rich information created and modified by several verified editors.
+The content and relation of an article provide a lot when building a cross-domain knowledge base.
 In general, there are five elements can be exploited:
@@
     \centering
-    %\subfigure[]{
     \begin{minipage}[t]{0.5\textwidth}
@@
         \caption{Taxonomy in Hudong.}
-    %}
     \end{minipage}%
@@
 \begin{itemize}
-  \item Title: A Title is the label of topic. Every article has a unique title, which can be used to distinguish each topic.
-  \item Abstract: An abstract is a brief summarize of the article topic. It's always the first paragraph of an article. Usually it can be taken as an important feature to a topic. 
+  \item Title: A Title is the label of entity, which is unique to an article so that it can be used to distinguish entities.
+  \item Abstract: An abstract is a brief summarize of the entity. It's always the first paragraph of an article. Usually it can be taken as an important feature due to the summary content. 
   \item Infobox: Most of articles contain infobox.
-An infobox maintains structured data which are in general subject-attribute-value triples formalized as a table.
-Information in this table includes important properties of the topic.
-  \item Links: Links are entries directing to other articles within the encyclopedia.
+An infobox maintains structured data which are frequently subject-attribute-value triples formalized as a table.
+Information in this table includes important properties of an entity.
+  \item Links: Links are entries to other articles within the encyclopedia.
 They lead readers to reference articles.
 Actually, they represent the relations between the current article and other articles.
-  \item Category: The categories that an article belongs to are usually listed below the article page, shown as tags. An article attaches to one or more categories.
+  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article attaches to one or more categories.
 \end{itemize}
 Fig. \ref{fig:baidu-article} shows a snap of an article in Baidu Baike. The five elements mentioned above are annotated.
+
 \subsection{Cross-lingual Links}
@@
 \subsection{Definitions}
+Here we list definitions involved in the later sections/
+
+Definition 1: A Encyclopedia is considered as a collection of articles, category system and links, which can be defined as a 3-tuple:
+
+\begin{equation}
+W = <A,C,L>
+\end{equation}
+
+where A denotes articles, C denotes categories, and L denotes links in W.
+
+We involve four encyclopedias, which are expressed as Wen, Wzh, Whd and Wbb.
+
+Definition 2: According to Section \ref {sec:}, there are several elements of an article. Therefore, each article a A can be defined as follow:
+\begin{equation}
+    a = <T(a),AB(a),L(a),I(a),C(a)>
+\end{equation}
+where T(a),AB(a),L(a),I(a),C(a) denotes title, abstract, links, infobox, category tag of article a.
+
+Definition 3:  An ontology...
+
+Definition 4: To an article a containing multi-language contents in Wikipedia, Le and Lz denotes its article tags, usually titles, in English and Chinese. Thus cl(a) = <Le(a), Lz(a)>
+
+Definition 5: An Infobox I(a) in article a contains a set of attribute-value pairs{<a,v>...}.
+In Wikipedia, an infobox is usually edited based on an appropriate infobox template recommended by Wikipedia, which we denote it as T(a).
 
 \section{Extraction}
-\label{sec:oe}
+\label{sec:extraction}
 In order to build a billinual knowledge base, we first set up an ontology to schema information from the four encyclopedia.
@@
 Those concepts comprise a taxonomy which presents a backbone of the ontology.
+
 In an encyclopedia, a category groups several articles and also has super-categories and sub-categories, just like concept doing. Therefore we can extract concepts based on existed category system. 
@@
 Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.
+
 We occur some chanllenges when extracting properties from infoboxes:
@@
 But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including Category List pages, Template documentations \textcolor{red}{and...}.
+
 Each instance contains relations with concepts and properties.
@@
 Besides, according to links placing in content, we gain the reference between the current instance to others, such as 华纳兄弟(Warner Bros.).
+
 After the preprocessing above, we harvest two types of information.
@@
 The other is relationships, containing concept-instance, instance-property-value and instance-instance.
+
 \subsection{Cross-lingual Links Extraction}
@@
 By extracting language links from Wikipedia, we can get an initial cross-lingual link set of concepts and instances.
+
 However, in property aspect, there is no obvious infobox links between English and its mapping Chinese article.
@@
 \ref{fig:template} shows a typical example of infobox template.
+
 \section{Cross-lingual Links Extension}
@@
 \subsection{Cross-lingual Linking}
-\label{sec:cld}
-combine four ontology into on
+\label{sec:cll}
+In order to make the ontology of one ency linked with others, we unify the same concept, instance and property from four source as unique one and indentify.
+For example, we merge instances by the following method:
+
+(1) Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
+
+(2) Give an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
+
+(3) The other instances existing in only one encyclopedia are considered as an independent instance.
+
+Up to now, we have combined all Chinese articles describing the same entity as one instance. Each entity may correspond to 1 to 3 sources.
+
+(4) To a Lzh(a), which is same as T(a), find whether there is an English cross-lingual link in CL<Le, Lz>. If exists, make the two as one instance and identify it using an ID.
+
+(5) If a Lzh or a Len has no matched cross-lingual link, number it with an independent ID.
+
+After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain monolingual.
+
+The process of unify concept and property is the same as instance. Meanwhile, all the relation in all sources are kept to prevent the loss of information. For example, in …
 
@@
 \label{sec:tp}
-Research of Wang Zhigang
+As a result of combining multi source information without verifying, the taxonomy of concept system is mussy.
+For example, \textcolor{red}{example}.
+Therefore, we introduce the method from\cite{wang2014cross} to filter the correct subClassOf and instanceOf relations between two entities.
+Table.
+\ref{tab:} shows some examples of correct relations.
+In particular, some language-dependent literal and language-independent structural features are defined to vector each concept or instance.
+The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities.
+The structural features include article divergence for subClassOf, property divergence for subClassOf, category divergence for subClassOf, article divergence for instanceOf, property divergence for instanceOf, category divergence for instanceOf.
+By employing these features, a binary-classification model is trained based on Logistic Regression.
+The whole process is iterative by add assured result into training set and retraining the model to get higher precision.
+Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also related with cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are right.
+Fig.
+\ref{fig:} shows an example of this process.
 
-\subsection{Taxonomy Prune}
+The ideal result of pruning is a tree, whose lines denote relations, nodes denote concepts and leaves denote instances.
+However, with wrong relations cut without caring about integrity, getting a forest is inevitable.
+We may lose some links but get more accurate relations instead.
+
+\subsection{Knowledge Base Building}
+To build a knowledge base, we first define specific URI to identify each element in the prepared dataset.
+URIs of concept, instance, and property are created by concatenating a namespace prefix and ID.
+Table \ref{tab:} lists the URI defined in the knowledge base.
 
@@
 \subsection{DataSet}
-The four encyclopedias and their statistics data
+四个百科的数据统计，包括我们有的百科数据的发布时间，格式（xml。html），article数量，抽取的instance数量，concept数量，property数量, wiki中跨语言链接数量
+其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
 \subsection{Extracted Knowledge Base}
-Xlore statistics data.
+xlore 的统计数据，包括instance数量，concept数量，property数量，有双语的instance、concept、property，只有中文的，只有英文的
+顶层分类以及下属concept和instance数量
+有最多instance的property(object property)，以及相应的instance数量
+有最多的text的property(datatype property)，以及数量
+删除的taxonomy关系（如果重做实验的话）
+
 \subsection{Query Interface}
-Xlore query interface
+各种我们自己定义的uri，比如abstract，reference。。。。
+各种查询语句示例
 
@@
 \label{sec:work}
+In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods are referred to.
+\subsection{Chinese Knowledge Bases}
+Currently, several large-scale Chinese knowledge bases have been generated.
+Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first large-scale Linking Open Data published.
+It acquires structural information from three original sources, Chinese Wikipedia, BaiduBaike and Hudong and gets more than 5 million distinct entities.
+Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
+Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike.
+It first learns an ontology based on category system and properties, and then collects 19542 concepts, 2381 properties, 802593 instances.
+Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g.
+microblog posts, news pages, images) to enrich the structured knowledge.
+\subsection{Cross-lingual Knowledge Bases}
+DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world.
+It's extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
+This knowledge base is widely applied in many domain, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
+Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
+It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods.
+The API is available to over 200 languages and more than 16 million words and names.
+UWN provides semantic relationship of list of word meanings for Aya's work on conceptual search \cite{al2015conceptual}
+
+\subsection{Cross-lingual Knowledge Linking}
+Discovering more cross-lingual links is benefit to development of a multilingual knowledge base.
+General method is divided into two steps.
+First find missing link candidates using link structure of articles and then decide whether candidates are cross links or not by classification.
+\cite{sorg2008enriching} employs such approach to resolve the problem of automatically inducing new cross-language links.
+Wang\cite{wang2012cross} utilize a linkage factor graph model
 
@@
 
-\section*{Acknowledgement}
-Thanks anonymous reviewers for their valuable suggestions that help us improve the quality of the paper.
+%\section*{Acknowledgement}
+%Thanks anonymous reviewers for their valuable suggestions that help us improve the quality of the paper.
 Thanks Prof.

### 2015-05-22 nlpcc/paper.tex
整理了一版，更接近初稿了

@@
 \usepackage{CJKutf8}
+\usepackage{url}
+\usepackage[ruled]{algorithm2e}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{enumerate}
 
@@
 
-To build a cross-lingual knowledge base, some problems are to be addressed:(1)The imbalanced size of different Wikipedia languages leads to less data of various languages.
-In Wikipeida, the number of articles in English has reached almost 5 millions, while in Chinese there are only 800 thousand.
+To build a cross-lingual knowledge base, some problems are to be addressed: (1) The imbalanced size of different Wikipedia languages leads to less data of various languages.
+In Wikipedia, the number of articles in English has reached almost 5 millions, while in Chinese there are only 800 thousand.
 The scarcity of resources makes structuring a large-scale cross-lingual knowledge base within Chinese and English difficult.
-(2)The number of existed cross-lingual links in Wikipedia is so small that affects the quality of a bilingual knowledge base.
-Especially there is no obvious links in properties.Statistically, only about XX thousand cross-lingual links are between English and Chinese articles.(3)The large but irrigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
+(2) The number of existed cross-lingual links in Wikipedia is so small that affects the quality of a bilingual knowledge base.
+Especially there is no obvious links in properties.Statistically, only about XX thousand cross-lingual links are between English and Chinese articles.
+(3) The large but irrigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
 For example,\textcolor{red}{example}
@@
 Besides, definitions are proposed in this section.
-Section \ref{sec:extraction} presents the extraction approach in concept, instance and property level.
-Method of initiating cross-lingual link set will also be mentioned.
-\iffalse Section \ref{sec:cle} propose an extension approach for discovering more cross-lingual relations.\fi Section \ref{sec:tp} describes how to prune the taxonomy.
+Section \ref{sec:dp} presents the extraction approach in concept, instance and property level.
+Section \ref{sec:clkbb} describes the procedure of bulding a knowledge base using extracting result.
 Section \ref{sec:result} shows the results of established knowledge base.
 Section \ref{sec:work} induces related work about this paper.
-Section \ref{sec:con} gives the conclusion and future work.
+Section \ref{sec:con} gives the conclusion.
 
@@
 \label{sec:pre}
-In this section, we firstly introduce the four encyclopedias used to build and enrich our knowledge base. Then we give some related definitions to formalize our precedure.
+In this section, we firstly introduce the four encyclopedias used to build and enrich our knowledge base. Then we give some related definitions to formalize our procedure.
 
@@
 Articles in Wikipedia are manually editted by various authors.
-Wikipedia provides many templates to guide authors composing their context in a standard way.
-For example, \textcolor{red}{China use template XXX}.
-Moreover, an infobox in one article also follows an infobox template, which maintains a property set of similar articles and display labels on website page.
+Wikipedia provides many templates to guide authors composing their context in a standard way, so do infoboxes.
+For example, The infobox in film 星际穿越(Interstellar) use the Template \emph{Infobox film}.
+Infobox template maintains a property set of similar articles and display labels on webpage.
 
@@
 \subsubsection{Encyclopedia Page}
+\label{sec:ep}
 All these four encyclopedias have two important elements, articles and category taxonomy.
@@
 Usually a category has its sub-categories and super-categories.
+Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy.
 Besides, an article belongs to one or more categories.
-Fig.
-\ref{fig:hudong-taxonomy} An article describes an entity with rich information created and modified by several verified editors.
+An article describes an entity with rich information created and modified by several verified editors.
 The content and relation of an article provide a lot when building a cross-domain knowledge base.
@@
     \centering
-    \begin{minipage}[t]{0.5\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy}}
+    \begin{minipage}[t]{0.8\textwidth}
+        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
         \label{fig:hudong-taxonomy}
-        \caption{Taxonomy in Hudong.}
-    \end{minipage}%
-    \begin{minipage}[t]{0.5\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/baidu-article}}
-        \label{fig:baidu-article}
-        \caption{A snap of an article in Baidu Baike}
+        \caption{Taxonomy in Hudong}
     \end{minipage}%
@@
 \end{itemize}
-Fig. \ref{fig:baidu-article} shows a snap of an article in Baidu Baike. The five elements mentioned above are annotated.
+Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia. 
+\begin{figure}[ht]
+    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
+    \label{fig:interstellar}
+    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
+\end{figure}%
 
 \subsection{Cross-lingual Links}
-In order to build a bilingual knowledge base, we need the relation between Chinese source and English source, which helps merge different language information into their unique and common topic.
-In Wikipedia, most articles have language links which guide the reader to the article in specific language under the same topic.
+In order to build a cross-lingual knowledge base, we need the relation between Chinese source and English source, which helps merge different language information into their common entities.
+In Wikipedia, most articles have language links which guide the reader to the article in specific language under the same entity.
 Fig.
-\ref{fig:lang-link} shows an example of language links in Wikipedia.
-Taking advantage of such existed links in Wikipedia, we can generate an initial bilingual ontology based on Chinese and English Wikipedia.
-However, the result is just an ontology based on Wikipedia, like DBpedia.
-To combine Hudong and Baidu Baike ,which are lack of cross-lingual information but more Chinese source, we employ the approach from \cite{} to discover bilingual links between English Wikipedia and Hudong in Section \ref{sec:cld}
+\ref{fig:interstellar}shows language links of \emph{Interstellar} is on the right of Wikipedia page.
+Taking advantage of human established language links, we can generate an initial cross-lingual ontology based on Chinese and English Wikipedia, similar to DBpedia.
+Afterwards, to combine Hudong Baike and Baidu Baike, which are lack of cross-lingual information but rich in Chinese data, we employ the approach proposed in \cite{wang2012cross} to discover cross-lingual links between English Wikipedia and Baidu Baike.
 
 \subsection{Definitions}
-Here we list definitions involved in the later sections/
+\label{sec:definition}
+Here we list definitions involved in the later sections:
 
-Definition 1: A Encyclopedia is considered as a collection of articles, category system and links, which can be defined as a 3-tuple:
+\textbf{Definition 1:} A Encyclopedia is considered as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.
 
+\textbf{Definition 2:} According to Section \ref{sec:ep}, there are several elements of an article. Therefore, each article $a$ can be defined as follow:
 \begin{equation}
-W = <A,C,L>
+    a = <Ti(a),AB(a),Li(a),I(a),C(a)>
 \end{equation}
+where $Ti(a),AB(a),Li(a),I(a),C(a)$ denotes title, abstract, links, infobox, category tag of article a.
 
-where A denotes articles, C denotes categories, and L denotes links in W.
+\textbf{Definition 3:} To an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article tags, usually titles, in English and Chinese.
+Thus $cl(a) = <L_{e}(a), L_{z}(a)>$
 
-We involve four encyclopedias, which are expressed as Wen, Wzh, Whd and Wbb.
+\textbf{Definition 4:} An Infobox $I(a)$ in an article contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
+In Wikipedia, an infobox is usually edited based on an appropriate infobox template recommended by Wikipedia, which here we denote as $T(a)$.
+Templates specify certain attributes, which are usually different from those displayed on the web page.
+Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value.
 
-Definition 2: According to Section \ref {sec:}, there are several elements of an article. Therefore, each article a A can be defined as follow:
-\begin{equation}
-    a = <T(a),AB(a),L(a),I(a),C(a)>
-\end{equation}
-where T(a),AB(a),L(a),I(a),C(a) denotes title, abstract, links, infobox, category tag of article a.
+\section{Procedure Overview}
+Fig. \ref{fig:procedure} presents the whole procedure of our knowledge base building. 
+\begin{figure}[ht]
+    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
+    \label{fig:procedure}
+    \caption{Procedure of building our cross-lingual knowledge base}
+\end{figure}%
+We extract information from four source, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
+Because the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be applied.
+After file parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source.
+Meanwhile, an initial Chinese-English lan-link set is generated, which is then employed a link-discovery method to become a larger set.
+Using the extended language links, we combine the four datasets into one.
+At last, going through the step of taxonomy pruning and data-cleaning, we get a final knowledge base which higher accuracy.
 
-Definition 3:  An ontology...
+\section{Data Preprocessing}
+\label{sec:dp}
+We prepare data for the knowledge base by a series of preprocessing operations.
+During this stage, our goal is to get a structured dataset includes concepts, which are extracted from category taxonomy; instances, which are defined according to articles and properties, which are based on infobox and also templates assistant.
+We will describe the extraction approach in detail.
 
-Definition 4: To an article a containing multi-language contents in Wikipedia, Le and Lz denotes its article tags, usually titles, in English and Chinese. Thus cl(a) = <Le(a), Lz(a)>
-
-Definition 5: An Infobox I(a) in article a contains a set of attribute-value pairs{<a,v>...}.
-In Wikipedia, an infobox is usually edited based on an appropriate infobox template recommended by Wikipedia, which we denote it as T(a).
-
-\section{Extraction}
-\label{sec:extraction}
-In order to build a billinual knowledge base, we first set up an ontology to schema information from the four encyclopedia.
-The ontology includes concepts, which are extracted from category taxonomy, instances, which are defined according to articles and properties, which are based on infobox and also templates assistant.
-We will describe our building approach as follow.
 \subsection{Concept Extraction}
 \label{sec:ce}
-A concept in ontology is defined as a type of similar instances.
-For example, the concept of instance \emph{Tsinghua University} is \emph{University} or \emph{Organization}.
+A concept is defined as a type of similar instances.
+For example, the concept of instance \emph{Interstellar} is \emph{Movie}.
 In general, a concept has super classes and sub classes, which means it has \emph{subClassOf} relation with other classes.
-Those concepts comprise a taxonomy which presents a backbone of the ontology.
+Concepts comprise a taxonomy which presents a backbone of an ontology.
 
-In an encyclopedia, a category groups several articles and also has super-categories and sub-categories, just like concept doing. Therefore we can extract concepts based on existed category system. 
+In an encyclopedia, a category groups several articles and also has super-categories and sub-categories, just like concept does. Therefore we can extract concepts based on existing category system.
+
 However, the whole taxonomy can not directly transform from category system because of the following problems:
 \begin{itemize}
-    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages that are typical of Wikipedia.
-For example, \textcolor{red}{list of ...
-or tempalte:infobox}
+    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
     \item Some sub-category links in the category system maybe inconsistent.
@@
 As Fig.
-\ref{fig:category-mistakes} shows: In Hudong, the sub-categories of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree.
+\ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree.
 Meanwhile, in Wikipedia, \textcolor{red}{例子}
     \item Some categories relate to only one or two articles.
-According to the definition of concept, such categories are less representive to a group of instance, therefore it's unwise to retain it as concept.
+According to the definition of concept, such categories are less representive to a group of instances, therefore it's unwise to retain it as concept.
 \end{itemize}
-   To retrieve a cleaner and preciser concept taxonomy, we firstly do some refine works as follow:
+   To receive a cleaner and preciser concept taxonomy, we firstly do some refining works as follow:
 \begin{itemize}
-    \item Delete specific categories in Wikipedia.
+    \item Delete list categories or template categories in Wikipedia.
     \item Delete inconsistent sub-categories and keep the super one.
@@
 \end{itemize}
-The cleaning works are carried out in all encyclopedias for rule consistency when extracting.
+The cleaning works are carried out in all encyclopedias are consistency when extracting.
 The remaining categories comprise an original concept taxonomy.
 A category and its sub-categories are correlated by the relation \emph{SubClassOf}, and a category and its articles are correlated by the relation \emph{InstanceOf}.
-However, there are still inaccurate samples in the two relations.
-For example, \textcolor{red}{example}.
-We will prune the taxonomy later.
+However, there are still incorrect samples in the two relations.
+For example, \emph{Tsinghua University} is not an entity of \emph{Haidian District}, but relates to.
+Thus we will prune the taxonomy later.
 
@@
 \label{sec:pe}
-A property is defined as an attribute of instance.
+A property is defined as an attribute of entity.
 It represents the relation between two instances or an instance and its value.
-We divided properties into two types: datatype properties, which \textcolor{red}{...}; object properties, which \textcolor{red}{...}.
+We divided properties into two types: object property, whose value is an individual, such as \emph{directed by}; datatype property, whose value is a text literal, such as \emph{birth date}.
 Considering both content and infobox of an article, we extract two groups of properties, general-properties and Infobox-properties.
@@
 \subsubsection{General-properties}
-Characteristics of an instance are seen as general-properties, including label, abstract, and url.
-Those properties describe specific information of an instance.
-The label property identifies a unique instance, whose value is article title.
-The abstract property provides a brief description of an instance, whose value is the first paragraph of article.
-The url property saves the resource of an instance, which is actually a url in Wikipedia or Hudong or Baidu Baike.
+Characteristics of an entity are seen as general-properties, including label, abstract, and url.
+Those properties describe specific information of an entity.
+The label property identifies a unique entity, whose value is article title.
+The abstract property provides a brief description of an entity, whose value is the first paragraph of article.
+The url property saves the resource of an entity, which is actually a url in each source.
 All of them are datetype properies.
+
 \subsubsection{Infobox-properties}
-Attributes acquired from infobox data are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
-All attributes are relating with a typical value in the infobox, the value maybe a text or a reference, usually a url links to anothor instance.
+Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
+All attributes relate with a typical value in the infobox.
+The value maybe a text or a reference to anothor entity.
 The type of a property, datatype or object, depends on the value.
-Ordinarily, a plain text value marks the property as datetype while an instance reference determines the property as object.
+Ordinarily, a plain text value marks the property as datetype while an entity reference determines the property as object.
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
@@
 \begin{itemize}
-    \item There are some 
-    \item 
-    \item 
+    \item The attribute label displayed in webpage infobox is inconsistent with it in dump file of Wikipedia.
+Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox.
+The left is infobox while the other is a snap from dump file in Wikipedia.
+This movie's infobox follows template \emph{Infobox film}, where dump labels come from.
+Obviously the two labels are similar but not the same.
+As the property labels from Hudong Baike and Baidu Baike are equal to text displayed on the webpage, we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
+    \begin{figure}[ht]
+        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
+        \label{fig:infobox-template}
+        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
+    \end{figure}%
+    \item There are special characters in labels.
+For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
+Population property have sub-properties of "Density" and "Urban".
+In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
 \end{itemize}
+
+To solve the problems above, we take advantage of template information.
+Specifically, Wikipedia institutes rules of rendering label in templates.
+Fig.\ref{fig:infobox-render-rule} shows part of rules in \emph{template:infobox film}.
+When a dump label in triple-bracket occurs in a dump page, we can replace it by its mapping display label.
+After collecting all the display labels, we make a filter to redress the label text.
 
@@
 Therefore we can extract article content as an instance.
-But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including Category List pages, Template documentations \textcolor{red}{and...}.
+But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including category List pages and template documentations.
 
 Each instance contains relations with concepts and properties.
-Take the movie 星际穿越(Interstellar) as an example in Fig.\ref{fig:interstellar}.
-concepts are assigned according to the category tags below the article page.
+Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page.
 美国科幻片(American science fiction films) is a concept to Interstellar.
@@
 
-\subsection{Cross-lingual Links Extraction}
-\label{sec:cld}
-Wikipedia has \textcolor{red}{number} cross-lingual links between articles of English and Chinese.
-By extracting language links from Wikipedia, we can get an initial cross-lingual link set of concepts and instances.
-
-However, in property aspect, there is no obvious infobox links between English and its mapping Chinese article.
-According to the edit mechanism of Wikipedia, we use infobox template to get display label and cross-lingual links of an infobox-property.
-Fig.
-\ref{fig:template} shows a typical example of infobox template.
-
-\section{Cross-lingual Links Extension}
-\label{sec:cle}
-Research of Wang ZhiChun
-
-After the extracting preprocessing, we acquire a series of semi-structured data, including concept information, property pairs, instance information, relations among the three and cross-lingual links.
-Holding these raw data in hand, we then build an ontology schema for the futher knowledge base.
-
 \section{Cross-lingual Knowledge Base Building}
-To construct an cross-lingual ontology schema with existing semi-structured data, firstly we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing.
-Secondly, we prune the taxonomy which generates from concept relationships to retain a more accurate one.
+\label{sec:clkbb}
+To construct a cross-lingual knowledge base with existing structured data, firstly we gathor cross-lingual links which can help match the same entity in two languages and extend the link set.
+Secondly, we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing.
+Thirdly, we prune the taxonomy which generates from concept relationships to retain a more accurate one.
 At last, we hung instances and properties on to taxonomy to create a complete knowledge base.
 
+\subsection{Cross-lingual Links}
+Wikipedia has \textcolor{red}{number} cross-lingual links between English and Chinese.
+By extracting language links from Wikipedia, we can get an initial cross-lingual link set of concepts and instances.
+Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
+With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\%.
+
+However, due to following templates, Infobox-properties have no obvious cross-lingual links.
+To aquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
+(3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+The whole process can be summarized as Algorithm \ref{alg:ple}.
+Some of the symbols have already denoted in \ref{sed:definition}
 \subsection{Cross-lingual Linking}
-\label{sec:cll}
-In order to make the ontology of one ency linked with others, we unify the same concept, instance and property from four source as unique one and indentify.
+In order to make the ontology of one encyclopedia link to others, we unify the same concept, instance and property from four source to unique one and make identifier.
 For example, we merge instances by the following method:
 
-(1) Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
-
-(2) Give an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
-
-(3) The other instances existing in only one encyclopedia are considered as an independent instance.
-
-Up to now, we have combined all Chinese articles describing the same entity as one instance. Each entity may correspond to 1 to 3 sources.
-
-(4) To a Lzh(a), which is same as T(a), find whether there is an English cross-lingual link in CL<Le, Lz>. If exists, make the two as one instance and identify it using an ID.
-
-(5) If a Lzh or a Len has no matched cross-lingual link, number it with an independent ID.
+\begin{enumerate}[1)]
+    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title. 
+    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
+    \item The other instances existing in only one encyclopedia are considered as an independent instance.
+Up to now, we have combined all Chinese articles describing the same entity as one instance.
+Each instance may correspond to 1 to 3 sources.
+    \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
+    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an independent ID.
+\end{enumerate}
 
@@
 
-The process of unify concept and property is the same as instance. Meanwhile, all the relation in all sources are kept to prevent the loss of information. For example, in …
+The process of unify concept and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
 
@@
 Fig.
-\ref{fig:} shows an example of this process.
+\ref{fig:} shows an example of the process.
 
@@
 URIs of concept, instance, and property are created by concatenating a namespace prefix and ID.
-Table \ref{tab:} lists the URI defined in the knowledge base.
+Table \ref{tab:uris} lists the URI defined in the knowledge base.
+\begin{table}[h]
+\small
+\centering
+\caption{URIs for concept, instance, property in our knowledge base}
+\label{tab:uris}
+    \begin{tabular}{|c|c|}
+        \hline
+        Type     & URI                          \\ \hline
+        Concept  & http://xlore.org/concept/id  \\ \hline
+        Instance & http://xlore.org/instance/id \\ \hline
+        Property & http://xlore.org/property/id \\ \hline
+    \end{tabular}
+\end{table}
 
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion}
 \label{sec:con}
@@
 
+\begin{algorithm}[t]
+    \KwIn{ English Infobox template set $TS_{e}$, Chinese Infobox template set $TS_{z}$, English article set $AS_{e}$, Chinese article set $AS_{z}$, existing lan-link map $CL<L_{e}, L_{z}>$ }
+\KwOut{Property lan-link map $CL_{p}$}
+
+Initialization: $CL_{p} = \{\} $\\
+\ForEach {English Template $T_{e} \in TS_{e}$}{
+    $L_{e}$ = label of $T{e}$ \\
+    \eIf {$L_{e} \in CL$}{
+        $L_{z} = CL\left[L_{e}\right] $ ,\ $T_{z} = TS_{z}\left[L_{z}\right]$\\
+        \ForEach{$tl \in T_{e}.pset.tlset \cap T_{z}.pset.tlset $}{
+            $CL_{p}$.add(<$T_{e}.p[tl].dl$, $T_{z}.p[tl].dl$>)
+        }
+    }
+}
+
+\ForEach {English Article $A_{e}$ \in $AS_{e}$}{
+    $L_{e}$ = label of $A_{e}$ 
+    \eIf {$L_{e} \in CL$}{
+        $L_{z} = CL\left[L_{e}\right]$ ,\ $A_{z} = AS_{z}\left[L_{z}\right]$ \\
+
+        $T_{e}$ = Template of $A_{e}$.I ,\ $T_{z}$ = Template of $A_{z}$.I \\
+
+        Set $Cset$ as the Common set of template labels of $T_{e}$ and template labels of $T_{z}$ \\
+        $Cset = T_{e}.pset.tlset \cap T_{z}.pset.tlset $ \\
+
+        \ForEach {template label $tl \in Cset $}{
+            $CL_{p}$.add(<$T_{e}.pset[tl].dl$, $T_{z}.pset[tl].dl$>)
+        }
+
+        \ForEach{English template label $tl_{e} \in T_{e}.pset.tlset \minus Cset$}{
+            $p_{e} = T_{e}.pset\left[tl_{e}\right]$ \\
+            \ForEach{Chinese template label $tl_{z} \in T_{z}.pset.tlset - Cset$}{
+                $p_{z} = T_{z}.pset\left[tl_{z}\right]$ \\
+                \eIf {$p_{e}.type$ is datatype $\&\&$ $p_{z}.type$ is datatype}{
+                    \eIf {CalculateSimilar($p_{e}.v$, $p_{z}.v$) > $threshold$}{
+                        $CL_{p}$.add(<$p_{e}.dl$, $p_{z}.dl$>)
+                    }
+                } \eElseIf {$p_{e}.type$ is object $\&\&$ $p_{z}.type$ is object}{
+                    \eIf{ReferToCommmonEntity($p_{e}.v$, $p_{z}.v$)}{
+                        $CL_{p}$.add(<$p_{e}.dl$, $p_{z}.dl$>)
+                    }
+                }
+            }
+        }
+    }
+}
+\caption{Property Links Extraction}
+\label{alg:ple}
+\end{algorithm}
+
 \end{document}

### 2015-05-22 nlpcc/paper.tex
add result from sy

@@
 \subsection{Extracted Knowledge Base}
-xlore 的统计数据，包括instance数量，concept数量，property数量，有双语的instance、concept、property，只有中文的，只有英文的
-顶层分类以及下属concept和instance数量
-有最多instance的property(object property)，以及相应的instance数量
-有最多的text的property(datatype property)，以及数量
-删除的taxonomy关系（如果重做实验的话）
+We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu.
+Each of the wikis has three types of information, which can be utilized for building our ontology, namely, specific articles, classification system, and attribute of articles.
+We extract each raw data, then form the extracted information into well-structured data.
+Table\ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.
+
+\begin{table}[h]
+\small
+\centering
+\caption{Statistics of elementary extraction result}
+\label{tab:extract-result}
+    \begin{tabular}{|l|l|l|l|l|}
+        \hline
+                 & Enwiki  & Zhwiki & Hudong  & Baidu   \\ \hline
+        Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
+        Concept  & 982432  & 159705 & 31802   & 1300    \\ \hline
+        Property & 43976   & 18842  & 1187    & 139634  \\ \hline
+    \end{tabular}
+\end{table}
+
+After fusing the heterogeneous resources, we harvest a cross-lingual graph with 1,093,855 classes, 200,223 properties, and 11,721,238 instances separately.
+With different methods of extraction and language linking discovery, these three kinds of entries show different results in languages.
+We give a breakdown of both Chinese knowledge and English knowledge in Table\ref{tab:kb-result}.
+
+\begin{table}[h]
+\small
+\centering
+\caption{Statistics of our knowledge base}
+\label{tab:kb-result}
+    \begin{tabular}{|l|l|l|l|}
+        \hline
+                        & Concepts  & Instance   & Property \\ \hline
+        English         & 982,982   & 4,311,719  & 54,802   \\ \hline
+        English\%       & 89.86\%   & 37.79\%    & 27.37\%  \\ \hline
+        Chinese         & 176,648   & 7,842,117  & 167,083  \\ \hline
+        Chinese\%       & 16.15\%   & 66.9\%     & 83.45\%  \\ \hline
+        Cross-lingual   & 65,775    & 432,598    & 21,662   \\ \hline
+        Cross-lingual\% & 6.01\%    & 3.7\%      & 10.82\%  \\ \hline
+        Only English    & 917,207   &            & 33140    \\ \hline
+        Only English\%  & 83.9\%    &            & 16.6\%   \\ \hline
+        Only Chinese    & 110,873   &            & 145,421  \\ \hline
+        Only Chinese\%  & 10.1\%    &            & 72.6\%   \\ \hline
+        Sum             & 1,093,855 & 11,721,238 & 200,223  \\ \hline
+    \end{tabular}
+\end{table}
+
+Our knowledge graph is organized in Openlink Virtuoso, which is a data management platform covering various server, including triple store.
 
 \subsection{Query Interface}
-各种我们自己定义的uri，比如abstract，reference。。。。
-各种查询语句示例
+We provide a website to demonstrate our knowledge in the forms of class, instance and property.
+The users of our system can choose language preference which is convenient for both English speaker and Chinese speaker.
+In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.
+ In the instance webpage we display bilingual label, super classes, related classes, abstract, property key value pairs, images and references.
+In the property webpage, we presents bilingual label, domains, ranges, and related instances of each property.
+Beside these user-friendly pages, we as well provide SPARQL interface for professional users to query our knowledge graph.
+Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.
 

### 2015-05-22 nlpcc/paper.tex
first version to zigo

@@
 \usepackage{graphicx}
-%\usepackage{multirow}
 \usepackage{url}
@@
 
-\keywords{Knowledge Base, Semantic Web, Linked Data, Ontology, Cross-lingual}
+\keywords{Knowledge Base, Semantic Web, Ontology, Cross-lingual}
 \end{abstract}
@@
 \section{Introduction}
-With LOD growing recent years, more and more knowledge bases are generated in different languages and in various domains.
-Several large-scale knowledge bases, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are well-known and often used for information extraction \cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and so on.
+With LOD growing recent years, more and more knowledge bases are generated for information sharing.
+Several large-scale knowledge bases, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are well-known and often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and so on.
 These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.
 
-Take DBpedia as an example, it extracts structural information from Wikipedia, the largest knowledge sharing resource in the world and have already contained approximately 38.3 million things.
-Right now DBpedia provides 124 versions of non-English language including German, French and Japanese etc.
-Moreover, there are instances and 11 classes in Chinese.
+Take DBpedia as an example.
+It extracts structured information from Wikipedia, and has already contained approximately 38.3 million things.
+Right now DBpedia provides 124 versions of non-English language including Chinese.
+There are XXX instances and 11 classes in Chinese.
 Obviously, the quality of Chinese information is not enough for further research or application.
-Neither do the other knowledge bases containing Chinese version.
 
-To build a cross-lingual knowledge base, some problems are to be addressed: (1) The imbalanced size of different Wikipedia languages leads to less data of various languages.
-In Wikipedia, the number of articles in English has reached almost 5 millions, while in Chinese there are only 800 thousand.
-The scarcity of resources makes structuring a large-scale cross-lingual knowledge base within Chinese and English difficult.
-(2) The number of existed cross-lingual links in Wikipedia is so small that affects the quality of a bilingual knowledge base.
-Especially there is no obvious links in properties.Statistically, only about XX thousand cross-lingual links are between English and Chinese articles.
-(3) The large but irrigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
+A cross-lingual knowledge base has benefit efforts on global knowledge sharing, understanding and expanding.
+However, to build an available knowledge base, some problems are to be addressed: (1) The imbalanced size of different language sources leads to less entities.
+Comparing the number of articles in English Wikipedia and that in Chinese Wikipedia, which are 5 million and 800 thousand, it's obvious that to structure a knowledge base with Chinese is more difficult.
+(2) The number of existing cross-lingual links in Wikipedia is so small, which affects the quality of a bilingual knowledge base.
+Especially there is no evident links in properties.
+Statistically, only XX thousand cross-lingual links are there between English and Chinese articles.
+(3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
 For example,\textcolor{red}{example}
@@
 
-%Thus it’s significative to build a Chinese-English knowledge base and benefit from it.
+%Thus it’s significant to build a Chinese-English knowledge base and benefit from it.
 
-Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong and Baidu Baike.
-To solve the unbalance problem, we utilize such seperated resources to enrich our Chinese information.
+Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike.
+To solve the unbalance problem, we utilize such separated sources to enrich our Chinese information.
 In this paper, we propose an approach to combine four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
@@
 \begin{itemize}
-  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining four encyclopedias, which are English Wikipedia, Chinese Wikipedia, Baidu and Hudong.
-The latter three contain large amount of Chinese knowledge, which helps balance and enrich information of two languages.
-  %\item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and by analysing templates in Wikipedia for property.
+  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedias.
+Among them, two  Chinese encyclopedias are utilized to helps balance and enrich information of two languages.
+  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analysing templates in Wikipedia for property.
   \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relation in ontology.
@@
 Section \ref{sec:dp} presents the extraction approach in concept, instance and property level.
-Section \ref{sec:clkbb} describes the procedure of bulding a knowledge base using extracting result.
+Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracting result.
 Section \ref{sec:result} shows the results of established knowledge base.
@@
 Such imbalance makes those ontologies based on Wikipedia-only behave badly in cross-lingual aspect.
-For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that helps little when other poeple want to do cross-lingual research depending on DBpedia.
+For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that helps little when other people want to do cross-lingual research depending on DBpedia.
 To avoid the imbalance problem, two other Chinese encyclopedias are utilized to extend Chinese source.
 
-Articles in Wikipedia are manually editted by various authors.
+Articles in Wikipedia are manually edited by various authors.
 Wikipedia provides many templates to guide authors composing their context in a standard way, so do infoboxes.
@@
 Among those, Baidu Baike and Hudong Baike are the most well-known.
-Hudong Baike was founded in 2005 and contains more than 12 millions articles with about 9 millions experts' contribution util 2015.
+Hudong Baike was founded in 2005 and contains more than 12 millions articles with about 9 millions experts' contribution until 2015.
 At the mean time, Baidu Baike maintains more than 11 millions articles.
-These two resources are similar in article structure, somethimes even in content.
+These two resources are similar in article structure, sometimes even in content.
 
@@
 \end{equation}
-where $Ti(a),AB(a),Li(a),I(a),C(a)$ denotes title, abstract, links, infobox, category tag of article a.
+where $Ti(a),AB(a),Li(a),I(a),C(a)$ denotes title, abstract, links, infobox, category tag of article $a$.
 
@@
     \item Some categories relate to only one or two articles.
-According to the definition of concept, such categories are less representive to a group of instances, therefore it's unwise to retain it as concept.
+According to the definition of concept, such categories are less representative to a group of instances, therefore it's unwise to retain it as concept.
 \end{itemize}
@@
 The url property saves the resource of an entity, which is actually a url in each source.
-All of them are datetype properies.
+All of them are datatype properties.
 
@@
 All attributes relate with a typical value in the infobox.
-The value maybe a text or a reference to anothor entity.
+The value maybe a text or a reference to another entity.
 The type of a property, datatype or object, depends on the value.
-Ordinarily, a plain text value marks the property as datetype while an entity reference determines the property as object.
+Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object.
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
@@
 
-We occur some chanllenges when extracting properties from infoboxes:
+We occur some challenges when extracting properties from infoboxes:
 \begin{itemize}
@@
 \label{sec:clkbb}
-To construct a cross-lingual knowledge base with existing structured data, firstly we gathor cross-lingual links which can help match the same entity in two languages and extend the link set.
+To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
 Secondly, we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing.
@@
 However, due to following templates, Infobox-properties have no obvious cross-lingual links.
-To aquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
+To acquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
 (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
@@
 
-\subsection{Cross-lingual Knowledge Linking}
-Discovering more cross-lingual links is benefit to development of a multilingual knowledge base.
+%\subsection{Cross-lingual Knowledge Linking}
+%Discovering more cross-lingual links is benefit to development of a multilingual knowledge base.
 General method is divided into two steps.

### 2015-05-25 nlpcc/paper.tex
再次尝试提交

@@
 \section{Introduction}
-With LOD growing recent years, more and more knowledge bases are generated for information sharing.
-Several large-scale knowledge bases, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are well-known and often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and so on.
+With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing.
+Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and many other applications.
 These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.
 
-Take DBpedia as an example.
-It extracts structured information from Wikipedia, and has already contained approximately 38.3 million things.
-Right now DBpedia provides 124 versions of non-English language including Chinese.
-There are XXX instances and 11 classes in Chinese.
-Obviously, the quality of Chinese information is not enough for further research or application.
+Take DBpedia as an example, it extracts structured information from Wikipedia and has already contained approximately 38.3 million things.
+Now DBpedia provides 124 versions of non-English language including Chinese.
+However, there are only XXX instances and 11 classes in Chinese.
+Obviously, the quality of Chinese information is insufficient for further research and application.
 
-A cross-lingual knowledge base has benefit efforts on global knowledge sharing, understanding and expanding.
-However, to build an available knowledge base, some problems are to be addressed: (1) The imbalanced size of different language sources leads to less entities.
-Comparing the number of articles in English Wikipedia and that in Chinese Wikipedia, which are 5 million and 800 thousand, it's obvious that to structure a knowledge base with Chinese is more difficult.
-(2) The number of existing cross-lingual links in Wikipedia is so small, which affects the quality of a bilingual knowledge base.
+A cross-lingual knowledge base has positive effect on global knowledge sharing, understanding and expanding.
+However, to build an available knowledge base, some problems must be addressed: (1) The imbalanced size of different language sources leads to less entities.
+Comparing the number of articles in English Wikipedia and those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
+(2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which affects the quality of a bilingual knowledge base.
 Especially there is no evident links in properties.
-Statistically, only XX thousand cross-lingual links are there between English and Chinese articles.
+Statistically, only XX thousand cross-lingual links can be found between English and Chinese articles.
 (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
@@
 Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike.
-To solve the unbalance problem, we utilize such separated sources to enrich our Chinese information.
+To solve the imbalance problem, we utilize such separated sources to enrich our Chinese information.
 In this paper, we propose an approach to combine four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.

### 2015-05-26 nlpcc/paper.tex
add conclusion

@@
 
-Take DBpedia as an example, it extracts structured information from Wikipedia and has already contained approximately 38.3 million things.
+ The nucleus of LOD DBpedia extracts structured information from Wikipedia and has already contained approximately 38.3 million things.
 Now DBpedia provides 124 versions of non-English language including Chinese.
 However, there are only XXX instances and 11 classes in Chinese.
-Obviously, the quality of Chinese information is insufficient for further research and application.
+Compared with the 4.58 million things in English, the quality of Chinese information is obviously insufficient for further research and application.
 
-A cross-lingual knowledge base has positive effect on global knowledge sharing, understanding and expanding.
+A cross-lingual knowledge base can effectively promote global knowledge sharing, understanding and expanding.
 However, to build an available knowledge base, some problems must be addressed: (1) The imbalanced size of different language sources leads to less entities.
-Comparing the number of articles in English Wikipedia and those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
-(2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which affects the quality of a bilingual knowledge base.
-Especially there is no evident links in properties.
+Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
+(2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which effects the quality of a bilingual knowledge base.
+Especially when there scarcely exists evident links in properties.
 Statistically, only XX thousand cross-lingual links can be found between English and Chinese articles.
@@
 To solve the imbalance problem, we utilize such separated sources to enrich our Chinese information.
-In this paper, we propose an approach to combine four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
-To get a more available result, we also make judgement on the relation among concepts and instances.
-At last, a query interface is provided to access the knowledge base.
+In this paper, we propose an approach to integrate four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
+To get a more available result, we also make judgement on the relations among concepts and instances.
+At last, a SPARQL query interface is provided to access to the knowledge base.
 Specifically, our work makes the following contributions:
@@
   \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedias.
-Among them, two  Chinese encyclopedias are utilized to helps balance and enrich information of two languages.
-  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analysing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relation in ontology.
+Among them, two  Chinese encyclopedias are utilized to help balance and enrich information in two languages.
+  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analyzing templates in Wikipedia for property.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relations in ontology.
   \item A website is developed based on our ontology and also a SPARQL interface is provided for public query operations in our knowledge base.
@@
 Out of these, English articles contribute most.
-There are 4.8 million articles in English while only over 800thousand articles in Chinese.
+There are 4.8 million articles in English while only over 800 thousand articles in Chinese.
 It is obvious that the quantity of English articles is far more than Chinese.
 Such imbalance makes those ontologies based on Wikipedia-only behave badly in cross-lingual aspect.
-For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that helps little when other people want to do cross-lingual research depending on DBpedia.
-To avoid the imbalance problem, two other Chinese encyclopedias are utilized to extend Chinese source.
+For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that shows little help when trying to do cross-lingual research depending on DBpedia.
+To avoid this imbalance problem, two other Chinese encyclopedias are utilized to enrich Chinese source.
 
 Articles in Wikipedia are manually edited by various authors.
-Wikipedia provides many templates to guide authors composing their context in a standard way, so do infoboxes.
-For example, The infobox in film 星际穿越(Interstellar) use the Template \emph{Infobox film}.
-Infobox template maintains a property set of similar articles and display labels on webpage.
+To avoid distinct formats and styles, Wikipedia provides templates to format their editing content, especially infoboxes.
+For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of film articles.
 
@@
 There are several large-scale monolingual Chinese Encyclopedias currently.
-Among those, Baidu Baike and Hudong Baike are the most well-known.
-Hudong Baike was founded in 2005 and contains more than 12 millions articles with about 9 millions experts' contribution until 2015.
-At the mean time, Baidu Baike maintains more than 11 millions articles.
-These two resources are similar in article structure, sometimes even in content.
+Among those, Baidu Baike and Hudong Baike are the most content-rich.
+Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015.
+At the mean time, Baidu Baike maintains more than 11 million articles.
+These two resources are similar in article structure, even in content in some cases.
 
@@
 \label{sec:ep}
-All these four encyclopedias have two important elements, articles and category taxonomy.
-A taxonomy presents the relation between categories.
+All these four encyclopedias provide two important elements which contain potential semantic information, category taxonomy and articles.
+A taxonomy presents the relations between categories.
 Usually a category has its sub-categories and super-categories.
 Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy.
-Besides, an article belongs to one or more categories.
 An article describes an entity with rich information created and modified by several verified editors.
-The content and relation of an article provide a lot when building a cross-domain knowledge base.
-In general, there are five elements can be exploited:
+Besides, an article may belong to one or more categories.
+The article content as well as the relation between an article and its belonged categories both help enormously when constructing a knowledge base.
+In general, there are five elements can be exploited in each article page:
 \begin{figure}
@@
 \begin{itemize}
-  \item Title: A Title is the label of entity, which is unique to an article so that it can be used to distinguish entities.
+  \item Title: A Title is the label of an entity, which is unique to each article so that it can be used to distinguish entities.
   \item Abstract: An abstract is a brief summarize of the entity. It's always the first paragraph of an article. Usually it can be taken as an important feature due to the summary content.
@@
 \subsection{Cross-lingual Links}
-In order to build a cross-lingual knowledge base, we need the relation between Chinese source and English source, which helps merge different language information into their common entities.
-In Wikipedia, most articles have language links which guide the reader to the article in specific language under the same entity.
+In order to build a cross-lingual knowledge base, we need the mapping relation between Chinese sources and English sources, which can be used to fuze information in different language.
+In Wikipedia, some article pages have language links so that the reader can switch languages within the same article.
 Fig.
-\ref{fig:interstellar}shows language links of \emph{Interstellar} is on the right of Wikipedia page.
-Taking advantage of human established language links, we can generate an initial cross-lingual ontology based on Chinese and English Wikipedia, similar to DBpedia.
+\ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page.
+Taking advantage of manually established language links, we can generate an initial cross-lingual ontology based on Chinese and English Wikipedia, similar to DBpedia.
 Afterwards, to combine Hudong Baike and Baidu Baike, which are lack of cross-lingual information but rich in Chinese data, we employ the approach proposed in \cite{wang2012cross} to discover cross-lingual links between English Wikipedia and Baidu Baike.
@@
 \end{equation}
-where $Ti(a),AB(a),Li(a),I(a),C(a)$ denotes title, abstract, links, infobox, category tag of article $a$.
+where $Ti(a),AB(a),Li(a),I(a),C(a)$ denotes title, abstract, links, infobox, category tags of article $a$.
 
-\textbf{Definition 3:} To an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article tags, usually titles, in English and Chinese.
+\textbf{Definition 3:} As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article tags, usually titles, in English and Chinese separately.
 Thus $cl(a) = <L_{e}(a), L_{z}(a)>$
@@
 \end{figure}%
-We extract information from four source, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
-Because the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be applied.
-After file parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source.
-Meanwhile, an initial Chinese-English lan-link set is generated, which is then employed a link-discovery method to become a larger set.
+We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
+Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed.
+After data parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source.
+Meanwhile, an initial Chinese-English lan-link map is generated, which is then employed a link-discovery method to obtain a larger one.
 Using the extended language links, we combine the four datasets into one.
-At last, going through the step of taxonomy pruning and data-cleaning, we get a final knowledge base which higher accuracy.
+At last, going through the procedure of taxonomy pruning and data-cleaning, we get a final knowledge base with higher accuracy.
 
@@
 We prepare data for the knowledge base by a series of preprocessing operations.
-During this stage, our goal is to get a structured dataset includes concepts, which are extracted from category taxonomy; instances, which are defined according to articles and properties, which are based on infobox and also templates assistant.
-We will describe the extraction approach in detail.
+During this stage, our goal is to get a structured dataset including concepts, which are extracted from category taxonomy; instances, which are defined according to articles and properties based on both infobox and templates assistant.
+We will describe the extraction approach in detail below.
 
@@
 \end{itemize}
-   To receive a cleaner and preciser concept taxonomy, we firstly do some refining works as follow:
+   To receive a cleaner and more precise concept taxonomy, we firstly do some refining works as follow:
 \begin{itemize}
@@
 \end{itemize}
-The cleaning works are carried out in all encyclopedias are consistency when extracting.
+The cleaning work carried out in all encyclopedias are consistency when extracting.
 The remaining categories comprise an original concept taxonomy.
@@
 \label{sec:pe}
-A property is defined as an attribute of entity.
+A property is defined as an attribute of an entity.
 It represents the relation between two instances or an instance and its value.
-We divided properties into two types: object property, whose value is an individual, such as \emph{directed by}; datatype property, whose value is a text literal, such as \emph{birth date}.
-Considering both content and infobox of an article, we extract two groups of properties, general-properties and Infobox-properties.
+We divided properties into two types: object property, whose value is an individual, such as \emph{directed by}; datatype property, whose value is a literal text, such as \emph{birth date}.
+Considering both content and infobox of an article, we extract two kinds of properties, general-properties and Infobox-properties.
 
@@
 Those properties describe specific information of an entity.
-The label property identifies a unique entity, whose value is article title.
+The label property identifies a unique entity, whose value is the article title.
 The abstract property provides a brief description of an entity, whose value is the first paragraph of article.
-The url property saves the resource of an entity, which is actually a url in each source.
+The url property saves the source of an entity, which is actually a url in each source.
 All of them are datatype properties.
@@
 Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
-All attributes relate with a typical value in the infobox.
+Each attribute in the infobox is related to its own corresponding value.
 The value maybe a text or a reference to another entity.
-The type of a property, datatype or object, depends on the value.
-Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object.
+The type of a property, datatype or object, depends on the type of the value.
+Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype.
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
@@
 
-We occur some challenges when extracting properties from infoboxes:
+We are challenged when extracting properties from infoboxes:
 \begin{itemize}
-    \item The attribute label displayed in webpage infobox is inconsistent with it in dump file of Wikipedia.
+    \item The attribute label displayed in the webpage infobox is inconsistent with it in the published dump file of Wikipedia.
 Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox.
@@
 Obviously the two labels are similar but not the same.
-As the property labels from Hudong Baike and Baidu Baike are equal to text displayed on the webpage, we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
+As a result we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
+As to Chinese sources, the property labels from Hudong Baike and Baidu Baike are equal literally to texts displayed on the webpage, so we don't need extra process as we have in Wikipedia.
     \begin{figure}[ht]
@@
 For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
-Population property have sub-properties of "Density" and "Urban".
+For example, population property have sub-properties "-Density" and "-Urban".
 In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
@@
 In encyclopedia, an article describes an unique entity in the world.
-Therefore we can extract article content as an instance.
+Therefore we can extract an article content as an instance.
 But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including category List pages and template documentations.
@@
 Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page.
-美国科幻片(American science fiction films) is a concept to Interstellar.
-In the meantime, we obtain label property from article title, which is 星际穿越(Interstellar) and abstract property from the first paragraph.
-Infobox-properties are also acquired via extracting from infobox in the article.
-Besides, according to links placing in content, we gain the reference between the current instance to others, such as 华纳兄弟(Warner Bros.).
+美国科幻片(American science fiction films) is a concept of Interstellar.
+In the meantime, we obtain the label property from the article title, which is 星际穿越(Interstellar) and the abstract property from the first paragraph.
+The infobox-properties are also acquired via extracting from the infobox in the article.
+Besides, according to links in the content, we gain the reference between the current instance and others, such as 华纳兄弟(Warner Bros.).
 
@@
 One is the characteristics of instance, including instance-label, instance-abstract.
-The other is relationships, containing concept-instance, instance-property-value and instance-instance.
+The other includes relationships, containing concept-instance, instance-property-value and instance-instance.
 
@@
 To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing.
-Thirdly, we prune the taxonomy which generates from concept relationships to retain a more accurate one.
-At last, we hung instances and properties on to taxonomy to create a complete knowledge base.
+Secondly, we link this four encyclopedia, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
+Thirdly, we prune the taxonomy generated from concept relationships to retain a more accurate one.
+At last, we make instances and properties attached to the taxonomy to create a complete knowledge base.
 
@@
 However, due to following templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
+To acquire such links, we take the following steps: (1) Given a matched template, which has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, find the matched label mapping to the same dump label.
 (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
@@
 \subsection{Cross-lingual Linking}
-In order to make the ontology of one encyclopedia link to others, we unify the same concept, instance and property from four source to unique one and make identifier.
+In order to make all these encyclopedias linked to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
 For example, we merge instances by the following method:
@@
     \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
-    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
-    \item The other instances existing in only one encyclopedia are considered as an independent instance.
+    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
+    \item Other instances existing in only one encyclopedia are considered as independent instances.
 Up to now, we have combined all Chinese articles describing the same entity as one instance.
@@
     \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
-    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an independent ID.
+    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an new ID.
 \end{enumerate}
 
-After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain monolingual.
+After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain just monolingual information.
 
@@
 \label{sec:tp}
-As a result of combining multi source information without verifying, the taxonomy of concept system is mussy.
+As a result of combining multi-source information without verifying, the taxonomy of concept system is mussy.
 For example, \textcolor{red}{example}.
@@
 \ref{tab:} shows some examples of correct relations.
-In particular, some language-dependent literal and language-independent structural features are defined to vector each concept or instance.
+In particular, some language-dependent literal and language-independent structural features are defined to vectorize each concept or instance.
 The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities.
@@
 The whole process is iterative by add assured result into training set and retraining the model to get higher precision.
-Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also related with cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are right.
+Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
 Fig.
@@
 
-The ideal result of pruning is a tree, whose lines denote relations, nodes denote concepts and leaves denote instances.
-However, with wrong relations cut without caring about integrity, getting a forest is inevitable.
-We may lose some links but get more accurate relations instead.
+The ideal result of pruning is a tree, whose edges denote relations, nodes denote concepts and leaves denote instances.
+However, since get rid of incorrect entity relations without consideration of integrity, getting a forest result is inevitable.
+We may omit some links but get more accurate relations instead.
 
@@
 To build a knowledge base, we first define specific URI to identify each element in the prepared dataset.
-URIs of concept, instance, and property are created by concatenating a namespace prefix and ID.
+URIs of concept, instance, and property are created by concatenating a namespace prefix to an ID.
 Table \ref{tab:uris} lists the URI defined in the knowledge base.
@@
 We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu.
-Each of the wikis has three types of information, which can be utilized for building our ontology, namely, specific articles, classification system, and attribute of articles.
+Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles.
 We extract each raw data, then form the extracted information into well-structured data.
@@
 Currently, several large-scale Chinese knowledge bases have been generated.
-Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first large-scale Linking Open Data published.
-It acquires structural information from three original sources, Chinese Wikipedia, BaiduBaike and Hudong and gets more than 5 million distinct entities.
+Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first Chinese large-scale Linking Open Data published.
+It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities.
 Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
@@
 It's extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
-This knowledge base is widely applied in many domain, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
+This knowledge base is widely applied in many domains, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
 Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
@@
 \label{sec:con}
+This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources.
+At first, data preprocessing work is done to extract structured information and unify data format.
+Then a cross-lingual lan-link set is generated to help combine the bilingual sources.
+Besides, an extension method is applied to enrich the links.
+To refine our dataset, we also do pruning work on taxonomy.
+Finally, we acquire a knowledge base containing XXX concepts, XXX instances and XXX properties.
+Currently, a SPARQL query interface is provided to access the knowledge base.
 

### 2015-05-26 nlpcc/paper.tex
改了一半了，让我喘喘

@@
 Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
-Each attribute in the infobox is related to its own corresponding value.
+All attributes relate with a typical value in the infobox.
 The value maybe a text or a reference to another entity.
-The type of a property, datatype or object, depends on the type of the value.
-Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype.
+The type of a property, datatype or object, depends on the value.
+Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object.
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
@@
 
-We are challenged when extracting properties from infoboxes:
+We occur some challenges when extracting properties from infoboxes:
 \begin{itemize}
-    \item The attribute label displayed in the webpage infobox is inconsistent with it in the published dump file of Wikipedia.
+    \item The attribute label displayed in webpage infobox is inconsistent with it in dump file of Wikipedia.
 Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox.
@@
 Obviously the two labels are similar but not the same.
-As a result we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
-As to Chinese sources, the property labels from Hudong Baike and Baidu Baike are equal literally to texts displayed on the webpage, so we don't need extra process as we have in Wikipedia.
+As the property labels from Hudong Baike and Baidu Baike are equal to text displayed on the webpage, we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
     \begin{figure}[ht]
@@
 For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
-For example, population property have sub-properties "-Density" and "-Urban".
+Population property have sub-properties of "Density" and "Urban".
 In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
@@
 In encyclopedia, an article describes an unique entity in the world.
-Therefore we can extract an article content as an instance.
+Therefore we can extract article content as an instance.
 But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including category List pages and template documentations.
@@
 Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page.
-美国科幻片(American science fiction films) is a concept of Interstellar.
-In the meantime, we obtain the label property from the article title, which is 星际穿越(Interstellar) and the abstract property from the first paragraph.
-The infobox-properties are also acquired via extracting from the infobox in the article.
-Besides, according to links in the content, we gain the reference between the current instance and others, such as 华纳兄弟(Warner Bros.).
+美国科幻片(American science fiction films) is a concept to Interstellar.
+In the meantime, we obtain label property from article title, which is 星际穿越(Interstellar) and abstract property from the first paragraph.
+Infobox-properties are also acquired via extracting from infobox in the article.
+Besides, according to links placing in content, we gain the reference between the current instance to others, such as 华纳兄弟(Warner Bros.).
 
@@
 One is the characteristics of instance, including instance-label, instance-abstract.
-The other includes relationships, containing concept-instance, instance-property-value and instance-instance.
+The other is relationships, containing concept-instance, instance-property-value and instance-instance.
 
@@
 To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we link this four encyclopedia, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
-Thirdly, we prune the taxonomy generated from concept relationships to retain a more accurate one.
-At last, we make instances and properties attached to the taxonomy to create a complete knowledge base.
+Secondly, we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing.
+Thirdly, we prune the taxonomy which generates from concept relationships to retain a more accurate one.
+At last, we hung instances and properties on to taxonomy to create a complete knowledge base.
 
@@
 However, due to following templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we take the following steps: (1) Given a matched template, which has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, find the matched label mapping to the same dump label.
+To acquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
 (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
@@
 \subsection{Cross-lingual Linking}
-In order to make all these encyclopedias linked to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
+In order to make the ontology of one encyclopedia link to others, we unify the same concept, instance and property from four source to unique one and make identifier.
 For example, we merge instances by the following method:
@@
     \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
-    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
-    \item Other instances existing in only one encyclopedia are considered as independent instances.
+    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
+    \item The other instances existing in only one encyclopedia are considered as an independent instance.
 Up to now, we have combined all Chinese articles describing the same entity as one instance.
@@
     \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
-    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an new ID.
+    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an independent ID.
 \end{enumerate}
 
-After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain just monolingual information.
+After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain monolingual.
 
@@
 \label{sec:tp}
-As a result of combining multi-source information without verifying, the taxonomy of concept system is mussy.
+As a result of combining multi source information without verifying, the taxonomy of concept system is mussy.
 For example, \textcolor{red}{example}.
@@
 \ref{tab:} shows some examples of correct relations.
-In particular, some language-dependent literal and language-independent structural features are defined to vectorize each concept or instance.
+In particular, some language-dependent literal and language-independent structural features are defined to vector each concept or instance.
 The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities.
@@
 The whole process is iterative by add assured result into training set and retraining the model to get higher precision.
-Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
+Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also related with cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are right.
 Fig.
@@
 
-The ideal result of pruning is a tree, whose edges denote relations, nodes denote concepts and leaves denote instances.
-However, since get rid of incorrect entity relations without consideration of integrity, getting a forest result is inevitable.
-We may omit some links but get more accurate relations instead.
+The ideal result of pruning is a tree, whose lines denote relations, nodes denote concepts and leaves denote instances.
+However, with wrong relations cut without caring about integrity, getting a forest is inevitable.
+We may lose some links but get more accurate relations instead.
 
@@
 To build a knowledge base, we first define specific URI to identify each element in the prepared dataset.
-URIs of concept, instance, and property are created by concatenating a namespace prefix to an ID.
+URIs of concept, instance, and property are created by concatenating a namespace prefix and ID.
 Table \ref{tab:uris} lists the URI defined in the knowledge base.
@@
 We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu.
-Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles.
+Each of the wikis has three types of information, which can be utilized for building our ontology, namely, specific articles, classification system, and attribute of articles.
 We extract each raw data, then form the extracted information into well-structured data.
@@
 Currently, several large-scale Chinese knowledge bases have been generated.
-Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first Chinese large-scale Linking Open Data published.
-It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities.
+Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first large-scale Linking Open Data published.
+It acquires structural information from three original sources, Chinese Wikipedia, BaiduBaike and Hudong and gets more than 5 million distinct entities.
 Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
@@
 It's extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
-This knowledge base is widely applied in many domains, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
+This knowledge base is widely applied in many domain, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
 Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
@@
 \label{sec:con}
-This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources.
-At first, data preprocessing work is done to extract structured information and unify data format.
-Then a cross-lingual lan-link set is generated to help combine the bilingual sources.
-Besides, an extension method is applied to enrich the links.
-To refine our dataset, we also do pruning work on taxonomy.
-Finally, we acquire a knowledge base containing XXX concepts, XXX instances and XXX properties.
-Currently, a SPARQL query interface is provided to access the knowledge base.
 

### 2015-05-28 nlpcc/paper.tex
1

@@
 However, due to following templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
+To acquire such links, we take the following steps: (1) Given a matched template, which is a template having infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label.
 (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
@@
     \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
-    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
-    \item The other instances existing in only one encyclopedia are considered as an independent instance.
+    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
+    \item Other instances existing in only one encyclopedia are considered as an independent instance.
 Up to now, we have combined all Chinese articles describing the same entity as one instance.

### 2015-06-01 nlpcc/paper.tex
在大师兄的意见下改动的第一版

@@
 To get a more available result, we also make judgement on the relations among concepts and instances.
-At last, a SPARQL query interface is provided to access to the knowledge base.
+At last, a SPARQL endpoint is provided to access to the knowledge base.
 Specifically, our work makes the following contributions:
@@
   \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analyzing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relations in ontology.
-  \item A website is developed based on our ontology and also a SPARQL interface is provided for public query operations in our knowledge base.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise SubClassOf and InstanceOf relations in ontology.
+  \item Both website and SPARQL endpoint is provided for public query operations over our knowledge base.
 \end{itemize}
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:pre} introduces the four involved encyclopedias.
+Section \ref{sec:pd} introduces the four involved encyclopedias.
 Besides, definitions are proposed in this section.
@@
 
-\section{Preliminary}
-\label{sec:pre}
-In this section, we firstly introduce the four encyclopedias used to build and enrich our knowledge base. Then we give some related definitions to formalize our procedure.
+\section{Problem Definition}
+\label{sec:pd}
+In this section, we firstly introduce the four encyclopedias used to build and enrich our knowledge base. Then we give some related definitions to formalize our ontology model.
 
@@
 Out of these, English articles contribute most.
-There are 4.8 million articles in English while only over 800 thousand articles in Chinese.
-It is obvious that the quantity of English articles is far more than Chinese.
-Such imbalance makes those ontologies based on Wikipedia-only behave badly in cross-lingual aspect.
-For example, DBpedia has 683 concepts in English while only 11 Chinese concepts, that shows little help when trying to do cross-lingual research depending on DBpedia.
-To avoid this imbalance problem, two other Chinese encyclopedias are utilized to enrich Chinese source.
+The imbalance of different language articles makes ontologies based on Wikipedia-only behave badly in cross-lingual aspect.
+Thus, more Chinese encyclopedias are necessary to enrich Chinese source.
 
-Articles in Wikipedia are manually edited by various authors.
-To avoid distinct formats and styles, Wikipedia provides templates to format their editing content, especially infoboxes.
-For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of film articles.
+Among the large-scale monolingual Chinese encyclopedias currently, Baidu Baike and Hudong Baike are the most content-rich.
+Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015.
+Meanwhile, Baidu Baike maintains more than 11 million articles.
 
-\subsubsection{Other Chinese Encyclopedias}
-There are several large-scale monolingual Chinese Encyclopedias currently.
-Among those, Baidu Baike and Hudong Baike are the most content-rich.
-Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015.
-At the mean time, Baidu Baike maintains more than 11 million articles.
-These two resources are similar in article structure, even in content in some cases.
-
-\subsubsection{Encyclopedia Page}
-\label{sec:ep}
-All these four encyclopedias provide two important elements which contain potential semantic information, category taxonomy and articles.
+Articles from the four sources are similar in structure.
+Usually they provide two important elements with potential semantic information, category taxonomy and articles.
 A taxonomy presents the relations between categories.
-Usually a category has its sub-categories and super-categories.
+Usually a category has sub-categories and super-categories.
 Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy.
@@
 
-\subsection{Cross-lingual Links}
-In order to build a cross-lingual knowledge base, we need the mapping relation between Chinese sources and English sources, which can be used to fuze information in different language.
-In Wikipedia, some article pages have language links so that the reader can switch languages within the same article.
+Notably, articles in Wikipedia follow templates specified by Wikipedia when being editted.
+A template defines items that a group of article should fill.
+Besides, infoboxes are generated based on templates too.
+For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films.
+
+Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article.
 Fig.
 \ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page.
-Taking advantage of manually established language links, we can generate an initial cross-lingual ontology based on Chinese and English Wikipedia, similar to DBpedia.
-Afterwards, to combine Hudong Baike and Baidu Baike, which are lack of cross-lingual information but rich in Chinese data, we employ the approach proposed in \cite{wang2012cross} to discover cross-lingual links between English Wikipedia and Baidu Baike.
+Taking advantage of manually established language links, we can generate an initial cross-lingual ontology.
 
@@
 \label{sec:definition}
-Here we list definitions involved in the later sections:
+Here we list some definitions involved in the later sections:
 
-\textbf{Definition 1:} A Encyclopedia is considered as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.
+\textbf{Definition 1:} An encyclopedia is considered as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.
 
-\textbf{Definition 2:} According to Section \ref{sec:ep}, there are several elements of an article. Therefore, each article $a$ can be defined as follow:
+According to Section \ref{sec:encyclopedias}, the elements of each article $a$ can be defined as follow:
 \begin{equation}
-    a = <Ti(a),AB(a),Li(a),I(a),C(a)>
+    a = <Ti(a),Ab(a),Li(a),In(a),C(a),U(a)>
 \end{equation}
-where $Ti(a),AB(a),Li(a),I(a),C(a)$ denotes title, abstract, links, infobox, category tags of article $a$.
+where $Ti(a),Ab(a),Li(a),In(a),C(a),U(a)$ denotes title, abstract, links, infobox, category tags, url of article $a$.
 
-\textbf{Definition 3:} As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article tags, usually titles, in English and Chinese separately.
-Thus $cl(a) = <L_{e}(a), L_{z}(a)>$
+The topic described by $a$ is defined as Entity$e$. Ariticles from different sources may talk about the same entity. In such a situation, we say the articles are linked.
 
-\textbf{Definition 4:} An Infobox $I(a)$ in an article contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
+\textbf{Definition 2:} As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
+Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$
+
+\textbf{Definition 3:} An Infobox $In(a)$ in an article contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
 In Wikipedia, an infobox is usually edited based on an appropriate infobox template recommended by Wikipedia, which here we denote as $T(a)$.
-Templates specify certain attributes, which are usually different from those displayed on the web page.
+Templates specify certain attributes, which are usually different from those displayed on the webpage.
 Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value.
 
-\section{Procedure Overview}
+\textbf{Definition 4:} An ontology is a formal specification of a group of entitie. An ontology can be described as a 6-tuple:
+\begin{equation}
+    O = <C,I,P,H^C,H^I,H^P>
+\end{equation}
+where $C$, $I$, $P$ are the sets of concepts, instances, and properties, respectively.
+$H^C$, $H^I$, $H^P$ represents the hierarchical relationships of concept-concept, concept-instance, instance-property.
+A Taxonomy$T$ is comprised by $H^C$ and $H^I$, which seperately repesent \emph{SubClassOf} and \emph{InstanceOf} relations.
+
+\textbf{Definition 5:} Given several ontologies generated from various sources, a cross-lingual knowledge base combines them into one. Thus a knowledge base can be defined as 
+\begin{equation}
+    KB = <O_{i}, CL>
+\end{equation}
+where O denotes ontologies, CL represents the cross-lingual link set.
+
+\section{Proposed Framework}
 Fig. \ref{fig:procedure} presents the whole procedure of our knowledge base building.
@@
 After data parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source.
-Meanwhile, an initial Chinese-English lan-link map is generated, which is then employed a link-discovery method to obtain a larger one.
+Meanwhile, an initial Chinese-English lan-link set is generated, which will be increased by employing a link-discovery method to obtain a larger one.
 Using the extended language links, we combine the four datasets into one.
@@
 
-\section{Data Preprocessing}
+\section{Semantic Data Extraction}
 \label{sec:dp}
-We prepare data for the knowledge base by a series of preprocessing operations.
-During this stage, our goal is to get a structured dataset including concepts, which are extracted from category taxonomy; instances, which are defined according to articles and properties based on both infobox and templates assistant.
+We prepare data for the knowledge base by a series of extracting operations.
+During this stage, our goal is to get a structured dataset including concepts, which are extracted from category taxonomy; instances, which are defined according to articles, and properties based on both infobox and templates assistant.
 We will describe the extraction approach in detail below.
@@
 For example, the concept of instance \emph{Interstellar} is \emph{Movie}.
-In general, a concept has super classes and sub classes, which means it has \emph{subClassOf} relation with other classes.
+In general, a concept has super classes and sub classes, which means it has \emph{SubClassOf} relation with other classes.
 Concepts comprise a taxonomy which presents a backbone of an ontology.
@@
     \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
-    \item Some sub-category links in the category system maybe inconsistent.
+    %s\item Some sub-category links in the category system maybe inconsistent.
 Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it.
@@
 \end{itemize}
-   To receive a cleaner and more precise concept taxonomy, we firstly do some refining works as follow:
+   To receive a more precise concept taxonomy, we do some refining works as follow:
 \begin{itemize}
     \item Delete list categories or template categories in Wikipedia.
-    \item Delete inconsistent sub-categories and keep the super one.
+    %s\item Delete inconsistent sub-categories and keep the super one.
     \item Delete categories that relate to less than two articles.
 \end{itemize}
-The cleaning work carried out in all encyclopedias are consistency when extracting.
-The remaining categories comprise an original concept taxonomy.
-A category and its sub-categories are correlated by the relation \emph{SubClassOf}, and a category and its articles are correlated by the relation \emph{InstanceOf}.
-However, there are still incorrect samples in the two relations.
+The cleaning work is carried out consistently in all encyclopedias when extracting.
+Remaining categories comprise an original concept hierarchical relationship$H^C$ of $T$.
+However, among the relations there are still incorrect samples.
 For example, \emph{Tsinghua University} is not an entity of \emph{Haidian District}, but relates to.
@@
 \subsubsection{General-properties}
-Characteristics of an entity are seen as general-properties, including label, abstract, and url.
-Those properties describe specific information of an entity.
-The label property identifies a unique entity, whose value is the article title.
-The abstract property provides a brief description of an entity, whose value is the first paragraph of article.
-The url property saves the source of an entity, which is actually a url in each source.
+Characteristics of an entity are regarded as general-properties, including label, abstract, and url.
+General-properties describe specific information of an entity.
+Given an article$a$, title$Ti(a)$ is the value of label property, which identifies a unique entity.
+$Ab(a)$, usually the first paragraph of article, corresponding the abstract property, which provides a brief description of an entity.
+The url property saves the resource url of an entity, whose value is $U(a)$ .
 All of them are datatype properties.
@@
 Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
-Each attribute in the infobox is related to its own corresponding value.
+Each attribute in the infobox is related to a corresponding value.
 The value maybe a text or a reference to another entity.
@@
 \begin{itemize}
-    \item The attribute label displayed in the webpage infobox is inconsistent with it in the published dump file of Wikipedia.
+    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file.
 Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox.
-The left is infobox while the other is a snap from dump file in Wikipedia.
-This movie's infobox follows template \emph{Infobox film}, where dump labels come from.
-Obviously the two labels are similar but not the same.
+The left is infobox, the middle is a snap from dump file in Wikipedia.
+As we've seen, attribute label in infobox is different from it in dump file.
 As a result we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
-As to Chinese sources, the property labels from Hudong Baike and Baidu Baike are equal literally to texts displayed on the webpage, so we don't need extra process as we have in Wikipedia.
     \begin{figure}[ht]
@@
 \item There are special characters in labels.
-For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
-For example, population property have sub-properties "-Density" and "-Urban".
+Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
+For example, \emph{population} property have sub-properties "-Density" and "-Urban".
 In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
@@
 Specifically, Wikipedia institutes rules of rendering label in templates.
-Fig.\ref{fig:infobox-render-rule} shows part of rules in \emph{template:infobox film}.
-When a dump label in triple-bracket occurs in a dump page, we can replace it by its mapping display label.
-After collecting all the display labels, we make a filter to redress the label text.
+For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from.
+When a dump label in triple-bracket occurs in dump file, we replace it by its mapping display label.
+After convert all the dump labels, we make a filter to redress the label text.
 
@@
 Therefore we can extract an article content as an instance.
-But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including category List pages and template documentations.
+During the extraction, llustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.
 
@@
 美国科幻片(American science fiction films) is a concept of Interstellar.
-In the meantime, we obtain the label property from the article title, which is 星际穿越(Interstellar) and the abstract property from the first paragraph.
-The infobox-properties are also acquired via extracting from the infobox in the article.
-Besides, according to links in the content, we gain the reference between the current instance and others, such as 华纳兄弟(Warner Bros.).
+In the meantime, we obtain label property from the article title and abstract property from the first paragraph.
+Infobox-properties are also acquired via extracting from the infobox in the article.
+Besides, according to links in the content, we gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).
 
 After the preprocessing above, we harvest two types of information.
-One is the characteristics of instance, including instance-label, instance-abstract.
-The other includes relationships, containing concept-instance, instance-property-value and instance-instance.
+One is the characteristics of instance, including $Ti(a)$, $Ab(a)$ of article$a$.
+The other includes relationships, containing $H^I$ and $H^P$ associate with article$a$.
 
-\section{Cross-lingual Knowledge Base Building}
+\section{Cross-lingual Integration}
 \label{sec:clkbb}
@@
 
-\subsection{Cross-lingual Links}
+\subsection{Cross-lingual Linking}
 Wikipedia has \textcolor{red}{number} cross-lingual links between English and Chinese.
@@
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
-With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\%.
+With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.
 
-However, due to following templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we take the following steps: (1) Given a matched template, which has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, find the matched label mapping to the same dump label.
-(3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
-The whole process can be summarized as Algorithm \ref{alg:ple}.
-Some of the symbols have already denoted in \ref{sed:definition}
-\subsection{Cross-lingual Linking}
+However, due to using templates, Infobox-properties have no obvious cross-lingual links.
+To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
+That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are property cross-lingual; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template$T_{e}(a_{i})$ and a Chinese template$T_{z}(a_{j})$ in which $a_{i}$ and $a_{j}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+
 In order to make all these encyclopedias linked to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
@@
 
-\begin{enumerate}[1)]
+\begin{enumerate}[Step 1]
     \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
@@
 Each instance may correspond to 1 to 3 sources.
-    \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
+    \item To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
     \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an new ID.
@@
 For example, \textcolor{red}{example}.
-Therefore, we introduce the method from\cite{wang2014cross} to filter the correct subClassOf and instanceOf relations between two entities.
+Therefore, we introduce the method from\cite{wang2014cross} to filter the correct SubClassOf and InstanceOf relations between two entities.
 Table.
@@
 The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities.
-The structural features include article divergence for subClassOf, property divergence for subClassOf, category divergence for subClassOf, article divergence for instanceOf, property divergence for instanceOf, category divergence for instanceOf.
+The structural features include article divergence for SubClassOf, property divergence for SubClassOf, category divergence for SubClassOf, article divergence for InstanceOf, property divergence for InstanceOf, category divergence for InstanceOf.
 By employing these features, a binary-classification model is trained based on Logistic Regression.
 The whole process is iterative by add assured result into training set and retraining the model to get higher precision.
-Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
-Fig.
-\ref{fig:} shows an example of the process.
+Confirming a right SubClassOf or InstanceOf not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
 
-The ideal result of pruning is a tree, whose edges denote relations, nodes denote concepts and leaves denote instances.
-However, since get rid of incorrect entity relations without consideration of integrity, getting a forest result is inevitable.
+The ideal result of pruning is a tree, whose edges, nodes, and leaves separately denote relations, concepts and instances.
+However, since getting rid of incorrect entity relations without consideration of integrity, a forest result is inevitable.
 We may omit some links but get more accurate relations instead.
-
-\subsection{Knowledge Base Building}
-To build a knowledge base, we first define specific URI to identify each element in the prepared dataset.
-URIs of concept, instance, and property are created by concatenating a namespace prefix to an ID.
-Table \ref{tab:uris} lists the URI defined in the knowledge base.
-\begin{table}[h]
-\small
-\centering
-\caption{URIs for concept, instance, property in our knowledge base}
-\label{tab:uris}
-    \begin{tabular}{|c|c|}
-        \hline
-        Type     & URI                          \\ \hline
-        Concept  & http://xlore.org/concept/id  \\ \hline
-        Instance & http://xlore.org/instance/id \\ \hline
-        Property & http://xlore.org/property/id \\ \hline
-    \end{tabular}
-\end{table}
 
@@
                  & Enwiki  & Zhwiki & Hudong  & Baidu   \\ \hline
-        Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
-        Concept  & 982432  & 159705 & 31802   & 1300    \\ \hline
-        Property & 43976   & 18842  & 1187    & 139634  \\ \hline
+        #Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
+        #Concept  & 982432  & 159705 & 31802   & 1300    \\ \hline
+        #Property & 43976   & 18842  & 1187    & 139634  \\ \hline
+    \end{tabular}
+\end{table}
+
+To build a knowledge base, we create URIs to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.
+Table \ref{tab:uris} lists the defined URIs.
+\begin{table}[h]
+\small
+\centering
+\caption{URIs for concept, instance, property in our knowledge base}
+\label{tab:uris}
+    \begin{tabular}{|c|c|}
+        \hline
+        Type     & URI                          \\ \hline
+        Concept  & http://xlore.org/concept/id  \\ \hline
+        Instance & http://xlore.org/instance/id \\ \hline
+        Property & http://xlore.org/property/id \\ \hline
     \end{tabular}
@@
 
-\subsection{Query Interface}
-We provide a website to demonstrate our knowledge in the forms of class, instance and property.
+\subsection{Web Access to Knowledge Base}
+We provide a website to present an intuitive graph of our knowledge in the forms of class, instance and property.
+Fig.\ref{fig:xlore} shows sample pages of the integrated data.
 The users of our system can choose language preference which is convenient for both English speaker and Chinese speaker.
@@
 In the property webpage, we presents bilingual label, domains, ranges, and related instances of each property.
-Beside these user-friendly pages, we as well provide SPARQL interface for professional users to query our knowledge graph.
+\begin{figure}[ht]
+    \centerline{\includegraphics[width=1\columnwidth]{fig/xlore}}
+    \label{fig:xlore}
+    \caption{Sample Pages of Class, Instance and Property}
+\end{figure}%
+Beside these user-friendly pages, we provide two ways to access our knowledge base: via the search engine shown in Fig.\ref{fig:search-engine}, or via SPARQL endpoint shown in Fig.\ref{fig:sparql-endpoint}.
+For users who know little about semantic web, they can query by inputing related text into searchbox and search to get entities with similar label.
+To present practicable result, An index is generated over all entities.
+We as well provide SPARQL interface for professional users to query our knowledge graph.
 Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.
+\begin{figure}
+    \centering
+    \begin{minipage}[t]{0.8\textwidth}
+        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
+        \label{fig:search-engine}
+        \caption{A Sample Query for Using Search Box }
+    \end{minipage}%
+    \begin{minipage}[t]{0.8\textwidth}
+        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
+        \label{fig:sparql-endpoint}
+        \caption{A SPARQL Sample Query over the Knowledge Base}
+    \end{minipage}%
+\end{figure}
 

### 2015-06-01 nlpcc/paper.tex
add picture

@@
 
-\textbf{Definition 4:} An ontology is a formal specification of a group of entitie. An ontology can be described as a 6-tuple:
+\textbf{Definition 4:} An ontology is a formal specification of a group of entitie. In our work, an ontology is described as a 6-tuple:
 \begin{equation}
@@
 
-\textbf{Definition 5:} Given several ontologies generated from various sources, a cross-lingual knowledge base combines them into one. Thus a knowledge base can be defined as 
+\subsection{Cross-lingual Knowledge Base Building}
+A cross-lingual knowledge base is a database conform to a cross-lingual ontology.
+Taking advantage of language links in $CL$, several mono-ontologies generated from various sources can be merge into one cross-lingual ontology.
+Thus a knowledge base can be defined as:
 \begin{equation}
@@
 \end{equation}
-where O denotes ontologies, CL represents the cross-lingual link set.
-
-\section{Proposed Framework}
-Fig. \ref{fig:procedure} presents the whole procedure of our knowledge base building.
+where $O_{i}$ denotes the ith mono-ontology, CL represents the cross-lingual link set.
+We build the cross-lingual ontology according to the procedure in Fig. \ref{fig:procedure}
 \begin{figure}[ht]
@@
 Therefore we can extract an article content as an instance.
-During the extraction, llustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.
+During the extraction, illustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.
 
@@
 In the meantime, we obtain label property from the article title and abstract property from the first paragraph.
-Infobox-properties are also acquired via extracting from the infobox in the article.
+Infobox-properties are acquired via extracting from the infobox in the article.
 Besides, according to links in the content, we gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).
@@
 One is the characteristics of instance, including $Ti(a)$, $Ab(a)$ of article$a$.
-The other includes relationships, containing $H^I$ and $H^P$ associate with article$a$.
+The other includes relationships, containing $H^I$ and $H^P$ associated with article $a$.
 

### 2015-06-01 nlpcc/paper.tex
delete algorithm

@@
 其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
+The English Wikipedia dump files archived in April 2015 contains XXX articles an XXX categories.
+At the same period, the Chinese Wikipedia dump downloaded has XXX articles and XXX categories.
+While the Chinese Encyclopedia Baidu Baike we acquired in 2015 has XXX articles and XXX categories.
+And Hudong Baike in 2014 has XXX articles and XXX categories.
+
 \subsection{Extracted Knowledge Base}
@@
 
-\begin{algorithm}[t]
-    \KwIn{ English Infobox template set $TS_{e}$, Chinese Infobox template set $TS_{z}$, English article set $AS_{e}$, Chinese article set $AS_{z}$, existing lan-link map $CL<L_{e}, L_{z}>$ }
-\KwOut{Property lan-link map $CL_{p}$}
-
-Initialization: $CL_{p} = \{\} $\\
-\ForEach {English Template $T_{e} \in TS_{e}$}{
-    $L_{e}$ = label of $T{e}$ \\
-    \eIf {$L_{e} \in CL$}{
-        $L_{z} = CL\left[L_{e}\right] $ ,\ $T_{z} = TS_{z}\left[L_{z}\right]$\\
-        \ForEach{$tl \in T_{e}.pset.tlset \cap T_{z}.pset.tlset $}{
-            $CL_{p}$.add(<$T_{e}.p[tl].dl$, $T_{z}.p[tl].dl$>)
-        }
-    }
-}
-
-\ForEach {English Article $A_{e}$ \in $AS_{e}$}{
-    $L_{e}$ = label of $A_{e}$
-    \eIf {$L_{e} \in CL$}{
-        $L_{z} = CL\left[L_{e}\right]$ ,\ $A_{z} = AS_{z}\left[L_{z}\right]$ \\
-
-        $T_{e}$ = Template of $A_{e}$.I ,\ $T_{z}$ = Template of $A_{z}$.I \\
-
-        Set $Cset$ as the Common set of template labels of $T_{e}$ and template labels of $T_{z}$ \\
-        $Cset = T_{e}.pset.tlset \cap T_{z}.pset.tlset $ \\
-
-        \ForEach {template label $tl \in Cset $}{
-            $CL_{p}$.add(<$T_{e}.pset[tl].dl$, $T_{z}.pset[tl].dl$>)
-        }
-
-        \ForEach{English template label $tl_{e} \in T_{e}.pset.tlset \minus Cset$}{
-            $p_{e} = T_{e}.pset\left[tl_{e}\right]$ \\
-            \ForEach{Chinese template label $tl_{z} \in T_{z}.pset.tlset - Cset$}{
-                $p_{z} = T_{z}.pset\left[tl_{z}\right]$ \\
-                \eIf {$p_{e}.type$ is datatype $\&\&$ $p_{z}.type$ is datatype}{
-                    \eIf {CalculateSimilar($p_{e}.v$, $p_{z}.v$) > $threshold$}{
-                        $CL_{p}$.add(<$p_{e}.dl$, $p_{z}.dl$>)
-                    }
-                } \eElseIf {$p_{e}.type$ is object $\&\&$ $p_{z}.type$ is object}{
-                    \eIf{ReferToCommmonEntity($p_{e}.v$, $p_{z}.v$)}{
-                        $CL_{p}$.add(<$p_{e}.dl$, $p_{z}.dl$>)
-                    }
-                }
-            }
-        }
-    }
-}
-\caption{Property Links Extraction}
-\label{alg:ple}
-\end{algorithm}
-
 \end{document}

### 2015-06-01 nlpcc/paper.tex
msc font problem

--- 2015-06-01 nlpcc/paper.tex
@@
 
-\usepackage[BoldFont,SlantFont,CJKsetspaces,CJKchecksingle]{xeCJK}
-\setCJKmainfont[BoldFont=SimHei]{SimSun}
-\setCJKmonofont{SimSun}% 设置缺省中文字体
+\usepackage{xeCJK}
+\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
+\setCJKsansfont[BoldFont=STHeiti]
+\setCJKmonofont{STFangsong}
+
+%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
+%\setCJKmainfont[BoldFont=SimHei]{SimSun}
+%\setCJKmonofont{SimSun}% 设置缺省中文字体
+%\usepackage{CJKutf8}
 
@@
 \usepackage{color}
-\usepackage{CJKutf8}
+%\usepackage{CJK}
+
 \usepackage{url}
@@
 \begin{document}
+%\begin{CJK*}{UTF8}{simsun}
 \mainmatter
@@
                  & Enwiki  & Zhwiki & Hudong  & Baidu   \\ \hline
-        #Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
-        #Concept  & 982432  & 159705 & 31802   & 1300    \\ \hline
-        #Property & 43976   & 18842  & 1187    & 139634  \\ \hline
+        \#Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
+        \#Concept  & 982432  & 159705 & 31802   & 1300    \\ \hline
+        \#Property & 43976   & 18842  & 1187    & 139634  \\ \hline
     \end{tabular}
@@
 Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.
-\begin{figure}
-    \centering
-    \begin{minipage}[t]{0.8\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
-        \label{fig:search-engine}
-        \caption{A Sample Query for Using Search Box }
-    \end{minipage}%
-    \begin{minipage}[t]{0.8\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
-        \label{fig:sparql-endpoint}
-        \caption{A SPARQL Sample Query over the Knowledge Base}
-    \end{minipage}%
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \begin{minipage}[t]{0.8\textwidth}
+%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
+%        \label{fig:search-engine}
+%        \caption{A Sample Query for Using Search Box }
+%    \end{minipage}%
+%    \begin{minipage}[t]{0.8\textwidth}
+%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
+%        \label{fig:sparql-endpoint}
+%        \caption{A SPARQL Sample Query over the Knowledge Base}
+%    \end{minipage}%
+%\end{figure}
 
@@
 
+%\end{CJK*}
 \end{document}

### 2015-06-01 nlpcc/paper.tex
data set

@@
 Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
-(2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which effects the quality of a bilingual knowledge base.
-Especially when there scarcely exists evident links in properties.
+(2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which affects the quality of a bilingual knowledge base.
+Especially when there are scarce evident links in properties.
 Statistically, only XX thousand cross-lingual links can be found between English and Chinese articles.
@@
 Section \ref{sec:pd} introduces the four involved encyclopedias.
-Besides, definitions are proposed in this section.
+Besides, the procedure are formalized in this section.
 Section \ref{sec:dp} presents the extraction approach in concept, instance and property level.
-Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracting result.
-Section \ref{sec:result} shows the results of established knowledge base.
+Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result.
+Section \ref{sec:result} shows the data situation of established knowledge base.
 Section \ref{sec:work} induces related work about this paper.
@@
 Nowadays, Wikipedia is the largest data store of human knowledge.
-It was launched in 2001 and has hold over 35 million articles in 288 language by 2015.
+It was launched in 2001 and has hold over 35 million articles in 288 languages by 2015.
 Out of these, English articles contribute most.
@@
 \begin{itemize}
-  \item Title: A Title is the label of an entity, which is unique to each article so that it can be used to distinguish entities.
-  \item Abstract: An abstract is a brief summarize of the entity. It's always the first paragraph of an article. Usually it can be taken as an important feature due to the summary content.
+  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
+  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article. 
   \item Infobox: Most of articles contain infobox.
-An infobox maintains structured data which are frequently subject-attribute-value triples formalized as a table.
+An infobox maintains structured data which are subject-attribute-value triples formalized as a table.
 Information in this table includes important properties of an entity.
@@
 Actually, they represent the relations between the current article and other articles.
-  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article attaches to one or more categories.
+  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article belongs to one or more categories.
 \end{itemize}
@@
 Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed.
-After data parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source.
-Meanwhile, an initial Chinese-English lan-link set is generated, which will be increased by employing a link-discovery method to obtain a larger one.
+After data parsing, we get four datasets with concept lists, instance lists, property lists and their relations of each source.
+Meanwhile, an initial Chinese-English language-link set is generated, which will be increased by employing a link-discovery method to obtain a larger one.
 Using the extended language links, we combine the four datasets into one.
@@
 Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
-For example, \emph{population} property have sub-properties "-Density" and "-Urban".
+For example, \emph{population} property has sub-properties "-Density" and "-Urban".
 In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
@@
 
-However, due to using templates, Infobox-properties have no obvious cross-lingual links.
+However, due to following templates, Infobox-properties have no obvious cross-lingual links.
 To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
@@
 In order to make all these encyclopedias linked to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
-For example, we merge instances by the following method:
+For instance, we merge instances by the following method:
 
@@
 \label{sec:result}
-\subsection{DataSet}
-四个百科的数据统计，包括我们有的百科数据的发布时间，格式（xml。html），article数量，抽取的instance数量，concept数量，property数量, wiki中跨语言链接数量
-其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
-The English Wikipedia dump files archived in April 2015 contains XXX articles an XXX categories.
-At the same period, the Chinese Wikipedia dump downloaded has XXX articles and XXX categories.
-While the Chinese Encyclopedia Baidu Baike we acquired in 2015 has XXX articles and XXX categories.
-And Hudong Baike in 2014 has XXX articles and XXX categories.
 
 \subsection{Extracted Knowledge Base}
-We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu.
+We collect the resources from 4 wiki sites, English and Chinese Wikipedia dump files in 2015 April, Hudong html pages until 2014 May, and Baidu html pages until 2014 September.
 Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles.

### 2015-06-02 nlpcc/paper.tex
move caption onto label
definitions

@@
   \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analyzing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise SubClassOf and InstanceOf relations in ontology.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \emph{SubClassOf} and \emph{InstanceOf} relations in ontology.
   \item Both website and SPARQL endpoint is provided for public query operations over our knowledge base.
@@
 \label{sec:pd}
-In this section, we firstly introduce the four encyclopedias used to build and enrich our knowledge base. Then we give some related definitions to formalize our ontology model.
+In this section, we firstly introduce the encyclopedias used to build and enrich our knowledge base.
+Then we give definitions about ontology and knowledge base.
+At last we describe our task in this work.
 
@@
 Out of these, English articles contribute most.
-The imbalance of different language articles makes ontologies based on Wikipedia-only behave badly in cross-lingual aspect.
+The imbalance of different language articles makes ontologies based on Wikipedia-only behave badly in cross-lingual.
 Thus, more Chinese encyclopedias are necessary to enrich Chinese source.
@@
 
+Here, we consider an encyclopedia wiki as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.
+
+\subsection{Wiki Pages}
 Articles from the four sources are similar in structure.
@@
 An article describes an entity with rich information created and modified by several verified editors.
-Besides, an article may belong to one or more categories.
-The article content as well as the relation between an article and its belonged categories both help enormously when constructing a knowledge base.
+Besides, each article is linked to one or more categories by \emph{articleOf} relation.
 In general, there are five elements can be exploited in each article page:
@@
         \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
+        \caption{Taxonomy in Hudong}
         \label{fig:hudong-taxonomy}
-        \caption{Taxonomy in Hudong}
     \end{minipage}%
@@
   \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article belongs to one or more categories.
+  \item URL: Each article has an HTTP url to identify itself on web.
 \end{itemize}
+
 Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
@@
     \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
+    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
     \label{fig:interstellar}
-    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
 \end{figure}%
 
-Notably, articles in Wikipedia follow templates specified by Wikipedia when being editted.
-A template defines items that a group of article should fill.
-Besides, infoboxes are generated based on templates too.
-For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films.
-
-Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article.
-Fig.
-\ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page.
-Taking advantage of manually established language links, we can generate an initial cross-lingual ontology.
-
-\subsection{Definitions}
-\label{sec:definition}
-Here we list some definitions involved in the later sections:
-
-\textbf{Definition 1:} An encyclopedia is considered as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.
-
-According to Section \ref{sec:encyclopedias}, the elements of each article $a$ can be defined as follow:
+The elements of each article $a$ can be defined as follow:
 \begin{equation}
@@
 
-The topic described by $a$ is defined as Entity$e$. Ariticles from different sources may talk about the same entity. In such a situation, we say the articles are linked.
-
-\textbf{Definition 2:} As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
-Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$
-
-\textbf{Definition 3:} An Infobox $In(a)$ in an article contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
-In Wikipedia, an infobox is usually edited based on an appropriate infobox template recommended by Wikipedia, which here we denote as $T(a)$.
+Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited.
+A template defines items that a group of article should fill.
+Besides, infoboxes are also generated based on certain templates recommended by Wikipedia.
+For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films.
+An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
+We denote infobox template as $T(a)$.
 Templates specify certain attributes, which are usually different from those displayed on the webpage.
@@
 
-\textbf{Definition 4:} An ontology is a formal specification of a group of entitie. In our work, an ontology is described as a 6-tuple:
+Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article.
+Fig.
+\ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page.
+As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
+Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.
+
+\subsection{Ontology and Knowledge Base}
+
+An ontology is a formal specification of a group of entities. In our work, an ontology is described as a 4-tuple:
 \begin{equation}
-    O = <C,I,P,H^C,H^I,H^P>
+    O = <C,I,P,H^C>
 \end{equation}
 where $C$, $I$, $P$ are the sets of concepts, instances, and properties, respectively.
-$H^C$, $H^I$, $H^P$ represents the hierarchical relationships of concept-concept, concept-instance, instance-property.
-A Taxonomy$T$ is comprised by $H^C$ and $H^I$, which seperately repesent \emph{SubClassOf} and \emph{InstanceOf} relations.
+$H^C$ represents the hierarchical relationships of concepts.
+A Taxonomy includes two types of relationships, which are \emph{SubClassOf} of concept-concept and \emph{InstanceOf} of concept-instance.
 
-\subsection{Cross-lingual Knowledge Base Building}
 A cross-lingual knowledge base is a database conform to a cross-lingual ontology.
-Taking advantage of language links in $CL$, several mono-ontologies generated from various sources can be merge into one cross-lingual ontology.
+Taking advantage of language links in $CL$, several monolingual-ontologies generated from various sources can be merge into one cross-lingual ontology.
 Thus a knowledge base can be defined as:
@@
 \end{equation}
-where $O_{i}$ denotes the ith mono-ontology, CL represents the cross-lingual link set.
-We build the cross-lingual ontology according to the procedure in Fig. \ref{fig:procedure}
+where $O_{i}$ denotes the ith monolingual-ontology, $CL$ represents the cross-lingual link set.
+
+\subsection{Cross-lingual Knowledge Base Building}
+In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources.
+Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including concept list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting.
+We then enrich the extracted language-link set $CL$ using an link-discovery extension method.
+We also refining taxonomy by checking if an \emph{articleOf} or \emph{subCategoryOf} is really an \emph{InstanceOf} or \emph{SubClassOf} relationship.
+Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.
+
+The whole building procedure is shown in Fig. \ref{fig:procedure}
 \begin{figure}[ht]
     \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
+    \caption{Procedure of building our cross-lingual knowledge base}
     \label{fig:procedure}
-    \caption{Procedure of building our cross-lingual knowledge base}
 \end{figure}%
@@
 Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed.
-After data parsing, we get four datasets with concept lists, instance lists, property lists and their relations of each source.
-Meanwhile, an initial Chinese-English language-link set is generated, which will be increased by employing a link-discovery method to obtain a larger one.
-Using the extended language links, we combine the four datasets into one.
-At last, going through the procedure of taxonomy pruning and data-cleaning, we get a final knowledge base with higher accuracy.
+After data parsing, we get four ontologies each source.
+Going through the process of taxonomy pruning, we delete some incorrect relations.
+At last Using the extended language links, we combine the four ontologies into a cross-lingual knowledge base.
 
@@
         \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
+        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
         \label{fig:infobox-template}
-        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
     \end{figure}%
@@
         Type     & URI                          \\ \hline
-        Concept  & http://xlore.org/concept/id  \\ \hline
-        Instance & http://xlore.org/instance/id \\ \hline
-        Property & http://xlore.org/property/id \\ \hline
+        Concept  & http://clkb/concept/id  \\ \hline
+        Instance & http://clkb/instance/id \\ \hline
+        Property & http://clkb/property/id \\ \hline
     \end{tabular}
@@
     \centerline{\includegraphics[width=1\columnwidth]{fig/xlore}}
+    \caption{Sample Pages of Class, Instance and Property}
     \label{fig:xlore}
-    \caption{Sample Pages of Class, Instance and Property}
 \end{figure}%
@@
 %        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
+%        \caption{A Sample Query for Using Search Box }
 %        \label{fig:search-engine}
-%        \caption{A Sample Query for Using Search Box }
 %    \end{minipage}%
@@
 %        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
+%        \caption{A SPARQL Sample Query over the Knowledge Base}
 %        \label{fig:sparql-endpoint}
-%        \caption{A SPARQL Sample Query over the Knowledge Base}
 %    \end{minipage}%

### 2015-06-02 nlpcc/paper.tex
按照大师兄的6.1 改了一版

@@
 \usepackage{enumerate}
+\usepackage{multirow}
 
@@
 \begin{abstract}
-    Abstract Text
+Cross-lingual Knowledge Bases are important for global knowledge sharing.
+However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy.
+In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems.
+The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike.
+An extension method is used to increase language links while a pruning approach is used to refine taxonomy.
+Totally, there are XXX concepts, XXX instances, XXX properties referred in the CLKB.
+Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.
 
@@
 With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing.
-Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and many other applications.
+Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge} and many other applications.
 These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.
 
- The nucleus of LOD DBpedia extracts structured information from Wikipedia and has already contained approximately 38.3 million things.
+DBpedia, the nucleus of LOD, extracts structured information from Wikipedia and contains approximately 38.3 million things.
 Now DBpedia provides 124 versions of non-English language including Chinese.
 However, there are only XXX instances and 11 classes in Chinese.
-Compared with the 4.58 million things in English, the quality of Chinese information is obviously insufficient for further research and application.
+Compared with the 4.58 million things in English, the quantity of Chinese information is obviously insufficient for further research and application.
 
 A cross-lingual knowledge base can effectively promote global knowledge sharing, understanding and expanding.
-However, to build an available knowledge base, some problems must be addressed: (1) The imbalanced size of different language sources leads to less entities.
+However, to build an practical knowledge base, some problems must be addressed: (1) The imbalance of different language source size leads to less entities.
 Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
-(2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which affects the quality of a bilingual knowledge base.
-Especially when there are scarce evident links in properties.
-Statistically, only XX thousand cross-lingual links can be found between English and Chinese articles.
+(2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base.
+Statistically, only XX\% articles have cross-lingual links between English and Chinese in all articles of the two languages.
+Especially scarce evident links for infobox attribute.
 (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
@@
 Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike.
-To solve the imbalance problem, we utilize such separated sources to enrich our Chinese information.
-In this paper, we propose an approach to integrate four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
-To get a more available result, we also make judgement on the relations among concepts and instances.
-At last, a SPARQL endpoint is provided to access to the knowledge base.
+To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information.
+In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
+During the whole procedure, we also expand language links and make judgement on the semantic relations.
+Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our knowledge base.
 Specifically, our work makes the following contributions:
 \begin{itemize}
-  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedias.
-Among them, two  Chinese encyclopedias are utilized to help balance and enrich information in two languages.
+  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedia.
+Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
   \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analyzing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \emph{SubClassOf} and \emph{InstanceOf} relations in ontology.
-  \item Both website and SPARQL endpoint is provided for public query operations over our knowledge base.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
+  \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
 \end{itemize}
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:pd} introduces the four involved encyclopedias.
-Besides, the procedure are formalized in this section.
-Section \ref{sec:dp} presents the extraction approach in concept, instance and property level.
+Section \ref{sec:pd} introduces the related concepts and defines the problem of building a cross-lingual knowledge base.
+Section \ref{sec:dp} presents the extraction approaches in concept, instance and property level.
 Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result.
-Section \ref{sec:result} shows the data situation of established knowledge base.
-Section \ref{sec:work} induces related work about this paper.
-Section \ref{sec:con} gives the conclusion.
+Section \ref{sec:result} demonstrates the data situation of established knowledge base.
+Section \ref{sec:work} reviews the related literatures.
+Section \ref{sec:con} concludes this paper and points out some future directions of this work.
 
@@
 An article describes an entity with rich information created and modified by several verified editors.
-Besides, each article is linked to one or more categories by \emph{articleOf} relation.
+Besides, each article is linked to one or more categories by \textit{articleOf} relation.
 In general, there are five elements can be exploited in each article page:
@@
 Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value.
+The value maybe a text or a reference to another entity.
 
@@
 $H^C$ represents the hierarchical relationships of concepts.
-A Taxonomy includes two types of relationships, which are \emph{SubClassOf} of concept-concept and \emph{InstanceOf} of concept-instance.
+A Taxonomy includes two types of relationships, which are \textit{subClassOf} of concept-concept and \textit{instanceOf} of concept-instance.
 
@@
 We then enrich the extracted language-link set $CL$ using an link-discovery extension method.
-We also refining taxonomy by checking if an \emph{articleOf} or \emph{subCategoryOf} is really an \emph{InstanceOf} or \emph{SubClassOf} relationship.
+We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
 Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.
@@
 \label{sec:dp}
-We prepare data for the knowledge base by a series of extracting operations.
-During this stage, our goal is to get a structured dataset including concepts, which are extracted from category taxonomy; instances, which are defined according to articles, and properties based on both infobox and templates assistant.
-We will describe the extraction approach in detail below.
+Semantic data extraction aims to achieve a structured dataset from the input encyclopedias, preparing for the knowledge base construction.
+Specifically, we extracts concepts from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.
 
@@
 For example, the concept of instance \emph{Interstellar} is \emph{Movie}.
-In general, a concept has super classes and sub classes, which means it has \emph{SubClassOf} relation with other classes.
+In general, a concept has super classes and sub classes.
 Concepts comprise a taxonomy which presents a backbone of an ontology.
-
-In an encyclopedia, a category groups several articles and also has super-categories and sub-categories, just like concept does. Therefore we can extract concepts based on existing category system.
+In an encyclopedia, a category groups several articles and also has super-categories and sub-categories.
+Therefore we can extract concepts based on existing category system.
 
@@
 \end{itemize}
-   To receive a more precise concept taxonomy, we do some refining works as follow:
-\begin{itemize}
-    \item Delete list categories or template categories in Wikipedia.
-    %s\item Delete inconsistent sub-categories and keep the super one.
-    \item Delete categories that relate to less than two articles.
-\end{itemize}
-The cleaning work is carried out consistently in all encyclopedias when extracting.
-Remaining categories comprise an original concept hierarchical relationship$H^C$ of $T$.
+   To obtain a more precise concept taxonomy,first remove such categories in all encyclopedias, and build the original concept hierarchy $H^C$ using the remaining categories.  
 However, among the relations there are still incorrect samples.
@@
 Characteristics of an entity are regarded as general-properties, including label, abstract, and url.
-General-properties describe specific information of an entity.
-Given an article$a$, title$Ti(a)$ is the value of label property, which identifies a unique entity.
-$Ab(a)$, usually the first paragraph of article, corresponding the abstract property, which provides a brief description of an entity.
-The url property saves the resource url of an entity, whose value is $U(a)$ .
-All of them are datatype properties.
+General-properties describe general information of an entity.
+We define three datatype properties as general-properties for a given article $a$: (1) label property; (2) abstract property; (3) URL property.
 
@@
 Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
-Each attribute in the infobox is related to a corresponding value.
-The value maybe a text or a reference to another entity.
 The type of a property, datatype or object, depends on the type of the value.
@@
     \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file.
-Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox.
+Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Interstellar}' infobox.
 The left is infobox, the middle is a snap from dump file in Wikipedia.
 As we've seen, attribute label in infobox is different from it in dump file.
-As a result we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
+We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
     \begin{figure}[ht]
@@
 \item There are special characters in labels.
-Wikipedia usually use hyphen "-" or dot "•" to mark sublabels.
+Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels.
 For example, \emph{population} property has sub-properties "-Density" and "-Urban".
@@
 \label{sec:ie}
-In encyclopedia, an article describes an unique entity in the world.
-Therefore we can extract an article content as an instance.
+In encyclopedia, an article describes unique entity in the world.
+Therefore we can extract an article as an instance.
 During the extraction, illustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.
 
-Each instance contains relations with concepts and properties.
-Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page.
-美国科幻片(American science fiction films) is a concept of Interstellar.
-In the meantime, we obtain label property from the article title and abstract property from the first paragraph.
-Infobox-properties are acquired via extracting from the infobox in the article.
-Besides, according to links in the content, we gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).
-
-After the preprocessing above, we harvest two types of information.
-One is the characteristics of instance, including $Ti(a)$, $Ab(a)$ of article$a$.
-The other includes relationships, containing $H^I$ and $H^P$ associated with article $a$.
+We harvest four types of information during this stage.
+(1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value.
+(2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page.
+For example, 美国科幻片(American science fiction films) is a category of Interstellar; (4) Reference relation with other instances according to links in the content.
+We gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).
 
@@
 To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we link this four encyclopedia, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
-Thirdly, we prune the taxonomy generated from concept relationships to retain a more accurate one.
-At last, we make instances and properties attached to the taxonomy to create a complete knowledge base.
+Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
+Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate.
+At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.
 
 \subsection{Cross-lingual Linking}
-Wikipedia has \textcolor{red}{number} cross-lingual links between English and Chinese.
-By extracting language links from Wikipedia, we can get an initial cross-lingual link set of concepts and instances.
+There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances.
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
@@
 
-However, due to following templates, Infobox-properties have no obvious cross-lingual links.
+However, due to using templates, Infobox-properties have no obvious cross-lingual links.
 To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
-That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are property cross-lingual; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template$T_{e}(a_{i})$ and a Chinese template$T_{z}(a_{j})$ in which $a_{i}$ and $a_{j}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
 
-In order to make all these encyclopedias linked to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
+In order to make all these encyclopedias link to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
 For instance, we merge instances by the following method:
@@
 For example, \textcolor{red}{example}.
-Therefore, we introduce the method from\cite{wang2014cross} to filter the correct SubClassOf and InstanceOf relations between two entities.
+Therefore, we introduce the method from\cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}.
 Table.
@@
 In particular, some language-dependent literal and language-independent structural features are defined to vectorize each concept or instance.
-The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities.
-The structural features include article divergence for SubClassOf, property divergence for SubClassOf, category divergence for SubClassOf, article divergence for InstanceOf, property divergence for InstanceOf, category divergence for InstanceOf.
-By employing these features, a binary-classification model is trained based on Logistic Regression.
-The whole process is iterative by add assured result into training set and retraining the model to get higher precision.
-Confirming a right SubClassOf or InstanceOf not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
+Employing these features, a Yes-or-Not binary-classification model is trained based on Logistic Regression.
+The whole process is iterative by retraining model with assured result to get higher precision.
+Confirming a right \textit{subClassOf} or \textit{instanceOf} not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
 
@@
 However, since getting rid of incorrect entity relations without consideration of integrity, a forest result is inevitable.
-We may omit some links but get more accurate relations instead.
 
@@
 \subsection{Extracted Knowledge Base}
-We collect the resources from 4 wiki sites, English and Chinese Wikipedia dump files in 2015 April, Hudong html pages until 2014 May, and Baidu html pages until 2014 September.
+We collect the resources from 4 wiki sites, English and Chinese Wikipedia dump files in April, 2015, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
 Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles.
 We extract each raw data, then form the extracted information into well-structured data.
-Table\ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.
+Table \ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.
 
@@
 
-After fusing the heterogeneous resources, we harvest a cross-lingual graph with 1,093,855 classes, 200,223 properties, and 11,721,238 instances separately.
-With different methods of extraction and language linking discovery, these three kinds of entries show different results in languages.
-We give a breakdown of both Chinese knowledge and English knowledge in Table\ref{tab:kb-result}.
+After fusing the heterogeneous resources, we harvest a cross-lingual graph with 1,093,855 classes, 200,223 properties, and 11,721,238 instances respectively.
+With different methods of extraction and language link discovery, these three kinds of entries show different results in languages.
+We give a breakdown of both Chinese knowledge and English knowledge in Table \ref{tab:kb-result}.
 
@@
 \label{tab:kb-result}
-    \begin{tabular}{|l|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|l|l|}
 \hline
-                        & Concepts  & Instance   & Property \\ \hline
-        English         & 982,982   & 4,311,719  & 54,802   \\ \hline
-        English\%       & 89.86\%   & 37.79\%    & 27.37\%  \\ \hline
-        Chinese         & 176,648   & 7,842,117  & 167,083  \\ \hline
-        Chinese\%       & 16.15\%   & 66.9\%     & 83.45\%  \\ \hline
-        Cross-lingual   & 65,775    & 432,598    & 21,662   \\ \hline
-        Cross-lingual\% & 6.01\%    & 3.7\%      & 10.82\%  \\ \hline
-        Only English    & 917,207   &            & 33140    \\ \hline
-        Only English\%  & 83.9\%    &            & 16.6\%   \\ \hline
-        Only Chinese    & 110,873   &            & 145,421  \\ \hline
-        Only Chinese\%  & 10.1\%    &            & 72.6\%   \\ \hline
-        Sum             & 1,093,855 & 11,721,238 & 200,223  \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Concepts}      & \multicolumn{2}{c|}{Instance}                   & \multicolumn{2}{c|}{Property}    \\ \hline
+English                & 982,982   & 89.86\%                & 4,311,719              & 37.79\%                & 54,802  & 27.37\%                \\ \hline
+Chinese                & 176,648   & 16.15\%                & 7,842,117              & 66.9\%                 & 167,083 & 83.45\%                \\ \hline
+Cross-lingual          & 65,775    & 6.01\%                 & 432,598                & 3.7\%                  & 21,662  & 10.82\%                \\ \hline
+Only English           & 917,207   & 83.9\%                 & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 33140   & 16.6\%                 \\ \hline
+Only Chinese           & 110,873   & 10.1\%                 & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 145,421 & 72.6\%                 \\ \hline
+Sum                    & 1,093,855 & \multicolumn{1}{c|}{-} & 11,721,238             & \multicolumn{1}{c|}{-} & 200,223 & \multicolumn{1}{c|}{-} \\ \hline
 \end{tabular}
@@
 Fig.\ref{fig:xlore} shows sample pages of the integrated data.
-The users of our system can choose language preference which is convenient for both English speaker and Chinese speaker.
+Users can choose language preference which is convenient for both English speaker and Chinese speaker.
 In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.
  In the instance webpage we display bilingual label, super classes, related classes, abstract, property key value pairs, images and references.
-In the property webpage, we presents bilingual label, domains, ranges, and related instances of each property.
+In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
 \begin{figure}[ht]
@@
 \label{sec:work}
-In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods are referred to.
+In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods.
 \subsection{Chinese Knowledge Bases}
 Currently, several large-scale Chinese knowledge bases have been generated.
-Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first Chinese large-scale Linking Open Data published.
+Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first published Chinese large-scale Linking Open Data.
 It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities.
@@
 This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources.
-At first, data preprocessing work is done to extract structured information and unify data format.
-Then a cross-lingual lan-link set is generated to help combine the bilingual sources.
+At first, we extract structured information and unify data format.
+Then a cross-lingual language link set is generated to help combine the bilingual sources.
 Besides, an extension method is applied to enrich the links.
-To refine our dataset, we also do pruning work on taxonomy.
+To refine our dataset, we also conduct pruning work on taxonomy.
 Finally, we acquire a knowledge base containing XXX concepts, XXX instances and XXX properties.

### 2015-06-03 nlpcc/paper.tex
0601遗留的3个点

@@
 Articles from the four sources are similar in structure.
-Usually they provide two important elements with potential semantic information, category taxonomy and articles.
-A taxonomy presents the relations between categories.
-Usually a category has sub-categories and super-categories.
+Usually they provide two important elements with potential semantic information, category system and articles.
+A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}.
 Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy.
@@
 Actually, they represent the relations between the current article and other articles.
-  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article belongs to one or more categories.
+  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
   \item URL: Each article has an HTTP url to identify itself on web.
@@
 \end{itemize}
-   To obtain a more precise concept taxonomy,first remove such categories in all encyclopedias, and build the original concept hierarchy $H^C$ using the remaining categories.  
+   To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original concept hierarchy $H^C$ using the remaining categories.
+
 However, among the relations there are still incorrect samples.
@@
 For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from.
-When a dump label in triple-bracket occurs in dump file, we replace it by its mapping display label.
-After convert all the dump labels, we make a filter to redress the label text.
+When a dump label occurs in dump file, we replace it by its mapping display label.
 
@@
 
-However, due to using templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
-That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: 
+\begin{enumerate}[1)]
+    \item Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
+That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
+    \item Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label;
+    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+\end{enumerate}
 
 In order to make all these encyclopedias link to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
-For instance, we merge instances by the following method:
-
-\begin{enumerate}[Step 1]
-    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
-    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
-    \item Other instances existing in only one encyclopedia are considered as independent instances.
-Up to now, we have combined all Chinese articles describing the same entity as one instance.
-Each instance may correspond to 1 to 3 sources.
-    \item To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
-    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an new ID.
-\end{enumerate}
+For instance, we merge instances by the following method: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
+(2) To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$.
+If exists, make the two as one instance and identify it using an ID, else number it with an new ID.
 

### 2015-06-03 nlpcc/paper.tex
concept -> class

@@
 An extension method is used to increase language links while a pruning approach is used to refine taxonomy.
-Totally, there are XXX concepts, XXX instances, XXX properties referred in the CLKB.
+Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB.
 Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.
@@
 To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information.
-In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties.
+In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX classes, XXX instances and XXX properties.
 During the whole procedure, we also expand language links and make judgement on the semantic relations.
@@
 Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
-  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analyzing templates in Wikipedia for property.
+  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
   \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:pd} introduces the related concepts and defines the problem of building a cross-lingual knowledge base.
-Section \ref{sec:dp} presents the extraction approaches in concept, instance and property level.
+Section \ref{sec:pd} introduces the related classes and defines the problem of building a cross-lingual knowledge base.
+Section \ref{sec:dp} presents the extraction approaches in class, instance and property level.
 Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result.
@@
 \end{equation}
-where $C$, $I$, $P$ are the sets of concepts, instances, and properties, respectively.
-$H^C$ represents the hierarchical relationships of concepts.
-A Taxonomy includes two types of relationships, which are \textit{subClassOf} of concept-concept and \textit{instanceOf} of concept-instance.
+where $C$, $I$, $P$ are the sets of classes, instances, and properties, respectively.
+$H^C$ represents the hierarchical relationships of classes.
+A Taxonomy includes two types of relationships, which are \textit{subClassOf} of class-class and \textit{instanceOf} of class-instance.
 
@@
 In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources.
-Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including concept list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting.
+Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting.
 We then enrich the extracted language-link set $CL$ using an link-discovery extension method.
@@
 Semantic data extraction aims to achieve a structured dataset from the input encyclopedias, preparing for the knowledge base construction.
-Specifically, we extracts concepts from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.
+Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.
 
-\subsection{Concept Extraction}
+\subsection{Class Extraction}
 \label{sec:ce}
-A concept is defined as a type of similar instances.
-For example, the concept of instance \emph{Interstellar} is \emph{Movie}.
-In general, a concept has super classes and sub classes.
-Concepts comprise a taxonomy which presents a backbone of an ontology.
+A class is defined as a type of similar instances.
+For example, the class of instance \emph{Interstellar} is \emph{Movie}.
+In general, a class has super classes and sub classes.
+Classes comprise a taxonomy which presents a backbone of an ontology.
 In an encyclopedia, a category groups several articles and also has super-categories and sub-categories.
-Therefore we can extract concepts based on existing category system.
+Therefore we can extract classes based on existing category system.
 
@@
     \item Some categories relate to only one or two articles.
-According to the definition of concept, such categories are less representative to a group of instances, therefore it's unwise to retain it as concept.
+According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain it as class.
 \end{itemize}
-   To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original concept hierarchy $H^C$ using the remaining categories.
+   To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original class hierarchy $H^C$ using the remaining categories.
 
@@
 To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
-Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate.
+Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing.
+Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.
 At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.
@@
 \subsection{Cross-lingual Linking}
-There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances.
+There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
@@
 
-In order to make all these encyclopedias link to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers.
+In order to make all these encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
 For instance, we merge instances by the following method: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
@@
 
-The process of unify concept and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
+The process of unify class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
 
@@
 \label{sec:tp}
-As a result of combining multi-source information without verifying, the taxonomy of concept system is mussy.
+As a result of combining multi-source information without verifying, the taxonomy of class system is mussy.
 For example, \textcolor{red}{example}.
@@
 \ref{tab:} shows some examples of correct relations.
-In particular, some language-dependent literal and language-independent structural features are defined to vectorize each concept or instance.
+In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance.
 Employing these features, a Yes-or-Not binary-classification model is trained based on Logistic Regression.
@@
 
-The ideal result of pruning is a tree, whose edges, nodes, and leaves separately denote relations, concepts and instances.
+The ideal result of pruning is a tree, whose edges, nodes, and leaves separately denote relations, classes and instances.
 However, since getting rid of incorrect entity relations without consideration of integrity, a forest result is inevitable.
@@
         \#Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
-        \#Concept  & 982432  & 159705 & 31802   & 1300    \\ \hline
+        \#Class  & 982432  & 159705 & 31802   & 1300    \\ \hline
         \#Property & 43976   & 18842  & 1187    & 139634  \\ \hline
@@
 \centering
-\caption{URIs for concept, instance, property in our knowledge base}
+\caption{URIs for class, instance, property in our knowledge base}
 \label{tab:uris}
@@
         Type     & URI                     \\ \hline
-        Concept  & http://clkb/concept/id  \\ \hline
+        Class  & http://clkb/class/id  \\ \hline
         Instance & http://clkb/instance/id \\ \hline
@@
 \hline
-\multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Concepts}      & \multicolumn{2}{c|}{Instance}                   & \multicolumn{2}{c|}{Property}    \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Classes}      & \multicolumn{2}{c|}{Instance}                   & \multicolumn{2}{c|}{Property}    \\ \hline
 English                & 982,982   & 89.86\%                & 4,311,719              & 37.79\%                & 54,802  & 27.37\%                \\ \hline
@@
 Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike.
-It first learns an ontology based on category system and properties, and then collects 19542 concepts, 2381 properties, 802593 instances.
+It first learns an ontology based on category system and properties, and then collects 19542 classes, 2381 properties, 802593 instances.
 Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g.
@@
 The API is available to over 200 languages and more than 16 million words and names.
-UWN provides semantic relationship of list of word meanings for Aya's work on conceptual search \cite{al2015conceptual}
+UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015classual}
 
@@
 To refine our dataset, we also conduct pruning work on taxonomy.
-Finally, we acquire a knowledge base containing XXX concepts, XXX instances and XXX properties.
+Finally, we acquire a knowledge base containing XXX classes, XXX instances and XXX properties.
 Currently, a SPARQL query interface is provided to access the knowledge base.

### 2015-06-03 nlpcc/paper.tex
修改result

--- 2015-06-02 nlpcc/paper.tex
@@
 
-Our knowledge graph is organized in Openlink Virtuoso, which is a data management platform covering various server, including triple store.
+Our knowledge graph is organized in Openlink Virtuoso, which is a data management platform rendering various services, including triple store.
 
@@
 Beside these user-friendly pages, we provide two ways to access our knowledge base: via the search engine shown in Fig.\ref{fig:search-engine}, or via SPARQL endpoint shown in Fig.\ref{fig:sparql-endpoint}.
-For users who know little about semantic web, they can query by inputing related text into searchbox and search to get entities with similar label.
+For general users, they can make a query by inputing related text into searchbox and search to get entities with similar label.
 To present practicable result, An index is generated over all entities.
@@
 Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.
+For example, to get the English label of an instance, the query is: select * where {<http://xlore.org/instance/100> <http://www.w3.org/2000/01/rdf-schema#label> ?label.
+filter(langMatches(?label),"en"))}.
+
 %\begin{figure}

### 2015-06-03 nlpcc/paper.tex

--- 2015-06-03 nlpcc/paper.tex
@@
 \begin{abstract}
+
 Cross-lingual Knowledge Bases are important for global knowledge sharing.
@@
 \subsection{Cross-lingual Knowledge Base Building}
+
 In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources.
@@
 \end{itemize}
+
    To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original class hierarchy $H^C$ using the remaining categories.
@@
 \label{sec:clkbb}
+
 To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing.
-Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.
+Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
+Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate.
 At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.
@@
 \subsection{Cross-lingual Linking}
-There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
+There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances.
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
 With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.
+
+However, due to using templates, Infobox-properties have no obvious cross-lingual links.
+To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
+That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
 
@@
 \label{sec:tp}
+
 As a result of combining multi-source information without verifying, the taxonomy of class system is mussy.
@@
 \label{sec:con}
+
 This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources.

### 2015-06-04 nlpcc/paper.tex
自己改了一半

@@
 Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB.
-Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.
+Moreover, the paper provides webpages for knowledge visualization and a SPARQL endpoint accessing to the established CLKB.
 
@@
 With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing.
-Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge} and many other applications.
+Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{fernandez2011generic,kaminskas2012knowledge} and many other applications.
 These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.
@@
 However, to build an practical knowledge base, some problems must be addressed: (1) The imbalance of different language source size leads to less entities.
-Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
+Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand respectively, it's obvious that structuring a Chinese knowledge base based on Wikipedia-only is difficult.
 (2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base.
-Statistically, only XX\% articles have cross-lingual links between English and Chinese in all articles of the two languages.
-Especially scarce evident links for infobox attribute.
+Statistically, only XX\% articles have Chinese-English links among all articles in the two languages.
 (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
@@
 To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information.
-In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX classes, XXX instances and XXX properties.
+In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base(CLKB), which contains XXX classes, XXX instances and XXX properties.
 During the whole procedure, we also expand language links and make judgement on the semantic relations.
-Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our knowledge base.
+Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our CLKB.
 Specifically, our work makes the following contributions:
@@
 Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
-  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
+  \item We extend the language link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to obtain more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
   \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:pd} introduces the related classes and defines the problem of building a cross-lingual knowledge base.
+Section \ref{sec:pd} introduces the related concepts and defines the problem of building a CLKB.
 Section \ref{sec:dp} presents the extraction approaches in class, instance and property level.
@@
 \subsection{Wiki Pages}
-Articles from the four sources are similar in structure.
+Articles from wiki sources are similar in structure.
 Usually they provide two important elements with potential semantic information, category system and articles.
@@
 Besides, each article is linked to one or more categories by \textit{articleOf} relation.
-In general, there are five elements can be exploited in each article page:
+In general, there are six elements can be exploited in each article page:
 \begin{figure}
@@
 \begin{itemize}
-  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
+  \item Title: A title is the label of an entity, which is unique so that it can be used to distinguish entities.
   \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
@@
 Information in this table includes important properties of an entity.
-  \item Links: Links are entries to other articles within the encyclopedia.
-They lead readers to reference articles.
-Actually, they represent the relations between the current article and other articles.
+  \item Links: Links are entries to other articles within the encyclopedia. They represent the relations between the current article and others.
   \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
@@
 An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
-We denote infobox template as $T(a)$.
+We denote infobox template used in article $a$ as $T(a)$.
 Templates specify certain attributes, which are usually different from those displayed on the webpage.
@@
 Fig.
-\ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page.
-As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
-Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.
+\ref{fig:interstellar}shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
+As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese respectively.
+Thus, to a $cl \in CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.
 
@@
 
-A cross-lingual knowledge base is a database conform to a cross-lingual ontology.
+A Cross-lingual Knowledge Base(CLKB) is a database conform to a cross-lingual ontology.
 Taking advantage of language links in $CL$, several monolingual-ontologies generated from various sources can be merge into one cross-lingual ontology.
@@
 
-In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources.
+In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese encyclopedia sources.
 Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting.
@@
 We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
-Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.
+Our final output is an Chinese-English ontology with SPARQL endpoint through process of combining $O_{i}$ by utilizing language links in $CL$.
 
@@
 Going through the process of taxonomy pruning, we delete some incorrect relations.
-At last Using the extended language links, we combine the four ontologies into a cross-lingual knowledge base.
+At last using the extended language links, we combine the four ontologies into our .
 
@@
 \label{sec:dp}
-Semantic data extraction aims to achieve a structured dataset from the input encyclopedias, preparing for the knowledge base construction.
-Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.
+Semantic data extraction aims to achieve a structured dataset from the input encyclopedias.
+Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and their templates.
 
@@
 General-properties describe general information of an entity.
-We define three datatype properties as general-properties for a given article $a$: (1) label property; (2) abstract property; (3) URL property.
+We define three datatype properties as general-properties for a given article: (1) label property; (2) abstract property; (3) URL property.
 
@@
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
-Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.
+Meanwhile, 导演(directed by) is an object property because its value points to a person who directed the movie.
 
@@
 The left is infobox, the middle is a snap from dump file in Wikipedia.
-As we've seen, attribute label in infobox is different from it in dump file.
 We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
@@
 Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels.
-For example, \emph{population} property has sub-properties "-Density" and "-Urban".
-In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
+For example, attribute \emph{population} has sub-attribute "-Density" and "-Urban".
+In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong attribute labels by mistake.
 \end{itemize}
@@
 Specifically, Wikipedia institutes rules of rendering label in templates.
-For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from.
+Rright of Fig.\ref{fig:infobox-template} shows an example of template \emph{Infobox film}, where corresponding relations of display labels and dump labels come from.
 When a dump label occurs in dump file, we replace it by its mapping display label.
@@
 
-We harvest four types of information during this stage.
-(1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value.
+We harvest four types of information during this stage: (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value.
 (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page.
-For example, 美国科幻片(American science fiction films) is a category of Interstellar; (4) Reference relation with other instances according to links in the content.
-We gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).
+For example, \textit{美国科幻片(American science fiction films)} is a category of \textit{Interstellar}; (4) Reference relation $Li(a)$ with other instances according to links in the content, such as \textit{华纳兄弟(Warner Bros.)} of \textit{Interstellar}.
 
@@
 
-To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
-Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate.
-At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.
+To construct a CLKB with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
+Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing.
+Thirdly, we prune the taxonomy generated from classes relationships to make it more accurate.
 
 \subsection{Cross-lingual Linking}
-There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances.
+There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
@@
 However, due to using templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
-That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+Thus we take the following steps to solve the problem: (1) Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.
+That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
 

### 2015-06-06 nlpcc/paper.tex
自己改了点细节

@@
 (2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base.
-Statistically, only XX\% articles have Chinese-English links among all articles in the two languages.
+Statistically, only 9\% articles have Chinese-English links among all articles in the two languages.
 (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
@@
 
-However, due to using templates, Infobox-properties have no obvious cross-lingual links.
-Thus we take the following steps to solve the problem: (1) Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.
-That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
-
-However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps:
+However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus we take the following steps to solve the problem: 
 \begin{enumerate}[1)]
-    \item Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
-That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
-    \item Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label;
-    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.
+That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
+    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
+    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
 \end{enumerate}
 
-In order to make all these encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
-For instance, we merge instances by the following method: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
-(2) To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$.
-If exists, make the two as one instance and identify it using an ID, else number it with an new ID.
+In order to make all encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
+For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
+(2) To a $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$.
+If exists, make the two as one instance and identify it using an ID, else number it with a new ID.
 
-After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain just monolingual information.
-
-The process of unify class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
+The process of unifying class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
 
@@
 
-As a result of combining multi-source information without verifying, the taxonomy of class system is mussy.
+As a result of combining multi-source information without verifying, there is noise in taxonomy.
 For example, \textcolor{red}{example}.
@@
 In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance.
-Employing these features, a Yes-or-Not binary-classification model is trained based on Logistic Regression.
+Employing these features, a Yes-or-No binary-classification model is trained based on Logistic Regression.
 The whole process is iterative by retraining model with assured result to get higher precision.
-Confirming a right \textit{subClassOf} or \textit{instanceOf} not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.
+The prediction results are validated by cross-lingual information.
 
-The ideal result of pruning is a tree, whose edges, nodes, and leaves separately denote relations, classes and instances.
+The ideal result after pruning is a tree, whose edges, nodes, and leaves separately denote relations, classes and instances.
 However, since getting rid of incorrect entity relations without consideration of integrity, a forest result is inevitable.
@@
 \subsection{Extracted Knowledge Base}
-We collect the resources from 4 wiki sites, English and Chinese Wikipedia dump files in April, 2015, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
+We collect the resources from 4 wiki sites, English and Chinese Wikipedia dump files in Dec, 2014, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
 Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles.
 We extract each raw data, then form the extracted information into well-structured data.
-Table \ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.
+Table \ref{tab:extract-result} the result we get after elementary extraction on 4 different wiki sources.
 
@@
 
-To build a knowledge base, we create URIs to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.
-Table \ref{tab:uris} lists the defined URIs.
+Besides, we obtain 227 thousand language links between English and Chinese in Wikipeidia, and increase the number by 191 thousand enwiki-baidu language links.
+
+We create URIs to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base. Table \ref{tab:uris} lists the defined URIs.
 \begin{table}[h]
@@
 DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world.
-It's extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
-This knowledge base is widely applied in many domains, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
+It extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
+This knowledge base is widely applied in many domains, including media recommendation \cite{fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
 Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
@@
 \label{sec:con}
-
-This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources.
+This paper presents a procedure of building a Chinese-English CLKB from four encyclopedia sources.
 At first, we extract structured information and unify data format.
-Then a cross-lingual language link set is generated to help combine the bilingual sources.
-Besides, an extension method is applied to enrich the links.
+Then a cross-lingual language link set is generated and expanded to help combine the bilingual sources.
 To refine our dataset, we also conduct pruning work on taxonomy.
-Finally, we acquire a knowledge base containing XXX classes, XXX instances and XXX properties.
-Currently, a SPARQL query interface is provided to access the knowledge base.
+Finally, we acquire a CLKB containing XXX classes, XXX instances and XXX properties.
+Currently, a website and SPARQL query interface is provided to access the knowledge base.
 

### 2015-06-06 nlpcc/paper.tex
老大的修改

--- 2015-06-03 nlpcc/paper.tex
@@
 \documentclass[runningheads,a4paper]{llncs}
-
-\usepackage{xeCJK}
-\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
-\setCJKsansfont[BoldFont=STHeiti]
-\setCJKmonofont{STFangsong}
-
-%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
-%\setCJKmainfont[BoldFont=SimHei]{SimSun}
-%\setCJKmonofont{SimSun}% 设置缺省中文字体
-%\usepackage{CJKutf8}
 
@@
 \usepackage{color}
-%\usepackage{CJK}
-
+\usepackage{CJK}
 \usepackage{url}
@@
 
-\urldef{\mailthu}\path|{lmy13@}tsinghua.edu.cn|
-\urldef{\mailsy}\path|{fantasysy@}sina.com|
+\urldef{\mailthu}\path|{lmy13}@tsinghua.edu.cn|
+\urldef{\mailsy}\path|{fantasysy}@sina.com|
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip\noindent\keywordname\enspace\ignorespaces#1}
@@
 \begin{document}
-%\begin{CJK*}{UTF8}{simsun}
+\begin{CJK*}{UTF8}{song}
 \mainmatter
@@
 \section{Introduction}
-With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing.
-Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge} and many other applications.
-These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.
 
-DBpedia, the nucleus of LOD, extracts structured information from Wikipedia and contains approximately 38.3 million things.
-Now DBpedia provides 124 versions of non-English language including Chinese.
-However, there are only XXX instances and 11 classes in Chinese.
-Compared with the 4.58 million things in English, the quantity of Chinese information is obviously insufficient for further research and application.
+As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions.
+Multilingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering.
+DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}} in XXX different languages, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}.
+Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.
 
-A cross-lingual knowledge base can effectively promote global knowledge sharing, understanding and expanding.
-However, to build an practical knowledge base, some problems must be addressed: (1) The imbalance of different language source size leads to less entities.
-Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging.
-(2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base.
-Statistically, only XX\% articles have cross-lingual links between English and Chinese in all articles of the two languages.
-Especially scarce evident links for infobox attribute.
-(3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy.
-For example,\textcolor{red}{example}
+However, most non-English knowledge in those knowledge bases is pretty scarce.
+Figure \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions.
+Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia.
+For instance, DBpedia contains XXX English instances but only XXX Chinese instances.
+On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia.
+If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an English-Chinese knowledge base with much higher coverage in Chinese can be constructed.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=11cm]{fig_stat.png}\\
+  \caption{Number of Articles on Major Wikipedias, Baidu Baike and Hudong Baike}
+  \label{fig_stat}
+\end{figure}
 
-%In Semantic Web, a large-scale multilingual knowledge base can help …
+To enrich the Chinese knowledge, we try to build a large-scale English-Chinese knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike.
+In this paper, we propose a unified framework to build such a knowledge base.
+The framework contains XXX steps: XXX, XXX, and XXXX.
+The generated knowledge base contains XXX classes, XXX instances and XXX properties.
+An online system supporting keyword search and SPARQL endpoint is also developed.
 
-%Thus it’s significant to build a Chinese-English knowledge base and benefit from it.
+This non-trivial task poses the challenges as follows.
+\begin{enumerate}
+  \item The cross-lingual links are highly limited inside Wikipedia.
+For instance, there are only XXX English-Chinese links in Wikipedia.
+How could we find enough English-Chinese \verb"owl:sameAs" relations?
+  \item The subsumption relations of the online wikis' category systems contain lots of noise.
+For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly.
+How could we detect those incorrect semantic relations?
+\end{enumerate}
 
-Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike.
-To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information.
-In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX classes, XXX instances and XXX properties.
-During the whole procedure, we also expand language links and make judgement on the semantic relations.
-Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our knowledge base.
-Specifically, our work makes the following contributions:
-\begin{itemize}
-  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedia.
-Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
+Driven by these challenges, we propose a unified framework to build a English-Chinese knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
+\begin{enumerate}
   \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
@@
   \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
-\end{itemize}
+\end{enumerate}
 
 The rest of the paper is organized as follows.
-Section \ref{sec:pd} introduces the related classes and defines the problem of building a cross-lingual knowledge base.
-Section \ref{sec:dp} presents the extraction approaches in class, instance and property level.
-Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result.
-Section \ref{sec:result} demonstrates the data situation of established knowledge base.
-Section \ref{sec:work} reviews the related literatures.
-Section \ref{sec:con} concludes this paper and points out some future directions of this work.
+Section \ref{sec:pd} presents some basic concepts and the problem formulation.
+In Section \ref{sec:dp} we presents we present our detailed approaches.
+The experimental results are reported in Section \ref{sec:result}.
+Some related work are described in Section \ref{sec:work}.
+Finally we conclude our work in Section \ref{sec:con}.
 
@@
 Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.
-For example, to get the English label of an instance, the query is: select * where {<http://xlore.org/instance/100> <http://www.w3.org/2000/01/rdf-schema#label> ?label.
+For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
 filter(langMatches(?label),"en"))}.
@@
 
-%\end{CJK*}
+\end{CJK*}
 \end{document}

### 2015-06-06 nlpcc/paper.tex

@@
 \begin{enumerate}[1)]
-    \item Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
-That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
-    \item Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label;
-    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
+    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.
+That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
+    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
+    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
 \end{enumerate}
 
-In order to make all these encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
-For instance, we merge instances by the following method: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
-(2) To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$.
-If exists, make the two as one instance and identify it using an ID, else number it with an new ID.
+In order to make all encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
+For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
+(2) To a $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$.
+If exists, make the two as one instance and identify it using an ID, else number it with a new ID.
 
-After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain just monolingual information.
-
-The process of unify class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
+The process of unifying class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
 

### 2015-06-06 nlpcc/paper.tex
加了数据

@@
 \urldef{\mailsy}\path|{fantasysy}@sina.com|
+\urldef{\mailgmail}\path|{meeya.yx, shiyao, wangzigo}@gmail.com|
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip\noindent\keywordname\enspace\ignorespaces#1}
@@
 
-\title{Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia}
-\titlerunning{Bilingual Knowledge Base}
-\author{Mingyang Li$^\dag$ \and Yao Shi$^\dag$ \and Zhigang Wang$^\dag$}
-\authorrunning{Mingyang Li et.al}
+\title{Building Large-Scale Cross-lingual Knowledge Base from Multi-Wiki}
+%\titlerunning{Bilingual Knowledge Base}
+%\author{Mingyang Li$^\dag$ \and Yao Shi$^\dag$ \and Zhigang Wang$^\dag$}
+%\authorrunning{Mingyang Li et.al}
 
-\institute{$^\dag$Tsinghua National Laboratory for Information Science and Technology,\\
-Department of Computer Science and Technology,\\
-Tsinghua University, Beijing 100084, China\\
-\mailthu\\
-\mailsy\\
-}
+%\institute{$^\dag$ Department of Computer Science and Technology,\\
+%Tsinghua University, Beijing 100084, China\\
+%\mailgmail\\
+%}
 
@@
 \begin{abstract}
-
 Cross-lingual Knowledge Bases are important for global knowledge sharing.
@@
 An extension method is used to increase language links while a pruning approach is used to refine taxonomy.
-Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB.
-Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.
+Totally, there are 663,740 classes, 11,721,238 instances, 56,449 properties referred in the CLKB.
+Moreover, the paper provides visualization of knowledge and a SPARQL endpoint accessing to the established CLKB.
 
-\keywords{Knowledge Base, Semantic Web, Ontology, Cross-lingual}
+\keywords{Knowledge Base, Semantic Web, Taxonomy, Cross-lingual}
 \end{abstract}
@@
 \section{Introduction}
-
 As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions.
 Multilingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering.
-DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}} in XXX different languages, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}.
+DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}} in 125 different languages, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}.
 Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.
@@
 Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia.
-For instance, DBpedia contains XXX English instances but only XXX Chinese instances.
+For instance, DBpedia contains 4.58 million English instances but only XXX Chinese instances.
 On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia.
@@
 \centering
-  \includegraphics[width=11cm]{fig_stat.png}\\
+  \includegraphics[width=11cm]{fig/fig_stat.png}\\
   \caption{Number of Articles on Major Wikipedias, Baidu Baike and Hudong Baike}
@@
 In this paper, we propose a unified framework to build such a knowledge base.
-The framework contains XXX steps: XXX, XXX, and XXXX.
-The generated knowledge base contains XXX classes, XXX instances and XXX properties.
+The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relation.
+The generated knowledge base contains 663,740 classes, 11,721,238 instances and 56,449 properties.
 An online system supporting keyword search and SPARQL endpoint is also developed.
 
-This non-trivial task poses the challenges as follows.
+This non-trivial task poses the challenges as follows:
 \begin{enumerate}
   \item The cross-lingual links are highly limited inside Wikipedia.
-For instance, there are only XXX English-Chinese links in Wikipedia.
+For instance, there are only 9\% English-Chinese matched articles in Wikipedia in all articles.
 How could we find enough English-Chinese \verb"owl:sameAs" relations?
@@
 \begin{enumerate}
+  \item We achieve refined datasets from multiple heterogeneous online wikis through unified extracting process. 
   \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
   \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
-  \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
+  \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
 \end{enumerate}
@@
 Section \ref{sec:pd} presents some basic concepts and the problem formulation.
-In Section \ref{sec:dp} we presents we present our detailed approaches.
+In Section \ref{sec:dp} we present detailed approaches.
+Section \ref{clkbb} describes cross-lingual integration.
 The experimental results are reported in Section \ref{sec:result}.
-Some related work are described in Section \ref{sec:work}.
+Some related work are given in Section \ref{sec:work}.
 Finally we conclude our work in Section \ref{sec:con}.
 
-\section{Problem Definition}
+\section{Preliminaries}
 \label{sec:pd}
@@
 
-\subsection{Encyclopedias}
-\label{sec:encyclopedias}
-\subsubsection{Wikipedia}
+\subsection{Basic Concepts}
+\subsubsection{Online Wikis}
 Nowadays, Wikipedia is the largest data store of human knowledge.
@@
 Information in this table includes important properties of an entity.
-  \item Links: Links are entries to other articles within the encyclopedia.
-They lead readers to reference articles.
-Actually, they represent the relations between the current article and other articles.
+  \item Links: Links are entries to other articles within the encyclopedia. They lead readers to reference articles. 
   \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
@@
 \begin{figure}[ht]
-    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
+    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
     \caption{Procedure of building our cross-lingual knowledge base}
@@
 \multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Classes}     & \multicolumn{2}{c|}{Instance}                   & \multicolumn{2}{c|}{Property}    \\ \hline
-English                & 982,982   & 89.86\%                & 4,311,719              & 37.79\%                & 54,802  & 27.37\%                \\ \hline
-Chinese                & 176,648   & 16.15\%                & 7,842,117              & 66.9\%                 & 167,083 & 83.45\%                \\ \hline
-Cross-lingual          & 65,775    & 6.01\%                 & 432,598                & 3.7\%                  & 21,662  & 10.82\%                \\ \hline
-Only English           & 917,207   & 83.9\%                 & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 33140   & 16.6\%                 \\ \hline
-Only Chinese           & 110,873   & 10.1\%                 & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 145,421 & 72.6\%                 \\ \hline
-Sum                    & 1,093,855 & \multicolumn{1}{c|}{-} & 11,721,238             & \multicolumn{1}{c|}{-} & 200,223 & \multicolumn{1}{c|}{-} \\ \hline
+English                & 639,020 & 96.26\%                & 4,311,719              & 37.79\%                & 15,380  & 27.24\%                \\ \hline
+Chinese                & 88,615  & 13.35\%                & 7,842,117              & 66.9\%                 & 51,618  & 91.44\%                \\ \hline
+Cross-lingual          & 63,895  & 9.63\%                 & 432,598                & 3.7\%                  & 10,549  & 18.69\%                \\ \hline
+Only English           & 575,125 & 86.65\%                & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 4,831   & 8.56\%                 \\ \hline
+Only Chinese           & 24,720  & 3.72\%                 & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 41,069  & 72.75\%                \\ \hline
+Total                  & 663,740 & \multicolumn{1}{c|}{-} & 11,721,238             & \multicolumn{1}{c|}{-} & 56,449  & \multicolumn{1}{c|}{-} \\ \hline
 \end{tabular}
@@
 
-%\begin{figure}
-%    \centering
-%    \begin{minipage}[t]{0.8\textwidth}
-%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
-%        \caption{A Sample Query for Using Search Box }
-%        \label{fig:search-engine}
-%    \end{minipage}%
-%    \begin{minipage}[t]{0.8\textwidth}
-%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
-%        \caption{A SPARQL Sample Query over the Knowledge Base}
-%        \label{fig:sparql-endpoint}
-%    \end{minipage}%
-%\end{figure}
+\begin{figure}
+    \centering
+    \begin{minipage}[t]{0.8\textwidth}
+        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
+        \caption{A Sample Query for Using Search Box }
+        \label{fig:search-engine}
+    \end{minipage}%
+    \begin{minipage}[t]{0.8\textwidth}
+        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
+        \caption{A SPARQL Sample Query over the Knowledge Base}
+        \label{fig:sparql-endpoint}
+    \end{minipage}%
+\end{figure}
 

### 2015-06-06 nlpcc/paper.tex
丢失的改动。 删了两张图片

@@
 On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia.
-If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an English-Chinese knowledge base with much higher coverage in Chinese can be constructed.
+If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.
 \begin{figure}[h]
@@
 
-To enrich the Chinese knowledge, we try to build a large-scale English-Chinese knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike.
+To enrich the Chinese knowledge, we try to build a large-scale Chinese-English knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike.
 In this paper, we propose a unified framework to build such a knowledge base.
@@
   \item The cross-lingual links are highly limited inside Wikipedia.
-For instance, there are only 9\% English-Chinese matched articles in Wikipedia in all articles.
-How could we find enough English-Chinese \verb"owl:sameAs" relations?
+For instance, there are only 9\% Chinese-English matched articles in Wikipedia in all articles.
+How could we find enough Chinese-English \verb"owl:sameAs" relations?
   \item The subsumption relations of the online wikis' category systems contain lots of noise.
@@
 
-Driven by these challenges, we propose a unified framework to build a English-Chinese knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
+Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
 \begin{enumerate}
@@
 \subsection{Wiki Pages}
-Articles from the four sources are similar in structure.
+Articles from the wiki sources are similar in structure.
 Usually they provide two important elements with potential semantic information, category system and articles.
 A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}.
-Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy.
 An article describes an entity with rich information created and modified by several verified editors.
 Besides, each article is linked to one or more categories by \textit{articleOf} relation.
-In general, there are five elements can be exploited in each article page:
-\begin{figure}
-    \centering
-    \begin{minipage}[t]{0.8\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
-        \caption{Taxonomy in Hudong}
-        \label{fig:hudong-taxonomy}
-    \end{minipage}%
-\end{figure}
+In general, there are six elements can be exploited in each article page:
+%\begin{figure}
+%    \centering
+%    \begin{minipage}[t]{0.8\textwidth}
+%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
+%        \caption{Taxonomy in Hudong}
+%        \label{fig:hudong-taxonomy}
+%    \end{minipage}%
+%\end{figure}
 \begin{itemize}
@@
 Information in this table includes important properties of an entity.
-  \item Links: Links are entries to other articles within the encyclopedia. They lead readers to reference articles. 
+  \item Links: Links are entries to other articles within the encyclopedia. They represent the relations between the current article and others.
   \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
@@
 
-Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
-\begin{figure}[ht]
-    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
-    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
-    \label{fig:interstellar}
-\end{figure}%
-
+%Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
+%\begin{figure}[ht]
+%    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
+%    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
+%    \label{fig:interstellar}
+%\end{figure}%
+%
 The elements of each article $a$ can be defined as follow:
@@
 Fig.
-\ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page.
+\ref{fig:interstellar}shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
 As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
-Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.
+Thus, to a $cl \in CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.
 
@@
 We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
-Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.
+Our final output is an Chinese-English ontology  with SPARQL endpoint though process of combining $O_{i}$ by utilizing language links in $CL$.
 
@@
 Going through the process of taxonomy pruning, we delete some incorrect relations.
-At last Using the extended language links, we combine the four ontologies into a cross-lingual knowledge base.
+At last using the extended language links, we combine the four ontologies into our CLKB
 
@@
 \label{sec:dp}
-Semantic data extraction aims to achieve a structured dataset from the input encyclopedias, preparing for the knowledge base construction.
-Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.
+Semantic data extraction aims to achieve a structured dataset from the input encyclopedias.
+Specifically, we extract classes from category system, instances according to articles, and properties based on infoboxes and their templates.
 
@@
 Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels.
-For example, \emph{population} property has sub-properties "-Density" and "-Urban".
+For example, attribute \emph{population} property has sub-properties "-Density" and "-Urban".
 In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
@@
 Specifically, Wikipedia institutes rules of rendering label in templates.
-For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from.
+Right of Fig.\ref{fig:infobox-template} shows an example of template \emph{Infobox film}, where corresponding relations of display labels and dump labels come from.
 When a dump label occurs in dump file, we replace it by its mapping display label.
@@
 (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page.
-For example, 美国科幻片(American science fiction films) is a category of Interstellar; (4) Reference relation with other instances according to links in the content.
-We gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).
+For example, \textit{美国电影作品(American films)} is a category of \textit{Frozen}; (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).
 
@@
 
-To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing.
-Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate.
-At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.
+To construct a CLKB with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
+Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing.
+Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.
 
 \subsection{Cross-lingual Linking}
-There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances.
+There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
@@
 
-However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps:
-\begin{enumerate}[1)]
+However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to solve the problem:
     \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.

### 2015-06-07 nlpcc/paper.tex
删了uri table

@@
 
+\usepackage{xeCJK}
+\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
+\setCJKsansfont[BoldFont=STHeiti]
+\setCJKmonofont{STFangsong}
+
+%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
+%\setCJKmainfont[BoldFont=SimHei]{SimSun}
+%\setCJKmonofont{SimSun}% 设置缺省中文字体
+%\usepackage{CJKutf8}
+
 \urldef{\mailthu}\path|{lmy13}@tsinghua.edu.cn|
@@
 \begin{document}
-\begin{CJK*}{UTF8}{song}
+%\begin{CJK*}{UTF8}{song}
 \mainmatter
@@
 
-\begin{table}[h]
+\begin{table}[]
     \small
@@
 
-We create URIs to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base. Table \ref{tab:uris} lists the defined URIs.
-\begin{table}[h]
-\small
-\centering
-\caption{URIs for class, instance, property in our knowledge base}
-\label{tab:uris}
-    \begin{tabular}{|c|c|}
-        \hline
-        Type     & URI                     \\ \hline
-        Class    & http://clkb/class/id    \\ \hline
-        Instance & http://clkb/instance/id \\ \hline
-        Property & http://clkb/property/id \\ \hline
-    \end{tabular}
-\end{table}
+We create URIs \uri{http://clkb/type/id} (type could be \textit{class}, \textit{instance}, \textit{property}) to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.
 
@@
 \begin{figure}
-    \centering
-    \begin{minipage}[t]{0.8\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
-        \caption{A Sample Query for Using Search Box }
+    \begin{minipage}[t]{0.5\textwidth}
+        \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/search-engine}}
+        \caption{A picture of Search Box}
         \label{fig:search-engine}
     \end{minipage}%
-    \begin{minipage}[t]{0.8\textwidth}
-        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
-        \caption{A SPARQL Sample Query over the Knowledge Base}
+    \begin{minipage}[t]{0.5\textwidth}
+        \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/sparql-endpoint}}
+        \caption{A SPARQL Sample Query}
         \label{fig:sparql-endpoint}
@@
 Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike.
-It first learns an ontology based on category system and properties, and then collects 19542 classes, 2381 properties, 802593 instances.
+It first learns an ontology based on category system and properties, and then collects 19,542 classes, 2,381 properties, 802,593 instances.
 Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g.
@@
 To refine our dataset, we also conduct pruning work on taxonomy.
-Finally, we acquire a CLKB containing XXX classes, XXX instances and XXX properties.
+Finally, we acquire a CLKB containing 663,740 classes, 11,721,238 instances and 56,449 properties.
 Currently, a website and SPARQL query interface is provided to access the knowledge base.
@@
 
-\end{CJK*}
+%\end{CJK*}
 \end{document}

### 2015-06-07 nlpcc/paper.tex
大师兄调的格式

@@
 \usepackage[ruled]{algorithm2e}
-\usepackage{amsmath}
 \usepackage{graphicx}
+\usepackage{subfigure}
 \usepackage{enumerate}
@@
 
-\usepackage{xeCJK}
-\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
-\setCJKsansfont[BoldFont=STHeiti]
-\setCJKmonofont{STFangsong}
-
-%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
-%\setCJKmainfont[BoldFont=SimHei]{SimSun}
-%\setCJKmonofont{SimSun}% 设置缺省中文字体
-%\usepackage{CJKutf8}
+%\usepackage{xeCJK}
+%\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
+%\setCJKsansfont[BoldFont=STHeiti]
+%\setCJKmonofont{STFangsong}
 
@@
 \begin{document}
-%\begin{CJK*}{UTF8}{song}
+\begin{CJK*}{UTF8}{song}
 \mainmatter
@@
 If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.
-\begin{figure}[h]
+
+\begin{figure}[ht]
 \centering
-  \includegraphics[width=11cm]{fig/fig_stat.png}\\
+\includegraphics[width=0.75 \columnwidth]{fig/fig_stat.png}
 \caption{Number of Articles on Major Wikipedias, Baidu Baike and Hudong Baike}
@@
   \item The subsumption relations of the online wikis' category systems contain lots of noise.
-For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly.
+For example, in English Wikipedia "Wikipedia-books-on-people", which is actually \verb"subClassOf" "Books", is taken as the sub-category of "People" mistakenly.
 How could we detect those incorrect semantic relations?
@@
   \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
+  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.% in ontology.
   \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
@@
 
-The rest of the paper is organized as follows.
+%The rest of the paper is organized as follows.
 Section \ref{sec:pd} presents some basic concepts and the problem formulation.
@@
 \subsection{Basic Concepts}
-\subsubsection{Online Wikis}
-Nowadays, Wikipedia is the largest data store of human knowledge.
+\para{Online Wikis.} Nowadays, Wikipedia is the largest data store of human knowledge.
 It was launched in 2001 and has hold over 35 million articles in 288 languages by 2015.
@@
 Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article.
-Fig.
-\ref{fig:interstellar}shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
+%Fig.
+\ref{fig:interstellar} shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
 As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
@@
 Our final output is an Chinese-English ontology with SPARQL endpoint though process of combining $O_{i}$ by utilizing language links in $CL$.
-
-The whole building procedure is shown in Fig. \ref{fig:procedure}
+\vspace{-0.5cm}
 \begin{figure}[ht]
@@
     \label{fig:procedure}
-\end{figure}%
+\end{figure}
+\vspace{-0.5cm}
+
+The whole building procedure is shown in Fig.
+\ref{fig:procedure}.
 We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
@@
 Going through the process of taxonomy pruning, we delete some incorrect relations.
-At last using the extended language links, we combine the four ontologies into our CLKB
+At last using the extended language links, we combine the four ontologies into our CLKB.
 
@@
 
-\subsubsection{General-properties}
-Characteristics of an entity are regarded as general-properties, including label, abstract, and url.
+\para{General-properties.} Characteristics of an entity are regarded as general properties, including label, abstract, and url.
 General-properties describe general information of an entity.
@@
 
-\subsubsection{Infobox-properties}
-Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
+\para{Infobox-properties.} Attributes acquired from infobox are considered as infobox properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
 The type of a property, datatype or object, depends on the type of the value.
@@
 However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to solve the problem:
+\begin{enumerate}
     \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.
@@
 Therefore, we introduce the method from\cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}.
-Table.
+%Table.
 \ref{tab:} shows some examples of correct relations.
@@
 Table \ref{tab:extract-result} the result we get after elementary extraction on 4 different wiki sources.
-
-\begin{table}[]
+Besides, we obtain 227 thousand language links between English and Chinese in Wikipeidia, and increase the number by 191 thousand enwiki-baidu language links.
+\vspace{-0.5cm}
+\begin{table}[hb]
     \small
@@
                        & Enwiki  & Zhwiki & Hudong  & Baidu   \\ \hline
-            \#Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
-            \#Class    & 982432  & 159705 & 31802   & 1300    \\ \hline
-            \#Property & 43976   & 18842  & 1187    & 139634  \\ \hline
+            \#Instance & 4,304,113 & 662,650 & 5,590,751 & 5,622,404 \\ \hline
+            \#Class    & 982,432  & 159,705 & 31,802   & 1300    \\ \hline
+            \#Property & 43,976   & 18,842  & 1187    & 139,634  \\ \hline
         \end{tabular}
@@
 
-Besides, we obtain 227 thousand language links between English and Chinese in Wikipeidia, and increase the number by 191 thousand enwiki-baidu language links.
-
-We create URIs \uri{http://clkb/type/id} (type could be \textit{class}, \textit{instance}, \textit{property}) to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.
+We create URIs \url{http://clkb/type/id} (type could be \textit{class}, \textit{instance}, \textit{property}) to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.
 
@@
 We give a breakdown of both Chinese knowledge and English knowledge in Table \ref{tab:kb-result}.
-
-\begin{table}[h]
+\vspace{-0.5cm}
+\begin{table}[ht]
 \small
@@
 \end{table}
+\vspace{-0.5cm}
 
@@
 In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
+
 \begin{figure}[ht]
@@
     \label{fig:xlore}
-\end{figure}%
+\end{figure}
+
 Beside these user-friendly pages, we provide two ways to access our knowledge base: via the search engine shown in Fig.\ref{fig:search-engine}, or via SPARQL endpoint shown in Fig.\ref{fig:sparql-endpoint}.
@@
 We as well provide SPARQL interface for professional users to query our knowledge graph.
-Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.
-For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
+Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.%For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
 filter(langMatches(?label),"en"))}.
@@
 \begin{figure}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/search-engine}}
+\centering
+\subfigure[A picture of Search Box]{
+    \label{fig:search-engine}
+    \includegraphics[width=5.5cm,height=3cm]{fig/search-engine}
+    }
+\hspace{0.01cm}
+\subfigure[A SPARQL Sample Query]{
+    \label{fig:sparql-endpoint}
+    \includegraphics[width=5.5cm,height=3cm]{fig/sparql-endpoint}
+    }
 \caption{A picture of Search Box}
-        \label{fig:search-engine}
-    \end{minipage}%
-    \begin{minipage}[t]{0.5\textwidth}
-        \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/sparql-endpoint}}
-        \caption{A SPARQL Sample Query}
-        \label{fig:sparql-endpoint}
-    \end{minipage}%
+\label{fig:access}
+%\begin{minipage}[t]{0.5\textwidth}
+%    \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/search-engine}}
+%    \caption{A picture of Search Box}
+%    \label{fig:search-engine}
+%\end{minipage}%
+%\begin{minipage}[t]{0.5\textwidth}
+%    \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/sparql-endpoint}}
+%    \caption{A SPARQL Sample Query}
+%    \label{fig:sparql-endpoint}
+%\end{minipage}%
 \end{figure}
@@
 In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods.
-\subsection{Chinese Knowledge Bases}
-Currently, several large-scale Chinese knowledge bases have been generated.
+
+\para{Chinese Knowledge Bases.} Currently, several large-scale Chinese knowledge bases have been generated.
 Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first published Chinese large-scale Linking Open Data.
@@
 Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
+
 Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike.
@@
 microblog posts, news pages, images) to enrich the structured knowledge.
-\subsection{Cross-lingual Knowledge Bases}
-DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world.
+
+\para{Cross-lingual Knowledge Bases.} DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world.
 It extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
@@
 The API is available to over 200 languages and more than 16 million words and names.
-UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015classual}
+UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015conceptual}
 

### 2015-06-07 nlpcc/paper.tex
又一版

@@
 
-%\usepackage{xeCJK}
-%\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
-%\setCJKsansfont[BoldFont=STHeiti]
-%\setCJKmonofont{STFangsong}
+\usepackage{xeCJK}
+%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
+\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
+\setCJKsansfont[BoldFont=STHeiti]
+\setCJKmonofont{STFangsong}
+%\usepackage{CJKutf8}
+
+%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
+%\setCJKmainfont[BoldFont=SimHei]{SimSun}
+%\setCJKmonofont{SimSun}% 设置缺省中文字体
 
@@
 \begin{document}
-\begin{CJK*}{UTF8}{song}
+%\begin{CJK*}{UTF8}{song}
 \mainmatter
 
-\title{Building Large-Scale Cross-lingual Knowledge Base from Multi-Wiki}
+\title{Building Large-Scale Cross-Lingual Knowledge Base from Heterogeneous Online Wikis}
 %\titlerunning{Bilingual Knowledge Base}
@@
 Totally, there are 663,740 classes, 11,721,238 instances, 56,449 properties referred in the CLKB.
+Among of them, 507,042 items are cross-lingual linked.
+To the best of our knowledge, it's the first large-scale Chinese-English knowledge base with balanced knowledge quantity.
 Moreover, the paper provides visualization of knowledge and a SPARQL endpoint accessing to the established CLKB.
@@
 Multilingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering.
-DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}} in 125 different languages, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}.
+DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}.
 Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.
@@
 Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia.
-For instance, DBpedia contains 4.58 million English instances but only XXX Chinese instances.
+For instance, DBpedia contains 4.58 million English instances but even no Chinese dataset published.
 On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia.
@@
   \item We achieve refined datasets from multiple heterogeneous online wikis through unified extracting process.
-  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
-  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.% in ontology.
+  \item We extend cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
+  \item We prune the original taxonomy, which is extracted from wiki category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.
   \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
@@
 
-%The rest of the paper is organized as follows.
+The rest of the paper is organized as follows.
 Section \ref{sec:pd} presents some basic concepts and the problem formulation.
-In Section \ref{sec:dp} we present detailed approaches.
-Section \ref{clkbb} describes cross-lingual integration.
+In Section \ref{sec:sde} we present detailed approaches.
+Section \ref{sec:cli} describes cross-lingual integration.
 The experimental results are reported in Section \ref{sec:result}.
@@
 \label{sec:pd}
-In this section, we firstly introduce the encyclopedias used to build and enrich our knowledge base.
-Then we give definitions about ontology and knowledge base.
-At last we describe our task in this work.
+In this section, we give definitions about our knowledge base and describe the task in this work.
 
@@
 The imbalance of different language articles makes ontologies based on Wikipedia-only behave badly in cross-lingual.
-Thus, more Chinese encyclopedias are necessary to enrich Chinese source.
+Thus, more Chinese sources are necessary to enrich Chinese source.
 
-Among the large-scale monolingual Chinese encyclopedias currently, Baidu Baike and Hudong Baike are the most content-rich.
+Among the large-scale monolingual Chinese wikis currently, Baidu Baike and Hudong Baike are the most content-rich.
 Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015.
@@
 
-\subsection{Wiki Pages}
-Articles from the wiki sources are similar in structure.
+\para{Wiki Pages.} Articles from the wiki sources are similar in structure.
 Usually they provide two important elements with potential semantic information, category system and articles.
 A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}.
-An article describes an entity with rich information created and modified by several verified editors.
-Besides, each article is linked to one or more categories by \textit{articleOf} relation.
-In general, there are six elements can be exploited in each article page:
+An article describes an entity with rich information.
+Each article is linked to one or more categories by \textit{articleOf} relation.
+In general, six elements can be exploited in each article page:
 %\begin{figure}
@@
 \begin{itemize}
-  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
+  \item Title: A Title is the label of an entity, whose uniqueness can be used to distinguish entities.
   \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
-  \item Infobox: Most of articles contain infobox.
-An infobox maintains structured data which are subject-attribute-value triples formalized as a table.
-Information in this table includes important properties of an entity.
-  \item Links: Links are entries to other articles within the encyclopedia. They represent the relations between the current article and others.
+  \item Infobox: Most of articles contain infobox. An infobox maintains structured data in subject-attribute-value format.
+  \item Link: Links are entries to other articles within the wiki. They represent the relations between the current article and others.
   \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
@@
 %
-The elements of each article $a$ can be defined as follow:
+An article $a$ can be defined as follow:
 \begin{equation}
@@
 Besides, infoboxes are also generated based on certain templates recommended by Wikipedia.
-For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films.
-An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
+For example, The infobox in film 冰雪奇缘(Frozen) is edited according to the Template \emph{Infobox film}, which maintains a property set of films.
+An infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
 We denote infobox template used in article $a$ as $T(a)$.
@@
 
-Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article.
+Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version articles.
 %Fig.
 \ref{fig:interstellar} shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
-As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately.
-Thus, to a $cl \in CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.
+As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denote the article's language links in English and Chinese. To a $cl \in CL$, $cl(a) = <L_{z}(a), L_{e}(a)>$.
 
-\subsection{Ontology and Knowledge Base}
-
-An ontology is a formal specification of a group of entities. In our work, an ontology is described as a 4-tuple:
+\para{Knowledge Base} A knowledge base is a formal specification of a group of entities. Our knowledge base is described as a 4-tuple:
 \begin{equation}
-    O = <C,I,P,H^C>
+    KB = <C,I,P,H^C>
 \end{equation}
@@
 $H^C$ represents the hierarchical relationships of classes.
-A Taxonomy includes two types of relationships, which are \textit{subClassOf} of class-class and \textit{instanceOf} of class-instance.
+The taxonomy of our knowledge base includes four types of relationships, which are \textit{subClassOf} of class-class, \textit{instanceOf} of class-instance, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.
 
 A Cross-lingual Knowledge Base(CLKB) is a database conform to a cross-lingual ontology.
-Taking advantage of language links in $CL$, several monolingual-ontologies generated from various sources can be merge into one cross-lingual ontology.
-Thus a knowledge base can be defined as:
+Taking advantage of language links in $CL$, several monolingual knowledge bases generated from various sources can be merge into one.
+Thus our Chinese-English knowledge base can be defined as:
 \begin{equation}
-    KB = <O_{i}, CL>
+    CLKB = <KB_{z}, KB_{e}>
 \end{equation}
-where $O_{i}$ denotes the ith monolingual-ontology, $CL$ represents the cross-lingual link set.
+where $KB_{z}$ and $KB_{e}$ denote the monolingual knowledge base in Chinese and English. CLKB combines the two according to $CL$.
 
-\subsection{Cross-lingual Knowledge Base Building}
+\para{Cross-lingual Knowledge Base Building} In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese wiki sources.
+Given an online-wiki $W_{i}$, we get dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each $W_{i}$ by extraction.
+We then enrich the extracted cross-lingual link set $CL$ using an link-discovery extension method.
+We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
+Our final output is an Chinese-English CLKB though process of combining $KB_{z}$ and $KB_{e}$ by utilizing language links in $CL$.
 
-In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese encyclopedia sources.
-Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting.
-We then enrich the extracted language-link set $CL$ using an link-discovery extension method.
-We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
-Our final output is an Chinese-English ontology with SPARQL endpoint though process of combining $O_{i}$ by utilizing language links in $CL$.
+The whole building procedure is shown in Fig.
+\ref{fig:procedure}.
+We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
+Because of heterogeneity, various extractors should be employed.
+After data parsing, we delete incorrect semantic relations by going through taxonomy pruning.
+At last, using the extended cross-lingual links, we combine the four dataset into our CLKB.
+
 \vspace{-0.5cm}
@@
     \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
-    \caption{Procedure of building our cross-lingual knowledge base}
+    \caption{Procedure of Building Our Cross-lingual Knowledge Base}
     \label{fig:procedure}
@@
 
-The whole building procedure is shown in Fig.
-\ref{fig:procedure}.
-We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
-Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed.
-After data parsing, we get four ontologies each source.
-Going through the process of taxonomy pruning, we delete some incorrect relations.
-At last using the extended language links, we combine the four ontologies into our CLKB.
-
 \section{Semantic Data Extraction}
-\label{sec:dp}
-Semantic data extraction aims to achieve a structured dataset from the input encyclopedias.
+\label{sec:sde}
+Semantic data extraction aims to achieve a structured dataset from the input wikis.
 Specifically, we extract classes from category system, instances according to articles, and properties based on infoboxes and their templates.
@@
 A class is defined as a type of similar instances.
-For example, the class of instance \emph{Interstellar} is \emph{Movie}.
+For example, the class of instance \emph{Frozen} is \emph{Film}.
 In general, a class has super classes and sub classes.
 Classes comprise a taxonomy which presents a backbone of an ontology.
-In an encyclopedia, a category groups several articles and also has super-categories and sub-categories.
+In a wiki, a category groups several articles and also has super-categories and sub-categories.
 Therefore we can extract classes based on existing category system.
 
-However, the whole taxonomy can not directly transform from category system because of the following problems:
+However, the whole taxonomy can not directly transform from category system due to the following problems:
 \begin{itemize}
@@
 Meanwhile, in Wikipedia, \textcolor{red}{例子}
-    \item Some categories relate to only one or two articles.
-According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain it as class.
+    \item Some categories relate to only one article.
+According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain them as classes.
 \end{itemize}
 
-To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original class hierarchy $H^C$ using the remaining categories.
+To obtain a more precise $H^C$ in a wiki, we remove categories fit the above situations, then build the original class hierarchy $H^C$ using the remaining categories.
 
-However, among the relations there are still incorrect samples.
-For example, \emph{Tsinghua University} is not an entity of \emph{Haidian District}, but relates to.
-Thus we will prune the taxonomy later.
+%However, among the relations there are still incorrect samples. \textcolor{red}{example}
+%For example, \emph{Frozen} is not an entity of \emph{Disney Princess}, but relates to. Thus we will prune the taxonomy later.
 
@@
 A property is defined as an attribute of an entity.
-It represents the relation between two instances or an instance and its value.
-We divided properties into two types: object property, whose value is an individual, such as \emph{directed by}; datatype property, whose value is a literal text, such as \emph{birth date}.
-Considering both content and infobox of an article, we extract two kinds of properties, general-properties and Infobox-properties.
+It represents the relation between an instance and its value.
+We divided properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 生日(birth date).
+Considering both content and infobox of an article, we extract two kinds of properties, General-properties and Infobox-properties.
 
@@
 The type of a property, datatype or object, depends on the type of the value.
-Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype.
+Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object.
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
@@
     \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file.
-Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Interstellar}' infobox.
-The left is infobox, the middle is a snap from dump file in Wikipedia.
+Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Frozen's} infobox.
+The left is infobox, the middle is a glance from dump file in Wikipedia.
 We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
@@
 Specifically, Wikipedia institutes rules of rendering label in templates.
-Right of Fig.\ref{fig:infobox-template} shows an example of template \emph{Infobox film}, where corresponding relations of display labels and dump labels come from.
+Right of Fig.\ref{fig:infobox-template} shows an example of \emph{Template:Infobox film}, where corresponding relations of display labels and dump labels come from.
 When a dump label occurs in dump file, we replace it by its mapping display label.
@@
 \label{sec:ie}
-In encyclopedia, an article describes unique entity in the world.
+An article describes unique entity in the world.
 Therefore we can extract an article as an instance.
@@
 We harvest four types of information during this stage.
-(1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value.
-(2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page.
-For example, \textit{美国电影作品(American films)} is a category of \textit{Frozen}; (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).
+(1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value; (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page.
+For example, 美国电影作品(American films) is a category of 冰雪奇缘(Frozen); (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).
 
 \section{Cross-lingual Integration}
-\label{sec:clkbb}
+\label{sec:cli}
 
-To construct a CLKB with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set.
-Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing.
+To construct a CLKB with existing structured data, firstly we increase cross-lingual links, which can help match the same entity in two languages.
+Secondly, we integrate this four wikis, that is, respectively merging classes, instances and properties from the four sources if they represent the same thing.
 Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.
@@
 \subsection{Cross-lingual Linking}
-There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
+There are 227 thousand cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
 Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set.
-With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.
+With the linkage factor graph model, we harvest a cross-lingual links extension as many as 215 thousand with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.
 
-However, due to using templates, Infobox-properties have no obvious cross-lingual links.
-To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label.
-That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
-
-However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to solve the problem:
+However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to acquire property links:
 \begin{enumerate}
@@
 
-In order to make all encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
-For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese encyclopedias by instance title.
+In order to make all wikis link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
+For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese wikis by instance title.
 (2) To a $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$.
@@
 
-The process of unifying class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
+The process of unifying class and property is the same as instance. Meanwhile, all the relations are kept to prevent loss of information.
 
 \subsection{Taxonomy Prune}
-\label{sec:tp}
 
-As a result of combining multi-source information without verifying, there is noise in taxonomy.
-For example, \textcolor{red}{example}.
-Therefore, we introduce the method from\cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}.
+As a result of combining multi-source information without verifying, there is noise in taxonomy. %For example:
+Therefore, we introduce the method from \cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}.
 %Table.
@@
 
-The ideal result after pruning is a tree, whose edges, nodes, and leaves separately denote relations, classes and instances.
+The ideal result after pruning is a tree, whose edges, nodes, and leaves respectively denote relations, classes and instances.
 However, since getting rid of incorrect entity relations without consideration of integrity, a forest result is inevitable.
+
+To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut class-instance relations and \textit{relatedTopicOf} for cut class-class relations.
 
@@
 \subsection{Extracted Knowledge Base}
-We collect the resources from 4 wiki sites, English and Chinese Wikipedia dump files in Dec, 2014, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
-Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles.
+We collect the resources from four wiki sites, English and Chinese Wikipedia dump files in May, 2014, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
+Each of the wikis has three types of information, which can be utilized for constructing our knowledge base, namely, specific articles, category system, and attribute of articles.
 We extract each raw data, then form the extracted information into well-structured data.
 Table \ref{tab:extract-result} the result we get after elementary extraction on 4 different wiki sources.
-Besides, we obtain 227 thousand language links between English and Chinese in Wikipeidia, and increase the number by 191 thousand enwiki-baidu language links.
+Besides, we obtain 227 thousand language links between English and Chinese in Wikipeidia, and increase the number by 215 thousand enwiki-baidu language links and 10 thousand property links.
 \vspace{-0.5cm}
@@
 
-After fusing the heterogeneous resources, we harvest a cross-lingual graph with 1,093,855 classes, 200,223 properties, and 11,721,238 instances respectively.
+After fusing the heterogeneous resources, we harvest a cross-lingual graph with 663,740 classes, 56,449 properties, and 11,721,238 instances respectively.
 With different methods of extraction and language link discovery, these three kinds of entries show different results in languages.
@@
 \multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Classes}     & \multicolumn{2}{c|}{Instance}                   & \multicolumn{2}{c|}{Property}    \\ \hline
-English                & 639,020 & 96.26\%                & 4,311,719              & 37.79\%                & 15,380  & 27.24\%                \\ \hline
-Chinese                & 88,615  & 13.35\%                & 7,842,117              & 66.9\%                 & 51,618  & 91.44\%                \\ \hline
-Cross-lingual          & 63,895  & 9.63\%                 & 432,598                & 3.7\%                  & 10,549  & 18.69\%                \\ \hline
-Only English           & 575,125 & 86.65\%                & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 4,831   & 8.56\%                 \\ \hline
-Only Chinese           & 24,720  & 3.72\%                 & \multicolumn{1}{c|}{-} & \multicolumn{1}{c|}{-} & 41,069  & 72.75\%                \\ \hline
+English                & 639,020 & 96.26\%                & 3,879,121              & 38.79\%                & 15,380  & 27.24\%                \\ \hline
+Chinese                & 88,615  & 13.35\%                & 7,409,519              & 68.25\%                & 51,618  & 91.44\%                \\ \hline
+Cross-lingual          & 63,895  & 9.63\%                 & 432,598                & 3.98\%                 & 10,549  & 18.69\%                \\ \hline
+Only English           & 575,125 & 86.65\%                & 3,446,523              & 31.75\%                 & 4,831   & 8.56\%    \\ \hline
+Only Chinese           & 24,720  & 3.72\%                 & 7,409,519              & 64,27\%                  & 41,069  & 72.75\%   \\ \hline
 Total                  & 663,740 & \multicolumn{1}{c|}{-} & 11,721,238             & \multicolumn{1}{c|}{-} & 56,449  & \multicolumn{1}{c|}{-} \\ \hline
@@
 \subsection{Web Access to Knowledge Base}
-We provide a website to present an intuitive graph of our knowledge in the forms of class, instance and property.
-Fig.\ref{fig:xlore} shows sample pages of the integrated data.
-Users can choose language preference which is convenient for both English speaker and Chinese speaker.
-In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.
- In the instance webpage we display bilingual label, super classes, related classes, abstract, property key value pairs, images and references.
-In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
 
@@
 
-Beside these user-friendly pages, we provide two ways to access our knowledge base: via the search engine shown in Fig.\ref{fig:search-engine}, or via SPARQL endpoint shown in Fig.\ref{fig:sparql-endpoint}.
-For general users, they can make a query by inputing related text into searchbox and search to get entities with similar label.
-To present practicable result, An index is generated over all entities.
-We as well provide SPARQL interface for professional users to query our knowledge graph.
-Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.%For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
-filter(langMatches(?label),"en"))}.
+We provide a platform to present an intuitive graph of our knowledge in the forms of class, instance and property.
+Fig.\ref{fig:xlore} shows sample pages of the integrated data.
+Users can choose language preference which is convenient for both English speaker and Chinese speaker.
+In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.
+ In the instance webpage we display bilingual label, super classes, related classes, abstracts, infobox-properties, images and references.
+In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
 
@@
     }
-\caption{A picture of Search Box}
+\caption{Two ways to our knowledge base}
 \label{fig:access}
@@
 
+Beside these user-friendly pages, we provide two ways to access our knowledge base shown in Fig.\ref{fig:access}: via the search engine or via SPARQL endpoint.
+For general users, they can make a query by inputing related text into searchbox and search to get entities with similar label.
+To present practicable result, An index is generated over all entities.
+We as well provide SPARQL interface for professional users to query our knowledge graph.
+Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.%For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
+filter(langMatches(?label),"en"))}.
+
 \section{Related Work}
@@
 It first learns an ontology based on category system and properties, and then collects 19,542 classes, 2,381 properties, 802,593 instances.
-Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g.
+Besides using existing online-wikis, CASIA-KB employs other types of sources(e.g.
 microblog posts, news pages, images) to enrich the structured knowledge.
@@
 \label{sec:con}
-This paper presents a procedure of building a Chinese-English CLKB from four encyclopedia sources.
+This paper presents a procedure of building a Chinese-English CLKB from four wiki sources.
 At first, we extract structured information and unify data format.

### 2015-06-07 nlpcc/paper.tex
提交版本

@@
 \usepackage{color}
-\usepackage{CJK}
 \usepackage{url}
@@
 
+%\usepackage{CJK}
+
 \usepackage{xeCJK}
@@
 \setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
-\setCJKsansfont[BoldFont=STHeiti]
-\setCJKmonofont{STFangsong}
+%\setCJKmonofont{STFangsong}
 %\usepackage{CJKutf8}
@@
 
-\title{Building Large-Scale Cross-Lingual Knowledge Base from Heterogeneous Online Wikis}
+\title{Building a Large-Scale Cross-Lingual Knowledge Base from Heterogeneous Online Wikis}
 %\titlerunning{Bilingual Knowledge Base}
@@
 Cross-lingual Knowledge Bases are important for global knowledge sharing.
-However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy.
-In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems.
-The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike.
-An extension method is used to increase language links while a pruning approach is used to refine taxonomy.
-Totally, there are 663,740 classes, 11,721,238 instances, 56,449 properties referred in the CLKB.
-Among of them, 507,042 items are cross-lingual linked.
+However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the limited number of current cross-lingual language links; 3) the incorrect relation in semantic taxonomy.
+In this paper, a large-scale cross-lingual knowledge base(CLKB) is built to solve the above problems.
+Particularly, the CLKB integrates four online wikis including English Wikipedia, Chinese Wikipedia, Baidu Baike and Hudong Baike to balance the knowledge volume in different languages, employs a link-discovery method to augment the language links, and introduce a pruning approach to refine taxonomy.
+Totally, CLKB harvests 663,740 classes, 56,449 properties, 10,856,042 instances, among of which, 507,042 entities are cross-lingually linked.
 To the best of our knowledge, it's the first large-scale Chinese-English knowledge base with balanced knowledge quantity.
-Moreover, the paper provides visualization of knowledge and a SPARQL endpoint accessing to the established CLKB.
+At last, we provide a knowledge-display system supporting two ways to access the established CLKB, namely a keyword search box and a SPARQL endpoint.
 
-\keywords{Knowledge Base, Semantic Web, Taxonomy, Cross-lingual}
+\keywords{Knowledge Base, Cross-lingual Linking, Taxonomy Pruning}
 \end{abstract}
@@
 As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions.
-Multilingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering.
-DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}.
+Multi-lingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering.
+DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-lingual multi-domain knowledge base and becomes the nucleus of Linked Open Data\footnote{{\tt http://linkeddata.org/}}.
 Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.
@@
 However, most non-English knowledge in those knowledge bases is pretty scarce.
-Figure \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions.
+Fig.
+\ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions.
 Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia.
 For instance, DBpedia contains 4.58 million English instances but even no Chinese dataset published.
-On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia.
+On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 11 million articles, are even larger than the English Wikipedia.
 If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.
@@
 To enrich the Chinese knowledge, we try to build a large-scale Chinese-English knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike.
-In this paper, we propose a unified framework to build such a knowledge base.
-The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relation.
-The generated knowledge base contains 663,740 classes, 11,721,238 instances and 56,449 properties.
-An online system supporting keyword search and SPARQL endpoint is also developed.
-
 This non-trivial task poses the challenges as follows:
@@
   \item The subsumption relations of the online wikis' category systems contain lots of noise.
-For example, in English Wikipedia "Wikipedia-books-on-people", which is actually \verb"subClassOf" "Books", is taken as the sub-category of "People" mistakenly.
+For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly.
 How could we detect those incorrect semantic relations?
@@
 
-Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
+Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis.
+The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relations.
+The generated knowledge base contains 663,740 classes, 56,449 properties and 10,856,042 instances.
+Specifically, we make the following contributions:
 \begin{enumerate}
-  \item We achieve refined datasets from multiple heterogeneous online wikis through unified extracting process.
-  \item We extend cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
+  \item We extend cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and by analyzing templates in Wikipedia for property.
   \item We prune the original taxonomy, which is extracted from wiki category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.
-  \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
+  \item An online-system supporting keyword search and SPARQL endpoint is provided for public query operations over our knowledge base.
 \end{enumerate}
@@
 Section \ref{sec:pd} presents some basic concepts and the problem formulation.
-In Section \ref{sec:sde} we present detailed approaches.
+In Section \ref{sec:sde} we introduce detailed extraction approaches.
 Section \ref{sec:cli} describes cross-lingual integration.
@@
 \label{sec:pd}
-In this section, we give definitions about our knowledge base and describe the task in this work.
+In this section, we give definitions about our knowledge base and describe our task.
 
-\subsection{Basic Concepts}
+%\subsection{Basic Concepts}
 \para{Online Wikis.} Nowadays, Wikipedia is the largest data store of human knowledge.
@@
 Out of these, English articles contribute most.
-The imbalance of different language articles makes ontologies based on Wikipedia-only behave badly in cross-lingual.
-Thus, more Chinese sources are necessary to enrich Chinese source.
 
-Among the large-scale monolingual Chinese wikis currently, Baidu Baike and Hudong Baike are the most content-rich.
+Baidu Baike and Hudong Baike are the most content-rich among the large-scale monolingual Chinese wikis currently.
 Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015.
-Meanwhile, Baidu Baike maintains more than 11 million articles.
-
-Here, we consider an encyclopedia wiki as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.
+Meanwhile, Baidu Baike maintains over 11 million articles.
 
@@
 Usually they provide two important elements with potential semantic information, category system and articles.
+Here, we define an encyclopedia wiki as: $W = <C,A>$, where $C$ denotes categories, $A$ denotes articles in $W$.
 A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}.
 An article describes an entity with rich information.
-Each article is linked to one or more categories by \textit{articleOf} relation.
 In general, six elements can be exploited in each article page:
@@
   \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
-  \item Infobox: Most of articles contain infobox. An infobox maintains structured data in subject-attribute-value format.
+  \item Infobox: Most of articles contain infobox. An infobox maintains structured data in attribute-value format.
   \item Link: Links are entries to other articles within the wiki. They represent the relations between the current article and others.
@@
 An article $a$ can be defined as follow:
-\begin{equation}
+\begin{displaymath}
     a = <Ti(a),Ab(a),Li(a),In(a),C(a),U(a)>
-\end{equation}
+\end{displaymath}
 where $Ti(a),Ab(a),Li(a),In(a),C(a),U(a)$ denotes title, abstract, links, infobox, category tags, url of article $a$.
 
-Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited.
-A template defines items that a group of article should fill.
-Besides, infoboxes are also generated based on certain templates recommended by Wikipedia.
-For example, The infobox in film 冰雪奇缘(Frozen) is edited according to the Template \emph{Infobox film}, which maintains a property set of films.
-An infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}.
-We denote infobox template used in article $a$ as $T(a)$.
-Templates specify certain attributes, which are usually different from those displayed on the webpage.
-Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value.
+Notably, infoboxes in articles are generated based on certain templates recommended by Wikipedia.
+An infobox template collects attributes describing similar entities.
+For example, content in infobox of film 冰雪奇缘(Frozen) is normalized by \emph{Template:Infobox film}, which maintains a property set of films.
+We denote the infobox template used in article $a$ as $T(a)$.
+However, attribute labels in templates are usually different from those displayed on the webpage.
+Thus, we define an attribute as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is display label in web page and $v$ is the corresponding value.
 The value maybe a text or a reference to another entity.
 
-Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version articles.
+\para{Cross-lingual Links.} In Wikipedia, some article pages have language links which help readers switch to other language-version articles.
 %Fig.
 \ref{fig:interstellar} shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
-As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denote the article's language links in English and Chinese. To a $cl \in CL$, $cl(a) = <L_{z}(a), L_{e}(a)>$.
+As for an entity containing both Chinese article $a_{z}$ and English article $a_{e}$ in Wikipedia, $L_{z}$ and $L_{e}$ denote the entity's language links in Chinese and English.
+For a $cl \in CL$, $cl(a) = <L_{z}(a_{z}), L_{e}(a_{e})>$.
 
-\para{Knowledge Base} A knowledge base is a formal specification of a group of entities. Our knowledge base is described as a 4-tuple:
-\begin{equation}
+\para{Knowledge Base.} A knowledge base is a formal specification of a group of entities. Our knowledge base is described as a 4-tuple:
+\begin{displaymath}
     KB = <C,I,P,H^C>
-\end{equation}
-where $C$, $I$, $P$ are the sets of classes, instances, and properties, respectively.
-$H^C$ represents the hierarchical relationships of classes.
-The taxonomy of our knowledge base includes four types of relationships, which are \textit{subClassOf} of class-class, \textit{instanceOf} of class-instance, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.
+\end{displaymath}
+where $C$, $I$, $P$ are the sets of classes, instances, and properties, respectively. $H^C$ represents the hierarchical relationships of classes.
+
+Our knowledge base includes four kinds of semantic relation, which are \textit{subClassOf} of class-class, \textit{instanceOf} of class-instance, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.
 
@@
 Taking advantage of language links in $CL$, several monolingual knowledge bases generated from various sources can be merge into one.
-Thus our Chinese-English knowledge base can be defined as:
-\begin{equation}
+Thus our Chinese-English knowledge base is defined as:
+\begin{displaymath}
     CLKB = <KB_{z}, KB_{e}>
-\end{equation}
+\end{displaymath}
 where $KB_{z}$ and $KB_{e}$ denote the monolingual knowledge base in Chinese and English. CLKB combines the two according to $CL$.
 
-\para{Cross-lingual Knowledge Base Building} In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese wiki sources.
-Given an online-wiki $W_{i}$, we get dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each $W_{i}$ by extraction.
-We then enrich the extracted cross-lingual link set $CL$ using an link-discovery extension method.
-We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
-Our final output is an Chinese-English CLKB though process of combining $KB_{z}$ and $KB_{e}$ by utilizing language links in $CL$.
-
-The whole building procedure is shown in Fig.
+\para{Cross-lingual Knowledge Base Building.} In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese wiki sources.
+Given an online-wiki $W_{i}$, we get dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, class hierarchical relationships $H^C_{i}$ of $W_{i}$ by extraction.
+We then enrich the existing cross-lingual link set $CL$ using a link-discovery method.
+We also refine taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
+Our final output is a Chinese-English CLKB through process of combining $KB_{z}$ and $KB_{e}$ by utilizing language links in $CL$.
+The whole procedure is shown in Fig.
 \ref{fig:procedure}.
-We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
+%We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia.
 Because of heterogeneity, various extractors should be employed.
@@
 
-\vspace{-0.5cm}
 \begin{figure}[ht]
@@
 \end{figure}
-\vspace{-0.5cm}
 
@@
 Meanwhile, in Wikipedia, \textcolor{red}{例子}
-    \item Some categories relate to only one article.
-According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain them as classes.
+    \item Some categories relate to only one article. According to the definition of class, such categories are less representative types, therefore it's unwise to retain them as classes.
 \end{itemize}
@@
 A property is defined as an attribute of an entity.
-It represents the relation between an instance and its value.
-We divided properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 生日(birth date).
+It represents the relation between an entity and its value.
+We divide properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 生日(birth date).
 Considering both content and infobox of an article, we extract two kinds of properties, General-properties and Infobox-properties.
@@
 For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string.
-Meanwhile, 导演(directed by) is an object property because its value points to a person who directed the movie.
+On the other hand, 导演(directed by) is an object property because its value points to a person who directed the movie.
 
@@
 \begin{itemize}
-    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file.
-Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Frozen's} infobox.
+    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with that in the published dump file.
+Fig.
+\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Frozen's} infobox.
 The left is infobox, the middle is a glance from dump file in Wikipedia.
-We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
+The attribute label 主演 displayed on webpage is different from label \emph{starring} extracted from dump data.
+However, we generally consider the display label rather than extracted label as a property label.
     \begin{figure}[ht]
         \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
-        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
+        \caption{Comparison of display label and dump label in \emph{Frozen} infobox}
         \label{fig:infobox-template}
@@
 \item There are special characters in labels.
-Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels.
-For example, attribute \emph{population} property has sub-properties "-Density" and "-Urban".
-In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
+Wikipedia usually uses hyphen ``-" or dot ``•" to mark sublabels.
+For example, attribute \emph{population} property has sub-properties ``-Density" and ``Urban".
+In addition, colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
 \end{itemize}
@@
 Specifically, Wikipedia institutes rules of rendering label in templates.
-Right of Fig.\ref{fig:infobox-template} shows an example of \emph{Template:Infobox film}, where corresponding relations of display labels and dump labels come from.
+Right of Fig.
+\ref{fig:infobox-template} shows an example of \emph{Template:Infobox film}, where relations of display labels and dump labels come from.
 When a dump label occurs in dump file, we replace it by its mapping display label.
@@
 \label{sec:ie}
-An article describes unique entity in the world.
+An article describes a unique entity in the world.
 Therefore we can extract an article as an instance.
@@
 (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value; (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page.
-For example, 美国电影作品(American films) is a category of 冰雪奇缘(Frozen); (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).
+For example, 冰雪奇缘(Frozen) is an article of category 美国电影作品(American films); (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).
 
@@
 
-To construct a CLKB with existing structured data, firstly we increase cross-lingual links, which can help match the same entity in two languages.
+To construct a CLKB with obtained structured data, firstly we argument cross-lingual links, which can help match the same entity in two languages.
 Secondly, we integrate this four wikis, that is, respectively merging classes, instances and properties from the four sources if they represent the same thing.
@@
 \subsection{Cross-lingual Linking}
+We follow two ways to get cross-lingual links for class, instance and property.
+One is extracting links according to Wikipedia language links for class and instance, the other is achieving links using infobox templates for property.
+
 There are 227 thousand cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances.
@@
 \begin{enumerate}
-    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label.
-That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
-    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
+    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same template label.
+That is, for $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
+    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
     \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
@@
 For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese wikis by instance title.
-(2) To a $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$.
-If exists, make the two as one instance and identify it using an ID, else number it with a new ID.
+(2) To an $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$.
+If exists, make the two as one instance and identify it using an ID, otherwise number it with a new ID.
 
@@
 
-As a result of combining multi-source information without verifying, there is noise in taxonomy. %For example:
+%As a result of combining multi-source information without verifying, there is noise in taxonomy. %For example:
+There is inevitably noise in the taxonomy since we combine multi-source information without verification.
 Therefore, we introduce the method from \cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}.
@@
 In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance.
-Employing these features, a Yes-or-No binary-classification model is trained based on Logistic Regression.
+Employing these features, a binary-classification model is trained based on Logistic Regression.
 The whole process is iterative by retraining model with assured result to get higher precision.
-The prediction results are validated by cross-lingual information.
+Moreover, the prediction results are validated by cross-lingual information.
 
@@
 
-To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut class-instance relations and \textit{relatedTopicOf} for cut class-class relations.
+To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut class-instance relations and \textit{relatedTopicOf} for pruned class-class relations.
 
@@
 \label{sec:result}
+Here we show statistic results of our CLKB and introduce the system based on the knowledge base.
 
 \subsection{Extracted Knowledge Base}
-We collect the resources from four wiki sites, English and Chinese Wikipedia dump files in May, 2014, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
-Each of the wikis has three types of information, which can be utilized for constructing our knowledge base, namely, specific articles, category system, and attribute of articles.
+We collect the resources from four online wikis, English and Chinese Wikipedia dump files in May, 2014, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
+Each of the wikis has three types of information, which can be utilized for constructing our knowledge base, namely, specific articles, category system, and attributes of articles.
 We extract each raw data, then form the extracted information into well-structured data.
-Table \ref{tab:extract-result} the result we get after elementary extraction on 4 different wiki sources.
-Besides, we obtain 227 thousand language links between English and Chinese in Wikipeidia, and increase the number by 215 thousand enwiki-baidu language links and 10 thousand property links.
+Table \ref{tab:extract-result} shows the result we get after elementary extraction on 4 different wiki sources.
+Besides, we obtain 227 thousand class or instance links between English and Chinese in Wikipeidia, and increase the number by 215 thousand Enwiki-Baidu language links and 10 thousand property links.
+
 \vspace{-0.5cm}
@@
     \centering
-    \caption{Statistics of elementary extraction result}
+    \caption{Statistics of Elementary Extraction Result}
     \label{tab:extract-result}
-        \begin{tabular}{|l|l|l|l|l|}
+        \begin{tabular}{|p{2.5cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
             \hline
@@
 \end{table}
+\vspace{-0.5cm}
 
-We create URIs \url{http://clkb/type/id} (type could be \textit{class}, \textit{instance}, \textit{property}) to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.
+We create URIs \url{http://clkb/type/id} (type could be \textit{class}, \textit{instance}, \textit{property}) to identify each entry and provide corresponding information if users look up knowledge over HTTP protocol to achieve the knowledge base.
 
-After fusing the heterogeneous resources, we harvest a cross-lingual graph with 663,740 classes, 56,449 properties, and 11,721,238 instances respectively.
+After fusing the heterogeneous sources, we harvest a cross-lingual knowledge base with 663,740 classes, 56,449 properties, and 10,856,042 instances respectively.
 With different methods of extraction and language link discovery, these three kinds of entries show different results in languages.
@@
 \centering
-\caption{Statistics of our knowledge base}
+\caption{Statistics of Our Knowledge Base}
 \label{tab:kb-result}
-\begin{tabular}{|l|l|l|l|l|l|l|}
+\begin{tabular}{|p{2cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
 \hline
@@
 Only English           & 575,125 & 86.65\%                & 3,446,523              & 31.75\%                & 4,831   & 8.56\%    \\ \hline
-Only Chinese           & 24,720  & 3.72\%                 & 7,409,519              & 64,27\%                  & 41,069  & 72.75\%   \\ \hline
-Total                  & 663,740 & \multicolumn{1}{c|}{-} & 11,721,238             & \multicolumn{1}{c|}{-} & 56,449  & \multicolumn{1}{c|}{-} \\ \hline
+Only Chinese           & 24,720  & 3.72\%                 & 6,976,921              & 64,27\%                & 41,069  & 72.75\%   \\ \hline
+Total                  & 663,740 & \multicolumn{1}{c|}{-} & 10,856,042             & \multicolumn{1}{c|}{-} & 56,449  & \multicolumn{1}{c|}{-} \\ \hline
 \end{tabular}
@@
 
-Our knowledge graph is organized in Openlink Virtuoso, which is a data management platform rendering various services, including triple store.
+Our knowledge base is organized in Openlink Virtuoso, which is a data management platform rendering various services, including triple store.
 
@@
     \centerline{\includegraphics[width=1\columnwidth]{fig/xlore}}
-    \caption{Sample Pages of Class, Instance and Property}
+    \caption{Sample Pages of Instance, Class and Property}
     \label{fig:xlore}
@@
 
-We provide a platform to present an intuitive graph of our knowledge in the forms of class, instance and property.
-Fig.\ref{fig:xlore} shows sample pages of the integrated data.
-Users can choose language preference which is convenient for both English speaker and Chinese speaker.
-In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.
- In the instance webpage we display bilingual label, super classes, related classes, abstracts, infobox-properties, images and references.
-In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
+We provide a platform to present an intuitive visualization of our knowledge in the forms of class, instance and property.
+Fig.
+\ref{fig:xlore} shows sample pages of the integrated data.
+Language could be switched, which is convenient for both English speaking and Chinese speaking user.
+In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way.
+In the instance webpage we display bilingual label, super classes, related classes, abstracts, infobox-properties, images and URL references.
+In the property webpage, we present bilingual label, type, and related instances of each property.
 
@@
 \centering
-\subfigure[A picture of Search Box]{
+\subfigure[A Sample of Search Box ]{
     \label{fig:search-engine}
@@
 \hspace{0.01cm}
-\subfigure[A SPARQL Sample Query]{
+\subfigure[A Sample of SPARQL Query ]{
     \label{fig:sparql-endpoint}
@@
     }
-\caption{Two ways to our knowledge base}
+\caption{Two Ways Accessing to Our Knowledge Base}
 \label{fig:access}
@@
 
-Beside these user-friendly pages, we provide two ways to access our knowledge base shown in Fig.\ref{fig:access}: via the search engine or via SPARQL endpoint.
-For general users, they can make a query by inputing related text into searchbox and search to get entities with similar label.
+Beside these user-friendly pages, we provide two ways to access our knowledge base shown in Fig.
+\ref{fig:access}: via the search engine or via SPARQL endpoint.
+For general users, they can make a query by inputing related text into searchbox to get probable related entities.
 To present practicable result, An index is generated over all entities.
 We as well provide SPARQL interface for professional users to query our knowledge graph.
-Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}.%For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
+Users can choose the language tags of their desired results by \textbf{``filter(langMatches(?label),``en"))"} or \textbf{``filter(langMatches (?label),``zh"))"}.%For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label.
 filter(langMatches(?label),"en"))}.
@@
 \label{sec:work}
-In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods.
+In this section, we introduce some related knowledge bases. %and cross-lingual knowledge linking methods.
 
@@
 It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities.
-Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
+Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan's work\cite{pan2012building}.
 
@@
 \para{Cross-lingual Knowledge Bases.} DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world.
-It extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content.
+It extracts various kinds of structured information from Wikipedia and employ the multi-lingual characteristic of Wikipedia to generate 97 language versions of content.
 This knowledge base is widely applied in many domains, including media recommendation \cite{fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
-Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
+Universal WordNet(UWN)\cite{de2012uwn} is a large multi-lingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
 It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods.
@@
 %\subsection{Cross-lingual Knowledge Linking}
-%Discovering more cross-lingual links is benefit to development of a multilingual knowledge base.
+%Discovering more cross-lingual links is benefit to development of a multi-lingual knowledge base.
 General method is divided into two steps.
@@
 To refine our dataset, we also conduct pruning work on taxonomy.
-Finally, we acquire a CLKB containing 663,740 classes, 11,721,238 instances and 56,449 properties.
-Currently, a website and SPARQL query interface is provided to access the knowledge base.
+Finally, we acquire a CLKB containing 663,740 classes, 56,449 properties, and 10,856,042 instances.
+Currently, an online-system and a SPARQL query interface is provided to access the knowledge base.
 

### 2015-06-14 nlpcc/paper.tex
6.13 deadline之后又一版

@@
 
+%%% windows 注释这里  %%%
 \usepackage{xeCJK}
-%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
 \setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
@@
 %\usepackage{CJKutf8}
-
-%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
-%\setCJKmainfont[BoldFont=SimHei]{SimSun}
-%\setCJKmonofont{SimSun}% 设置缺省中文字体
+%%% windows 注释这里  %%%
 
@@
 In this paper, a large-scale cross-lingual knowledge base(CLKB) is built to solve the above problems.
-Particularly, the CLKB integrates four online wikis including English Wikipedia, Chinese Wikipedia, Baidu Baike and Hudong Baike to balance the knowledge volume in different languages, employs a link-discovery method to augment the language links, and introduce a pruning approach to refine taxonomy.
-Totally, CLKB harvests 663,740 classes, 56,449 properties, 10,856,042 instances, among of which, 507,042 entities are cross-lingually linked.
-To the best of our knowledge, it's the first large-scale Chinese-English knowledge base with balanced knowledge quantity.
-At last, we provide a knowledge-display system supporting two ways to access the established CLKB, namely a keyword search box and a SPARQL endpoint.
+Particularly, the CLKB integrates four online wikis including English Wikipedia, Chinese Wikipedia, Baidu Baike and Hudong Baike to balance the knowledge volume in different languages, employs a link-discovery method to augment the language links, and introduces a pruning approach to refine taxonomy.
+Totally, CLKB harvests 663,740 classes, 56,449 properties, and 10,856,042 instances, among of which, 507,042 entities are cross-lingually linked.
+To the best of our knowledge, our CLKB is the first large-scale Chinese-English knowledge base with balanced knowledge quantity.
+At last, we provide a knowledge-display system supporting two ways to access the established CLKB, namely a keyword search entrance and a SPARQL endpoint.
 
@@
 As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions.
-Multi-lingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering.
-DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-lingual multi-domain knowledge base and becomes the nucleus of Linked Open Data\footnote{{\tt http://linkeddata.org/}}.
+Multi-lingual knowledge bases have significant applications such as information retrieval, machine translation and deep question answering.
+DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-domain knowledge base covering many domains and becomes the nucleus of Linked Open Data\footnote{{\tt http://linkeddata.org/}}.
 Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.
@@
 Fig.
-\ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions.
-Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia.
+\ref{fig_stat} shows a long tail distribution of the number of articles on six major Wikipedia language versions until June,2015.
+Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases generated from Wikipedia.
 For instance, DBpedia contains 4.58 million English instances but even no Chinese dataset published.
 On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 11 million articles, are even larger than the English Wikipedia.
-If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.
+If a knowledge base could be established based on both English Wikipedia and Chinese Hudong Baike, a Chinese-English knowledge base with much higher coverage in Chinese can be constructed.
 
@@
   \item The subsumption relations of the online wikis' category systems contain lots of noise.
-For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly.
+For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \textit{subClassOf} ``Books", is taken as the sub-category of ``People" mistakenly.
 How could we detect those incorrect semantic relations?
@@
 Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis.
-The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relations.
+The framework contains three steps: extracting dataset from online wikis, extending an initial cross-lingual link set, and pruning taxonomy for more precise semantic relations.
 The generated knowledge base contains 663,740 classes, 56,449 properties and 10,856,042 instances.
@@
   \item We prune the original taxonomy, which is extracted from wiki category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.
-  \item An online-system supporting keyword search and SPARQL endpoint is provided for public query operations over our knowledge base.
+  \item An online-system supporting keyword search and SPARQL endpoint is provided for public access to our knowledge base.
 \end{enumerate}
@@
 The experimental results are reported in Section \ref{sec:result}.
-Some related work are given in Section \ref{sec:work}.
+Related works are given in Section \ref{sec:work}.
 Finally we conclude our work in Section \ref{sec:con}.
@@
 It was launched in 2001 and has hold over 35 million articles in 288 languages by 2015.
-Out of these, English articles contribute most.
+Out of these, English articles contribute 13\% while Chinese articles account for 2\%.
 
 Baidu Baike and Hudong Baike are the most content-rich among the large-scale monolingual Chinese wikis currently.
-Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015.
+Hudong Baike was founded in 2005 and contains more than 12 million articles until 2015.
 Meanwhile, Baidu Baike maintains over 11 million articles.
 
-\para{Wiki Pages.} Articles from the wiki sources are similar in structure.
-Usually they provide two important elements with potential semantic information, category system and articles.
+Wikis usually provide two important elements with potential semantic information, category system and articles.
 Here, we define an encyclopedia wiki as: $W = <C,A>$, where $C$ denotes categories, $A$ denotes articles in $W$.
 A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}.
-An article describes an entity with rich information.
-In general, six elements can be exploited in each article page:
+
+\para{Wiki Pages.} Articles from the wiki sources are similar in structure. An article describes an entity with rich information. In general, six elements can be exploited in each article page:
 %\begin{figure}
@@
 \begin{itemize}
-  \item Title: A Title is the label of an entity, whose uniqueness can be used to distinguish entities.
-  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
-  \item Infobox: Most of articles contain infobox. An infobox maintains structured data in attribute-value format.
-  \item Link: Links are entries to other articles within the wiki. They represent the relations between the current article and others.
-  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
-  \item URL: Each article has an HTTP url to identify itself on web.
+  \item \textbf{Title:} A Title is the label of an entity, whose uniqueness can be used to identify entities.
+  \item \textbf{Abstract:} An abstract which is always the first paragraph in content, is a brief summary of the entity.
+  \item \textbf{Infobox:} An infobox maintains structured data describing representative features of entity in subject-attribute-value triples.
+  \item \textbf{Link:} Links are entries to other articles within the wiki. They represent the relations between the current article and others.
+  \item \textbf{Category:} Categories that an article belongs to are usually listed at the bottom of article page. An article has \textit{articleOf} relation with its categories.
+  \item \textbf{URL:} Each article has an HTTP url to locate itself on web.
 \end{itemize}
@@
 An infobox template collects attributes describing similar entities.
-For example, content in infobox of film 冰雪奇缘(Frozen) is normalized by \emph{Template:Infobox film}, which maintains a property set of films.
+For example, content in infobox of film 冰雪奇缘(Frozen) is normalized by \emph{Template:Infobox film}, which maintains a property set of films that should be given assignment.
 We denote the infobox template used in article $a$ as $T(a)$.
@@
 
-\para{Cross-lingual Links.} In Wikipedia, some article pages have language links which help readers switch to other language-version articles.
+\para{Cross-lingual Links.} In Wikipedia, some article pages have cross-lingual links which help readers switch to corresponding articles in other languages.
 %Fig.
 \ref{fig:interstellar} shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
-As for an entity containing both Chinese article $a_{z}$ and English article $a_{e}$ in Wikipedia, $L_{z}$ and $L_{e}$ denote the entity's language links in Chinese and English.
-For a $cl \in CL$, $cl(a) = <L_{z}(a_{z}), L_{e}(a_{e})>$.
+As for an entity containing both Chinese article $a_{z}$ and English article $a_{e}$ in Wikipedia, we say $a_{z}$ and $a_{e}$ are \emph{cross-linked}.
+Infobox templates may also be cross-linked because they are articles in Wikipedia actually.
+For a pair $cl \in CL$, $cl = <L_{z}, L_{e}>$, where $L_{z}$ and $L_{e}$ denote the entity's cross-lingual links in Chinese and English.
+.
 
@@
 \begin{displaymath}
-    KB = <C,I,P,H^C>
+    KB = <C,P,I,H^C>
 \end{displaymath}
-where $C$, $I$, $P$ are the sets of classes, instances, and properties, respectively. $H^C$ represents the hierarchical relationships of classes.
+where $C$, $P$, $I$ are the sets of classes, properties, and instances respectively. $H^C$ represents the hierarchical relationships of classes.
 
-Our knowledge base includes four kinds of semantic relation, which are \textit{subClassOf} of class-class, \textit{instanceOf} of class-instance, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.
+Our knowledge base includes four kinds of semantic relation, which are \textit{subClassOf} of class-class, \textit{instanceOf} of instance-class, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.
 
-A Cross-lingual Knowledge Base(CLKB) is a database conform to a cross-lingual ontology.
-Taking advantage of language links in $CL$, several monolingual knowledge bases generated from various sources can be merge into one.
+A Cross-Lingual Knowledge Base(CLKB) is a database conforming to a cross-lingual ontology.
+Taking advantage of cross-lingual links, several monolingual knowledge bases generated from various sources can be merge into one.
 Thus our Chinese-English knowledge base is defined as:
@@
 \end{displaymath}
-where $KB_{z}$ and $KB_{e}$ denote the monolingual knowledge base in Chinese and English. CLKB combines the two according to $CL$.
+where $KB_{z}$ and $KB_{e}$ denote the monolingual knowledge base in Chinese and English.
 
-\para{Cross-lingual Knowledge Base Building.} In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese wiki sources.
-Given an online-wiki $W_{i}$, we get dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, class hierarchical relationships $H^C_{i}$ of $W_{i}$ by extraction.
+\para{Cross-Lingual Knowledge Base Building.} In this paper, our task is to build a CLKB assembling knowledge from several English and Chinese wiki sources.
+Given an online-wiki $W_{i}$, the final output is a Chinese-English CLKB combining $KB_{z}$ and $KB_{e}$.
+
+Specifically, we gain dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, class hierarchical relationships $H^C_{i}$ of $W_{i}$ by extraction.
 We then enrich the existing cross-lingual link set $CL$ using a link-discovery method.
 We also refine taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship.
-Our final output is a Chinese-English CLKB through process of combining $KB_{z}$ and $KB_{e}$ by utilizing language links in $CL$.
+At last the datasets in different languages are integrated by utilizing cross-lingual links in $CL$.
 The whole procedure is shown in Fig.
@@
     \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
-    \caption{Procedure of Building Our Cross-lingual Knowledge Base}
+    \caption{Procedure of Building Our Cross-Lingual Knowledge Base}
     \label{fig:procedure}
@@
 Semantic data extraction aims to achieve a structured dataset from the input wikis.
-Specifically, we extract classes from category system, instances according to articles, and properties based on infoboxes and their templates.
+Specifically, we extract classes from category system, instances according to articles, and properties based on infoboxes.
 
@@
 A class is defined as a type of similar instances.
-For example, the class of instance \emph{Frozen} is \emph{Film}.
-In general, a class has super classes and sub classes.
-Classes comprise a taxonomy which presents a backbone of an ontology.
-In a wiki, a category groups several articles and also has super-categories and sub-categories.
+For example, the class of instance 冰雪奇缘(Frozen) is 电影(Film).
+In general, a class is semantic related with other classes by $subClassOf$ relation.
+Such relations comprise a class hierarchy $H^C$ which presents the backbone of an ontology.
+In a wiki, a category groups several articles and also has $subCategoryOf$ relation with others.
 Therefore we can extract classes based on existing category system.
 
-However, the whole taxonomy can not directly transform from category system due to the following problems:
+However, the whole class hierarchy can not directly transform from category system due to the following problems:
 \begin{itemize}
@@
 
-To obtain a more precise $H^C$ in a wiki, we remove categories fit the above situations, then build the original class hierarchy $H^C$ using the remaining categories.
+To gain a more precise $H^C$ in a wiki, we discard categories matching the above conditions, then build the original class hierarchy $H^C$ using the remaining categories.
 
@@
 A property is defined as an attribute of an entity.
-It represents the relation between an entity and its value.
-We divide properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 生日(birth date).
+We divide properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 出生日期(birth date).
 Considering both content and infobox of an article, we extract two kinds of properties, General-properties and Infobox-properties.
 
-\para{General-properties.} Characteristics of an entity are regarded as general properties, including label, abstract, and url.
-General-properties describe general information of an entity.
-We define three datatype properties as general-properties for a given article $a$: (1) label property; (2) abstract property; (3) URL property.
+\para{General-properties.} %Characteristics of an entity are regarded as general properties, including label, abstract, and url. 
+General-properties describe general information of an entity. We define three datatype properties as general-properties for a given article $a$: (1) label; (2) abstract; (3) URL.
 
 \para{Infobox-properties.} Attributes acquired from infobox are considered as infobox properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox.
-The type of a property, datatype or object, depends on the type of the value.
+The type of a property, datatype or object, depends on the type of its value.
 Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object.
@@
 \begin{itemize}
-    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with that in the published dump file.
+    \item In Wikipedia, because the data is from dump files published in specific XML format rather than html pages like Baidu or Hudong, the attribute label displayed in the webpage infobox is inconsistent with that in the published dump file.
 Fig.
-\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Frozen's} infobox.
-The left is infobox, the middle is a glance from dump file in Wikipedia.
+\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in 冰雪奇缘(Frozen)'s infobox.
+Webpage infobox is on the left.
+The right is a glance from dump file in Wikipedia.
 The attribute label 主演 displayed on webpage is different from label \emph{starring} extracted from dump data.
-However, we generally consider the display label rather than extracted label as a property label.
+However, readers generally consider the display label rather than extracted label as an attribute label.
     \begin{figure}[ht]
-        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
+        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template3}}
         \caption{Comparison of display label and dump label in \emph{Frozen} infobox}
@@
 Wikipedia usually uses hyphen ``-" or dot ``•" to mark sublabels.
-For example, attribute \emph{population} property has sub-properties ``-Density" and ``Urban".
-In addition, colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
+For example, attribute 人口(population) has sub-attributes ``-Density" and ``-Urban".
+In addition, ``:" or ``*", may occur in Baidu or Hudong attribute labels by mistake.
 \end{itemize}
@@
 Specifically, Wikipedia institutes rules of rendering label in templates.
-Right of Fig.
+Middle of Fig.
 \ref{fig:infobox-template} shows an example of \emph{Template:Infobox film}, where relations of display labels and dump labels come from.
 When a dump label occurs in dump file, we replace it by its mapping display label.
+Then we clean attribute labels to sweep incorrect characters.
+Furthermore, properties correspond to only one instance are discarded.
 
@@
 To construct a CLKB with obtained structured data, firstly we argument cross-lingual links, which can help match the same entity in two languages.
-Secondly, we integrate this four wikis, that is, respectively merging classes, instances and properties from the four sources if they represent the same thing.
+Secondly, we integrate four wiki datasets, that is, respectively merging classes, instances and properties from the four sources.
 Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.
@@
 \begin{enumerate}
-    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same template label.
-That is, for $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
-    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
-    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
+    \item Given two cross-linked templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same template label.
+That is, for $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $p_{e}.tl$ is equal to $p_{z}.tl$, $<p_{e}.dl,p_{z}.dl>$ are cross-lingual property labels;
+    \item Given two cross-linked articles, $a_{e}$ and $a_{z}$, and their infobox templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same template label;
+    \item Given two cross-linked articles and their Infobox-properties $P_{e}$ and $P_{z}$, $p_{e}.dl$ and $p_{z}.dl$ are cross-lingual when: (1)for datatype properties, if $sim(p_{e}.v, p_{z}.v) > threshold$(usually useful when the value is datetime or number), where $sim(a,b)$ is a similarity calculation function.
+(2)for object properties, if $p_{e}.v$ and ${p_{z}.v}$ refer to the same entity.
 \end{enumerate}
 
-In order to make all wikis link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers.
-For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese wikis by instance title.
-(2) To an $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$.
-If exists, make the two as one instance and identify it using an ID, otherwise number it with a new ID.
+In order to integrate all wikis into one, we unify classes(instances or properties) describing the same thing from four sources, and distribute a unique identifiers.
+For instance, we merge instances by the following steps: (1) Merge all instances extracted from wikis by title.
+(2) If a Chinese instance has a cross-linked English instance, that is, to an $L_{z}$, if there is $<L_{z}, L_{e}>$ in $CL$, make the two as one instance.
+(3) Identify all instances, including both monolingual or matched, by IDs.
 
@@
 
-The ideal result after pruning is a tree, whose edges, nodes, and leaves respectively denote relations, classes and instances.
+The ideal result after pruning is a tree, whose edges, nodes, and leaves respectively denote semantic relations, classes and instances.
 However, since getting rid of incorrect entity relations without consideration of integrity, a forest result is inevitable.
 
-To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut class-instance relations and \textit{relatedTopicOf} for pruned class-class relations.
+To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut instance-class relations and \textit{relatedTopicOf} for pruned class-class relations.
 
@@
 We collect the resources from four online wikis, English and Chinese Wikipedia dump files in May, 2014, Hudong html pages until May, 2014, and Baidu html pages until September, 2014.
-Each of the wikis has three types of information, which can be utilized for constructing our knowledge base, namely, specific articles, category system, and attributes of articles.
+Each of the wikis has three types of information, which can be utilized for constructing our knowledge base, namely, category system, specific articles, and attributes of articles.
 We extract each raw data, then form the extracted information into well-structured data.
 Table \ref{tab:extract-result} shows the result we get after elementary extraction on 4 different wiki sources.
-Besides, we obtain 227 thousand class or instance links between English and Chinese in Wikipeidia, and increase the number by 215 thousand Enwiki-Baidu language links and 10 thousand property links.
+Besides, we obtain 227 thousand class or instance links between English and Chinese in Wikipeidia, and increase the number by 215 thousand Enwiki-Baidu language links and 10 thousand property cross-lingual links.
 
@@
                        & Enwiki    & Zhwiki   & Hudong    & Baidu     \\ \hline
+            \#Class    & 982,432   & 159,705  & 31,802    & 1300      \\ \hline
             \#Instance & 4,304,113 & 662,650  & 5,590,751 & 5,622,404 \\ \hline
-            \#Class    & 982,432   & 159,705  & 31,802    & 1300      \\ \hline
             \#Property & 43,976    & 18,842   & 1187      & 139,634   \\ \hline
@@
 \hline
-\multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Classes}     & \multicolumn{2}{c|}{Instance}                   & \multicolumn{2}{c|}{Property}    \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{2}{c|}{Classes}     & \multicolumn{2}{c|}{Instances}                   & \multicolumn{2}{c|}{Properties}    \\ \hline
 English                & 639,020 & 96.26\%                & 3,879,121              & 38.79\%                & 15,380  & 27.24\%                \\ \hline
@@
 Cross-lingual          & 63,895  & 9.63\%                 & 432,598                & 3.98\%                 & 10,549  & 18.69\%                \\ \hline
-Only English           & 575,125 & 86.65\%                & 3,446,523              & 31.75\%                & 4,831   & 8.56\%    \\ \hline
-Only Chinese           & 24,720  & 3.72\%                 & 6,976,921              & 64,27\%                & 41,069  & 72.75\%   \\ \hline
+English Only           & 575,125 & 86.65\%                & 3,446,523              & 31.75\%                & 4,831   & 8.56\%    \\ \hline
+Chinese Only           & 24,720  & 3.72\%                 & 6,976,921              & 64,27\%                & 41,069  & 72.75\%   \\ \hline
 Total                  & 663,740 & \multicolumn{1}{c|}{-} & 10,856,042             & \multicolumn{1}{c|}{-} & 56,449  & \multicolumn{1}{c|}{-} \\ \hline
@@
 
-Our knowledge base is organized in Openlink Virtuoso, which is a data management platform rendering various services, including triple store.
-
-\subsection{Web Access to Knowledge Base}
+\subsection{Web Access to CLKB}
 
@@
 
+Our knowledge base is organized in Openlink Virtuoso, which is a data management platform rendering various services, including triple store.
+
 We provide a platform to present an intuitive visualization of our knowledge in the forms of class, instance and property.
@@
 In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way.
-In the instance webpage we display bilingual label, super classes, related classes, abstracts, infobox-properties, images and URL references.
+In the instance webpage we display bilingual label, types, related classes, abstracts, infobox-properties, images and URL references.
 In the property webpage, we present bilingual label, type, and related instances of each property.
@@
 
-Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike.
+Similar to Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike.
 It first learns an ontology based on category system and properties, and then collects 19,542 classes, 2,381 properties, 802,593 instances.
@@
 \para{Cross-lingual Knowledge Bases.} DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world.
-It extracts various kinds of structured information from Wikipedia and employ the multi-lingual characteristic of Wikipedia to generate 97 language versions of content.
+It extracts various kinds of structured information from Wikipedia and employs the multi-lingual characteristic of Wikipedia to generate 97 language versions of content.
 This knowledge base is widely applied in many domains, including media recommendation \cite{fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
-Universal WordNet(UWN)\cite{de2012uwn} is a large multi-lingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia.
+
+Universal WordNet(UWN)\cite{de2012uwn} is a large multi-lingual lexical knowledge base which is built from WordNet and enrich entities from Wikipedia.
 It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods.
-The API is available to over 200 languages and more than 16 million words and names.
-UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015conceptual}
+The API accesses to more than 16 million words and names in over 200 languages.
+UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015conceptual}.
 
@@
 At first, we extract structured information and unify data format.
-Then a cross-lingual language link set is generated and expanded to help combine the bilingual sources.
+Then a cross-lingual link set is generated and expanded to help combine the bilingual sources.
 To refine our dataset, we also conduct pruning work on taxonomy.
 Finally, we acquire a CLKB containing 663,740 classes, 56,449 properties, and 10,856,042 instances.
-Currently, an online-system and a SPARQL query interface is provided to access the knowledge base.
+Currently, an online-system supporting keyword search and SPARQL query is provided to access the knowledge base.
 
